\documentclass[12pt]{book}
\frenchspacing
\usepackage{makeidx}
\makeindex

\begin{document}

\title{\textit{I Waded In Clear Water}: A Novel}
\author{Allison Parrish}
\date{November 2014}

\frontmatter
\maketitle

\pagestyle{empty}
%% copyrightpage
\begingroup
\footnotesize
\parindent 0pt
\parskip \baselineskip
\textcopyright{} 2014 Allison Parrish \\
All rights reserved.

This work is licensed with Creative Commons Attribution-ShareAlike 4.0
International. You are free to share (copy and redistribute the material in any
medium or format) and adapt (remix, transform, and build upon the material) for
any purpose, even commercially.

The licensor cannot revoke these freedoms as long as you follow the license
terms.

http://creativecommons.org/licenses/by-sa/4.0/

\endgroup
\clearpage

\pagestyle{myheadings}

\chapter{Preface}

This novel was generated from the text of Gustavus Hindman Miller's \textit{Ten
Thousand Dreams, Interpreted}. The ``What's In A Dream'' section of Miller's
book functions as a dream dictionary: you look up a word, and find out what it
means to dream about that word's referent. Each word has multiple interpretations,
and most of these interpretations can be broken down into what I
call an \textit{action} and a \textit{denotation}:

\begin{quote}
To see an oak full of acorns, denotes increase and promotion.
\end{quote}

In this entry, \textit{See an oak full of acorns} is the action, and
\textit{increase and promotion} is the denotation. The text of this novel was
made by extracting the actions and changing them to first-person, past-tense
sentences:

\begin{quote}
I saw an oak full of acorns.
\end{quote}

The denotation for each action is scored using a sentiment analysis algorithm,
and the sentences are printed in order by the sentiment of their corresponding
denotation, from most negative to most positive. (According to the sentiment
analysis algorithm, the first sentence of the novel, ``I saw a healthy belly,'' is the worst
thing that can happen in a dream; the last sentence, ``I waded in clear water,''
is the best thing.)

Elaborations, in the form of footnotes, are provided for many sentences. These
elaborations are generated using information in ConceptNet (in particular, the
\textit{IsA}, \textit{HasProperty}, and \textit{AtLocation} relations) and WordNet (for part-of-speech
checks, synonyms, and antonyms).

\mainmatter



\chapter{}

I saw a healthy \index{belly}belly\footnote{The belly was both stupid and intelligent. A bellybutton was in it.}. I was cursing myself. I saw \index{chicken}chickens\footnote{A hen. They were in a fair, and this fair looked good. You found a cotton candy within.} going to roost. I roosted. I sent for a clergyman to preach a funeral \index{sermon}sermon. I preached a funeral \index{sermon}sermon. I saw them out of \index{season}season. I was having trouble in \index{dressing}dressing. I thought I was having \index{trouble}trouble\footnote{Your trouble was in a street. We found a person there. (This person was warm-blooded.)} in \index{dressing}dressing. I saw \index{ears}ears. I tried to enchant others. I enchanted others. I saw a jailer. I saw \index{serpent}serpents\footnote{This serpent was slimy and unworthy.} crawling in the grass before me. I was in a \index{life-boat}life-boat. 

 I heard a minister exhort. I saw a dead \index{monkey}monkey\footnote{We found a marmoset there. They were seen in a treetop.}. I heard my cry as if in \index{pain}pain\footnote{A cottage was within our pain. (I saw them in an ass.) Bad. You said they were an ache.}. I killed one. I was building a \index{shelter}shelter\footnote{This shelter was in a house. Red. (A brownstone.) My brownstone did not appear big.}. I felt that any insect stings me. 

 I saw the \index{ruler}ruler\footnote{My ruler was straight, and we saw them in an office. (I found a telephone in this office.)} of my country undressed. I saw a vat. I was favoring any \index{vice}vice\footnote{Your vice was found in a workshop. We found a vice within. My vice did not seem useful.}. I drank \index{vinegar}vinegar\footnote{Your vinegar was sour, and it was fluid.}. I signed one. 



\chapter{}

I drove into muddy \index{water}water\footnote{I found an anemone there. (We found this anemone in an ocean.) You said that it was not alive.}. I saw others weeding.

\chapter{}

I abandoned. I won the game. I ate them at any \index{time}time\footnote{I saw your time in a timetable. We found a confetti within.}. I was spattered with \index{egg}eggs\footnote{We found a yolk within. (You told me your yolk was yellow, and it was discovered in an egg.)}. I saw a \index{head}head\footnote{The head was on. You found a mouth within. This mouth was a mouth organ but not a mouth harp.} severed from its trunk. I hugged a man. I broke open a \index{jail}jail\footnote{You found a rapist in your jail. (Your rapist was seen in a jail, and the jail was bad and forged.)}. I saw a mob attempting to break open a \index{jail}jail. I was peeling the \index{skin}skin\footnote{Yellow. It was in a good health, and I found a skin within.} from a \index{lamb}lamb. I saw pretty \index{girl}girls\footnote{A hose was within my girl. They seemed vain, and you said they were a niece. They appeared beautiful, and I found them in a movie.} at this \index{work}work\footnote{This work was found in a desk. (You said it was not a homework.)}. I drank some. I bought them. I could see the \index{bone}bone\footnote{We found a cartilage in the bone, and our cartilage was found in a tendon.}. I saw a \index{shooting}shooting or falling \index{star}star\footnote{Our star was seen in an outer space. An astronaut was within this outer space. (Noisy.) Black.}. I had \index{tar}tar\footnote{This tar was not a vehicle. Sticky. I found a tar pit in it, and it was found in a roof.} on my hands or clothing. I saw others undressed. I saw it rise up in my \index{house}house\footnote{Our house was a cellar but not a wine cellar. A wall was within it. (My wall was in a fridge, and my fridge was both white and black.)}. I saw it appearing weird. 



\chapter{}

I looked for one. I was in a hypnotic \index{state}state\footnote{Our state was false, and a county was in it. It was in a state capital.} or under the \index{power}power\footnote{A wind. They were in a desk, and my desk was flammable. (You told me it was clear.) We found a blotter in it.} of others. 

 I saw a corpse in black. 

 I heard a \index{cry}cry\footnote{A drug dealer was in the cry. I saw our drug dealer in a nightclub. Fragile.} for \index{help}help\footnote{Beneficial. (They were in a dentist.)} from relatives. I saw the \index{sun}sun\footnote{You told me your sun was red, and you saw them in a solar system. A star. They were hot but not live. You found a sunspot in them.} while flying. I hurt a person. I was poisoned. I fed that I was poisoned. I thought my husband or \index{lover}lover\footnote{A penis was within the lover. (They were seen in a restaurant.) They looked attractive and repulsive.} was a rogue. I had a misunderstanding with one. 

 I broke or ignore a vow. 



\chapter{}

I was in the \index{clutch}clutches\footnote{Your clutch seemed lightweight, and you saw it in a lipstick.} of \index{adversity}adversity. I was attired in a guazy black \index{costume}costume\footnote{I saw this costume in a theatre, and an audience was within my theatre.}. I saw a nude \index{back}back\footnote{Your back seemed important. (They were seen in a backdrop.)}. 

 I saw beard on \index{woman}women\footnote{We found a bobby pin in this woman. (They looked beautiful, and they were seen in a home.) Your home seemed white. It was not a mansion.}. 

 I saw a swollen mortifying \index{belly}belly\footnote{My belly was both creative and uncreative, and you found a fluff there.}. I saw a boiler out of repair. 

 I gave it away. I rode in a \index{cab}cab\footnote{Green. A cable. Your cable was found in a desk, and a stapler was not in my desk. Opaque.} with a \index{woman}woman. I saw a calendar. I saw a \index{cart}cart\footnote{The cart was a wheelbarrow. My wheelbarrow was two-dimensional but not flat.}. 

 I held hands full of \index{chalk}chalk\footnote{This chalk seemed clean. (You said it was a chalkboard.) Our chalkboard was found in a school.}. I saw a chambermaid. I was in a chapel. I saw a \index{clock}clock\footnote{The clock was a stop watch but not a stopwatch. (It seemed expensive.) It was discovered in a wall.}. I saw dark heavy \index{cloud}clouds\footnote{You told me your cloud was light, and a marmot was not in it. It was discovered in a blue sky.}. I found myself sitting on a \index{coffin}coffin\footnote{My coffin was opaque and unintelligible. It was in an underground. I found a corpse in it.} in a moving \index{hearse}hearse. I had bad and dark \index{complexion}complexion. I placed this rose in my hair. I heard of any \index{friend}friend\footnote{I found a dance in your friend. Your dance was in a dance floor.} or relative being dead. I held disputes over \index{trifle}trifles. I heard the growling and snarling of \index{dog}dogs\footnote{You found our dog in a rug. They were a golden retriever. Playful.}. I heard the distant braying filling space with \index{melancholy}melancholy\footnote{My melancholy seemed unpleasant.}. I closed a \index{door}door\footnote{An entrance. It was solid. We found it in a house, and a bathroom was in your house. (It was good and sound.)}. I attempted to close a \index{door}door\footnote{Underground. You found a lock in it, and you said it was not an entrance. (You found it in a front door.)}. I heard the lonely. I drove a \index{carriage}carriage\footnote{Your carriage was opaque but not unintelligible, and it was discovered in an alleyway. (I found someone within, and my someone appeared guilty and innocent.)}. I saw others in a drunken \index{condition}condition\footnote{Your condition appeared extreme. It was in a plan.}. I saw an earwig or had one in my ear. I was seated on a \index{fence}fence\footnote{My fence was smart and impudent, and an apple tree was within them.} with others. I engaged in a \index{fight}fight\footnote{Someone was in our fight. A war. Dangerous. It was in a fighter pilot.}. I had \index{flux}flux\footnote{You said that my flux was mean.}. I saw a funeral. I looked into an empty \index{grave}grave\footnote{A corpse was within this grave. (A duty.) Our duty was seen in an airport.}. I ate \index{gravy}gravy\footnote{You saw my gravy in a dinner, and I found a utensil within. You told me your utensil was wooden, and it was singular but not odd. It was a fork but not a crotch.}. I made pets of them. I saw me dead. 

 I saw old. I itched. I saw others with \index{jaundice}jaundice. I fell from one. 

 I descended a \index{ladder}ladder\footnote{My ladder was important, and it was a stepladder. Your stepladder was seen in a hardware store.}. I saw any one lame. I saw my \index{lover}lover\footnote{You found a penis in my lover, and they were attractive. They were found in a bed.} taking laudanum through disappointment. I heard mocking \index{laughter}laughter\footnote{My laughter appeared contagious. A giggle. Our giggle was infectious but not infective. We saw it in a craven.}. I kept a ledger. I had \index{louse}lice\footnote{Our louse seemed small.} on my \index{body}body\footnote{This body was a mummy but not a mammy. You saw it in a grave. Grey. We found a graveyard in it.}. I saw. I lost it. I felt \index{melancholy}melancholy\footnote{Our melancholy appeared pleasant.} over any \index{event}event\footnote{An exercise. I found this exercise in a gym, and our gym seemed expressive. (A muscle builder was not in it.)}. I saw others \index{melancholy}melancholy\footnote{You said that our melancholy was not pleasant.}. I sent a \index{message}message\footnote{Our message was a mail but not a ring armor. This mail appeared open and closed. It did not appear important, and it was in a house. A window was within our house.}. 

 I saw animals in a mirror. 

 I lost \index{money}money. I saw others morose. I was stung by them. I was a \index{newspaper}newspaper\footnote{Light. A cartoon was within it. My cartoon was both representational and nonrepresentational. (It was found in a newspaper.)} \index{reporter}reporter\footnote{The reporter was not readable.}. I saw them out of their \index{sphere}sphere\footnote{Our sphere was round, and you said it was not a planet. (Our planet was round and pear-shaped.)}. I wrote an obituary. I consulted an \index{oculist}oculist. I smelt disgusting \index{odor}odors\footnote{I saw your odor in a dirty laundry.}. I saw an old \index{man}man\footnote{Our man was curious but not odd. They appeared strong, and you said they were a boy. They were in a love. (A person was in my love.)}. 

 I bought \index{orange}oranges\footnote{The orange was yellow. It was edible but not comestible, and it was in a carton.} at my \index{wife}wife\footnote{The wife was not important. (They appeared female.) I saw them in a despair.}'s \index{solicitation}solicitation. 

 I had \index{paint}paint\footnote{A mammoth was not in your paint. It seemed pretty, and it was in a wall. (You told me this wall was black, and you said it was a membrane.)} on my \index{clothing}clothing. I carried a parcel. I resorted to \index{patent}patent\footnote{The patent was discovered in a medicine chest.} \index{medicine}medicine\footnote{My medicine appeared dangerous. A medicine cabinet was within it, and we saw it in a cabinet.} in my \index{search}search\footnote{I found a search party in your search.} for \index{health}health\footnote{A bully. A spa was in it, and you saw the spa in a resort. It was red.}. 

 I was a pauper. I sought to use \index{poison}poison\footnote{A wine. I found it in a forest, and my forest appeared cool.} on others. I used \index{poison}poison\footnote{Your poison was seen in a chemistry lab, and it was a wine but not a vino.} on others. I was pregnant. I ate it. I saw a broken reaping \index{machine}machine\footnote{A bicycle. Your bicycle was discovered in a lab. (It appeared expensive and cheap, and it seemed hard.) I found someone within.}. 

 I climbed a steep rock. I lost them. 

 I heard the shrill startling \index{note}notes\footnote{My note was a protocol but not a communications protocol.} of the \index{screech-owl}screech-owl\footnote{This screech-owl was pure but not utter.}. I saw \index{shampooing}shampooing going on. I saw them dead. I was overcome with \index{smoke}smoke\footnote{You found my smoke in a smoke alarm.}. I drank \index{oyster}oyster\footnote{A pearl was within the oyster, and you saw it in an ocean.} soup made of sweet \index{milk}milk\footnote{The milk was seen in a container, and you found a heifer within. My heifer was yummy and luscious.}. I saw the \index{spirit}spirit\footnote{A doppelganger. It was in an imagination, and a soul was within your imagination.} of my \index{friend}friend\footnote{You told me our friend was insignificant. You found a comfort in them, and they were in a fraternity house.} floating in my \index{room}room\footnote{Your room was found in a home. Good. You found someone within. You said our someone was not a student. The student appeared fragile.}. I spit. 

 I wore \index{spur}spurs\footnote{We found a spurt in our spur.}. 

 I saw a broken or imperfect one. I saw others going down \index{stair}stairs\footnote{My stair was in a house, and you told me it was dark. (A staircase.) I found a stairwell in it.}. I was in a starving \index{condition}condition\footnote{We saw my condition in a plan, and an alcohol was within our plan. (You told me it was ripe.)}. I stole. I saw \index{stone}stone\footnote{A mammoth was within my stone, and my mammoth was in a museum.} masons at \index{work}work\footnote{Our work seemed hard and soft. (We found it in a desk.) You said it was not a public servant. We found an assignment in it.}. I passed down a \index{street}street\footnote{A dirt was not in this street. It was in a map. It looked dark, and it was grey and hoary. (It was not an avenue.)} and felt alarmed lest a \index{thug}thug\footnote{Our thug was in a street. A dirt was not in my street, and you said it was not an avenue.} \index{attack}attack\footnote{Our attack was seen in an attacker. This attacker was both safe and out.} me. I was a \index{street-poster}street-poster. I drove one. 

 I saw a \index{number}number\footnote{You said that your number was solid. It was not a zero, and the zero was seen in a space shuttle. You found a person there.} of \index{tent}tents\footnote{We found a stove in this tent. You said our stove was a grill, and this grill seemed hot. (It was seen in an oven.)}. I descended from one. I saw ticks crawling on my flesh. I was tortured. I lost treasures. I saw trophies. 

 I looked into one. 

 I made a \index{present}present\footnote{Your present was discovered in a presenter.} of one. I saw them conjuring the \index{weather}weather\footnote{Your weather was in a weather map, and we found a cloud there. It was hot. It was a rain but not a pelting.}. I wore a \index{wig}wig\footnote{Your wig was a dance but not a saltation, and our dance was in a dance floor. A person was not in it.}. I saw soiled. I saw others yawning.

\chapter{}

I abandoned my \index{sweetheart}sweetheart. 

 I had no \index{abode}abode. I returned to an \index{academy}academy after having finished there. 

 I was accused. I read the \index{figure}figures\footnote{I found a figure skate in my figure, and this figure skate was recreational but not amateur.}. I failed to read the \index{figure}figures\footnote{An octagon. A figure skate was in them.}. I saw an \index{arm}arm\footnote{We saw our arm in a sleeve, and our sleeve was a vest but not an undershirt. (An arm was within it.)} amputated. 

 I cried \index{baby}babies\footnote{The baby looked innocent, and they were an infant but not a baby. (This infant was both happy and unhappy.) A grenade was within them.}. I was defeated in the \index{game}game\footnote{Enjoyable. We found a rule within, and it appeared painful. It was in a casino.}. I ascended in a \index{balloon}balloon\footnote{You told me this balloon was rubber. I found an air there, and your air seemed flammable. It was discovered in a sky.}. I ate them. I tended a \index{bar}bar\footnote{Rough. (You saw it in a cell.) A cellar was in this cell.}. 

 I wandered in the \index{night}night\footnote{You said my night was an earwig. I found a sloth in it. It appeared dark and light, and it was in a bedroom.} barefoot with torn \index{garment}garments\footnote{I found a silk in your garment. It was in a garment bag. You said it was not a coat.}. I admired a beard. I saw one. 

 I was affected with \index{bronchitis}bronchitis\footnote{Your bronchitis was dangerous and grievous.}. I heard my \index{name}name\footnote{You saw the name in a wallet, and we found a dollar in them. Our dollar was fake but not bogus.} called by strange \index{voice}voices\footnote{You told me our voice was loud, and they were in a person. You said your person was an actor.}. I saw my \index{sweetheart}sweetheart with a \index{cap}cap\footnote{You told me this cap was sweet. It was in a captain, and you found someone in my captain.} on. I was in a \index{cold}cold\footnote{This cold was not unethical, and it was a reptile. It was in a refrigerator. A butter was within our refrigerator. It seemed white and black.}. I wandered through the silent avenues of the dead \index{foreshow}foreshows they will meet with tender and loving responses from \index{friend}friends\footnote{This friend looked important. (You said that they were selfish.) They were in a fraternity house. An alcohol was within your fraternity house.}. I saw my \index{coat-of-arms}coat-of-arms. I saw a \index{collision}collision. I was the \index{object}object\footnote{An object program was not in my object.} of a \index{conspiracy}conspiracy. 

 I saw many of the old patriarchs traveling on \index{donkey}donkeys\footnote{Alive.}. I fell or be thrown from one. I died. 

 I died. I was going to die. I saw a dead eagle killed by others than myself. I bought an emerald. I had made a \index{failure}failure\footnote{You told me your failure was catastrophic, and they were discovered in a casino. A roulette was within the casino.}. I had \index{fit}fits\footnote{A squash court was within our fit, and my squash court was found in a country club.}. I was defrauded. 

 I saw my \index{friend}friend\footnote{A tv set was not in your friend, and they looked important. They did not seem social. They were discovered in a door.} who dressed in somber \index{color}colors\footnote{I found a mountain in our color, and the mountain was big. You said it was an alp.} in flaming \index{red}red\footnote{You told me your red was color. I found a rifle in it. Our rifle appeared dangerous, and you found it in a war.}. I sent a \index{gift}gift\footnote{I found your gift in a party. I found a cake there. (They were expensive, and they appeared uncomfortable.)}. I made presents of cut \index{glass}glass\footnote{This glass did not seem pale blue. Transparent. We found an overflow in it. It was discovered in a window.} \index{ornament}ornaments\footnote{This ornament was found in a windowsill. (It was a bow but not an obeisance.) Your bow was yellow and yellowish.}. I looked clearly through a \index{glass}glass\footnote{My glass was pale blue but not light-blue, and you told me it was transparent. You saw it in a window, and an ice cube was within it.} \index{window}window\footnote{I saw my window in a store. Dark. We found a computer in it, and it was a shop but not a store.}. I saw my own grave. I saw brown \index{hair}hair\footnote{We found a bobby pin in the hair, and this bobby pin was seen in a beauty shop.}. I saw a detached hand. 

 I shot a \index{hare}hare\footnote{A harem. It appeared cool, and you told me it was flighty.}. I heard the sad sweet \index{strain}strains\footnote{The strain was not deadly, and you saw it in a jar. A food was within the jar.} of a harp. I saw them broken. 

 I was hungry. I was sleeping in a \index{hut}hut\footnote{A hutch was in our hut. Fragile.}. I saw \index{icicle}icicles\footnote{This icicle did not seem strange, and it seemed cold and hot.} on the \index{eave}eaves\footnote{Our eave was discovered in a roof. A solar panel was in your roof.} of \index{house}houses\footnote{You said my house was an igloo. Someone was not in the igloo. (It did not appear big.)}. 

 I was brought before an \index{inquisition}inquisition on a \index{charge}charge\footnote{A captain was not in your charge. My captain was indestructible.} of \index{wilfulness}wilfulness. 

 I was \index{intemperate}intemperate in the \index{use}use\footnote{You told me the use was uncontroversial, and I found it in a floor. A basketball court was within it.} of my intellectual \index{force}forces\footnote{You said my force was not a gravity. You told me it was relentless.}. I was invited to make a \index{visit}visit\footnote{I found someone in our visit, and your someone was in a lake. You told me it was guilty.}. I made a \index{visit}visit\footnote{My visit was in a front door. Someone was in it. You told me our someone was innocent.}. I saw a \index{jackdaw}jackdaw\footnote{This jackdaw was not weird.}. I saw heavy. I thought that \index{vegetation}vegetation\footnote{We saw the vegetation in a countryside.} was decaying. I thought my lover was lazy. I saw one caged. I saw a \index{lynx}lynx\footnote{This lynx was alive but not awake, and you told me it was shy.}. I saw a dilapidated \index{mill}mill\footnote{We found a millimeter within. Million. It was found in a barn.}. I saw a minister. I heard my \index{mother}mother\footnote{Our mother was a woman but not an adult female, and you told me they were female. (A kitten was within them.) Our kitten was not distinct. You found it in a farmhouse.} call me. I wore mourning. 

 I saw my \index{muscle}muscle\footnote{We found a pain there. I found them in a city.} well developed. I saw others in \index{need}need\footnote{Our need appeared small, and a needle was within it. It was a coat. It was discovered in a needle.}. I looked for a \index{needle}needle\footnote{You saw our needle in a haystack, and this haystack appeared big.}. 

 I went to deliver it. I let a \index{parcel}parcel\footnote{The parcel was discovered in a mail, and we found a bomb in it.} \index{fall}fall\footnote{Your fall was both colorful and colorless. It was fatal, and you found a fungus there. Your fungus was in a cave. (You said it was not a mushroom.)} on the way as I went to deliver it. I delivered it. I rung one myself. I bought one. I found my path. I was trying to find my \index{path}path\footnote{You said our path was a road, and the road was seen in a city. It was wonderful and terrific, and it seemed rural. A gas station was in it.}. I shot them. I saw others with \index{pimple}pimples\footnote{A zit. (You found it in a body.) Our body seemed popular and unpopular. A blood was within it.} on them. I felt \index{pincers}pincers on my \index{flesh}flesh\footnote{This flesh was in an inside. (Tasty.) A meat. You found a heifer in my meat, and the heifer was herbivorous.}. I saw a bent or rusty \index{pin}pin\footnote{A needle was in our pin. (Our needle was sharp.) We saw it in a haystack.}. I was looking into a deep \index{pit}pit\footnote{Your pit was discovered in a mine. The mine was hard, and you found a mineral in it.}. I attacked any person with one of these \index{weapon}weapons\footnote{A projectile was in your weapon, and your projectile was seen in a canon. The canon appeared unreliable and dependable. They were both dangerous and safe.}. I engaged in political wrangling. I saw a dead one. I was lost on one. I was a \index{preacher}preacher\footnote{Our preacher was in a cathedral. (They appeared creative.)}. I saw a \index{printer}printer\footnote{You said the printer was not a laser printer, and my laser printer seemed mechanical.}. I drank the \index{concoction}concoction called \index{punch}punch\footnote{You said that our punch was one. It was in a box. An uppercut.}. I was questioned. I gave a baby a \index{rattle}rattle. I was engaged in reading. I saw a \index{friend}friend\footnote{My friend was in a door. Important. (I found someone in them, and the someone seemed dangerous.)} killed in a \index{riot}riot\footnote{High. (It was found in a demonstration.) I found an activist within.}. I putted them on the \index{table}table\footnote{This table was not hazardous, and I found it in a kitchen. (Our kitchen was not a kitchen utensil.)}. I decended one. I saw \index{sheet}sheet\footnote{I found a sheet of paper there, and it was found in a bedroom. (It looked blank.)} \index{iron}iron\footnote{My iron was heavy, and you told me it was rough. It was in a chemistry lab.}. I was seeking \index{shelter}shelter\footnote{Your shelter was a hut but not a hutch, and you found someone there. (You said that it was not solid.)}. I was a skeleton. I was slighted. I ate \index{snow}snow\footnote{Our snow did not seem mild. It seemed wet, and we found a snowstorm in it. I found it in a winter.}. I was a \index{somnambulist}somnambulist. 

 I imagined that I was a somnambulist. I saw my soul leaving my \index{body}body\footnote{Beautiful. (You saw it in a grave.) You said this grave was a duty. Solid.}. I saw broken \index{spectacle}spectacles\footnote{My spectacle was discovered in a show. (You said our show was a concert.) It appeared heavy.}. I was visiting me stick a \index{splinter}splinter\footnote{My splinter was not mean.} in my \index{foot}foot\footnote{Fast. A boy was not in them. They were discovered in a desk. They were a boot.}. I stuck a \index{splinter}splinter\footnote{You said that my splinter was not mean.} in my \index{foot}foot\footnote{You said our foot was a sandal, and the sandal was discovered in a back door.}. I thought a \index{spoon}spoon\footnote{You said that the spoon was not wooden. It was in a kitchen, and we found a kettle there. It was small, and it was not a kitchen utensil.} was lost. I was a \index{spy}spy. I saw some \index{person}person\footnote{Endothermic. (You said it was a cousin.)} with squinting \index{eye}eyes\footnote{This eye appeared green. We saw it in a mammal. (A dolphin.) Your dolphin appeared distinct.}. I fell from one. I was walking in a \index{street}street\footnote{The street was outside but not out-of-door. It was a lane. You saw your lane in a road.}. I saw one \index{standing}standing or sitting on a \index{table}table\footnote{A desk. You said that it was hazardous. (A food was within it, and you told me it was contrasty.) We found it in a restaurant.}. I had the \index{tail}tail\footnote{I found a fabric in the tail. You said our fabric was not a textile. My textile appeared soft. It was discovered in a kitchen.} of a \index{beast}beast\footnote{The beast was creative but not originative, and a beast of burden.} grown on me. I payed my taxes. 

 I fell out. I saw or be in a \index{telegraph}telegraph\footnote{A stop was in your telegraph, and this stop was in a bathtub. It was good and skilful, and it seemed red.} office. I was in a \index{dispute}dispute about a text. I was in a \index{thunder}thunder\footnote{We saw my thunder in a sky. (It was spectacular.) A thunderstorm was not in it. Scary.} \index{shower}shower\footnote{This shower was wet, and I found a shower curtain in them. They were in a bathroom.}. 

 I saw others tipsy. I was toothless. I was torturing others. I ate \index{tripe}tripe\footnote{The tripe was strange.}. I saw a truss. I saw a \index{train}train\footnote{You saw this train in a railway, and it seemed noisy and quiet. (A train ticket was within it.)} coming towards me while in a \index{tunnel}tunnel\footnote{We found a weasel within.}. I passed through a tunnel in a \index{car}car\footnote{The car looked fast, and it was mechanical but not mechanically skillful. (It was a bus but not an autobus.) You found a driveway in it. You found your driveway in a neighborhood.}. I saw \index{tweezer}tweezers. I saw my \index{uncle}uncle\footnote{The uncle was discovered in a family, and they looked male. They were both fertile and sterile.}. I saw a United States mail \index{box}box\footnote{You said my box was a cart. Animate. (It was opaque and unintelligible, and it was in a refrigerator.) A butter was not in my refrigerator.}. I saw urine. 

 I was in \index{want}want\footnote{I found a kitten in your want. You found it in a newspaper.}. I failed to prove a will. 

 I proved a will. 

 I looked through a window when passing and strange \index{object}objects\footnote{A pen. Fuzzy. We found an object program in it.} appeared. I saw \index{writing}writing. I visited a yew \index{tree}tree\footnote{The tree was alive and awake. (Alive.) It was not a pine, and someone was within it. It was found in a forest.} and find it dead and stripped of its \index{foliage}foliage\footnote{We saw our foliage in a forest. Pretty.}.

\chapter{}

I saw my \index{abdomen}abdomen\footnote{A navel was in the abdomen. (My navel was discovered in an abdomen.)} shriveled. 

 I saw others abject. I had \index{account}accounts\footnote{Your account was in an account book, and it was both stupid and intelligent. We found a ledger there.} presented to me for payment. I saw a small \index{ape}ape\footnote{The ape was a human, and you said that the human was not pure. You told me it was selfish. We found it in a workplace, and a skin was in it.} cling to a \index{tree}tree\footnote{This tree appeared green. You told me it was ripe, and someone was within it. It was an evergreen but not an evergreen plant. This evergreen was in a forest.}. I saw a fallen \index{arch}arch\footnote{My arch was powerful but not knock-down. You told me it was dangerous. It was in a build. A terrace was within it.}. I unwillinglied \index{ride}ride\footnote{Our ride was in a car. A driveway was not in our car.} on one. I went in \index{bathing}bathing with others. 

 I was blindfolded. I rode in a \index{cab}cab\footnote{The cab looked last and first. It was a cable but not a cable's length. Our cable was important. I found someone in it. (You found your someone in a hospital.)} at night. I carved a fowl. I heard the \index{scream}scream\footnote{A work of art, and this work of art was in a bus stop.} or the \index{mewing}mewing of a \index{cat}cat\footnote{Cute. They were not a lynx, and my lynx was strange and unusual.}. I entered a \index{chapel}chapel\footnote{A ceiling was within my chapel, and it was seen in a priest. It was strange but not unknown, and it was useless.}. 

 I gave charity. 

 I drank claret. I saw the \index{corpse}corpse\footnote{Your corpse was seen in a coffin.} of an animal. I saw a \index{crew}crew\footnote{This crew was found in a space shuttle.} working to save a \index{ship}ship\footnote{Your ship looked safe. It was not a junk. We found a life preserver in it. (The life preserver was seen in a lifeboat.)} in a storm. I saved a \index{ship}ship\footnote{Your ship was safe, and it was a junk but not a debris. You found it in a shipwreck. You found a cargo there.} in a \index{storm}storm\footnote{My storm was a thunderstorm but not an electric storm, and it did not appear hot. (It appeared dangerous and safe.) It was in an atmosphere.}. I saw a \index{crow}crow\footnote{I found someone in our crow. Dangerous. (You told me it was guilty, and it was seen in a lake.)}. I was on \index{dock}docks\footnote{I found a hoist within, and this hoist was in a boathouse. You said that our boathouse was not solid.}. I saw \index{animal}animals\footnote{My animal was cute. It was found in a cafe. (It was a mouse but not a shiner, and we found a button there.)} in the \index{thro}throes\footnote{You said our thro was not a baseball player. My baseball player was in a plate. (They were mortal but not deadly.)} of death. I saw my \index{foot}feet\footnote{This foot was seen in a shoe. You found an arch in our shoe. A boot. Our boot appeared black and white.} swollen and red. I found myself in a dense forest. 

 I was on a \index{gallows}gallows\footnote{The gallows was cold.}. I visited a newly made \index{grave}grave\footnote{My grave was grey. We saw it in an epitaph. A casket was not in it. It was a duty but not a tariff.}. 

 I lost one. 

 I saw a broken harp. I was a hypocrite. I demanded \index{justice}justice\footnote{Strange. They appeared blind and sighted.} from a \index{person}person\footnote{The person was seen in a conference, and you found a liver there. You told me it was stupid, and it was a cousin but not a cousin-german. It was individualist and individualistic.}. I saw the \index{kite}kite\footnote{You told me your kite was black. (It did not appear silly, and I found a string there.) It was in an air.} thrown upon the \index{ground}ground\footnote{We found someone within. A student. Mean. They appeared tough, and you saw them in a university.}. I had a wooden \index{leg}leg\footnote{You told me my leg was fragile. A muscle was in it. I saw it in a table. (A desk.) You said that it was hazardous.}. I repeated the Lord's Prayer. I lost my \index{luggage}luggage\footnote{You found a garment bag there, and it was found in a bus depot.}. I saw \index{mosquito}mosquitoes\footnote{The mosquito was found in an air, and it was bad but not spoilt.}. I was murdered. 

 I saw \index{mushroom}mushrooms\footnote{Your mushroom appeared yummy, and a fungus was not in it. (It was not edible.) You saw it in a lawn. This lawn was a lawn chair but not a garden chair.}. I had a \index{mustache}mustache. I saw a dead \index{owl}owl\footnote{The owl was stupid and dazed. You told me it was diurnal, and we found it in an air.}. I saw an \index{owl}owl\footnote{Your owl appeared nocturnal and diurnal, and it was not strange. It was in an air.}. I saw beautiful \index{painting}paintings. I saw others thus worried. 

 I put in a \index{window-pane}window-pane with \index{putty}putty\footnote{This putty did not appear heavy.}. 

 I took \index{quack}quack \index{medicine}medicine\footnote{We found a medicine cabinet there.}. I attended a riding \index{school}school\footnote{This school was in a neighborhood, and a driveway was not in your neighborhood.}. I had a loaded candle and find it empty. 

 I imagined that I had a loaded \index{candle}candle\footnote{An egg. (You told me it was romantic, and it was seen in a birthday cake.) I found a light source within.} and find it empty. I slept on one. I had seduced a \index{girl}girl\footnote{This girl was in a library. They were vain, and you said they were not a niece. A doll was within them. Our doll was color but not colour.}. I slept in unnatural resting \index{place}places\footnote{You said my place was a jail. We found a convict within. My convict was in a prison.}. I saw people with \index{smallpox}smallpox\footnote{The smallpox was deadly but not pestilent, and you told me it was contagious.}. I was a \index{stone}stone\footnote{A granite. Our granite seemed cold and hot.} \index{mason}mason\footnote{A lizard was in our mason. (My lizard was strange but not unusual.)}. I spilt \index{tea}tea\footnote{My tea was found in a classroom, and it was bad and speculative. A tear was not in it, and you told me your tear was glad.}. I saw them flying. I saw one \index{torn}torn\footnote{I found the torn in a tornado. (You said that my tornado was not hot, and a projectile was in it.) You said your projectile was a bullet, and you told me the bullet was square.} to \index{piece}pieces\footnote{This piece appeared black. You found it in a puzzle, and a piece was not in our puzzle.}. 

 I dropped the \index{crystal}crystal\footnote{A quartz. A drug dealer was not in it.} of one. I was in the \index{bond}bonds\footnote{Our bond looked strong. A love. I saw the love in a marriage.} of an unwelcome \index{wedlock}wedlock. I received a warm \index{welcome}welcome\footnote{You said my welcome was not a change, and it was discovered in a welcome mat.} into any \index{society}society\footnote{You said the society was not a coffee. A person was in it. (We saw it in a person, and it was ill.)}. I was caught in a \index{whirlwind}whirlwind\footnote{The whirlwind did not appear human.} and had \index{trouble}trouble\footnote{You found your trouble in a roadblock. A police car was not in your roadblock.} to keep my \index{skirt}skirts\footnote{My skirt seemed blue. (You said they were a dress.) We found a linen in your dress. The linen was found in a cabinet.} from blowing up and entangling my \index{waist}waist. I kept my \index{skirt}skirts\footnote{This skirt was both square and round. A dress. They were discovered in a suitcase, and a shirt was within this suitcase.} from blowing up and entangling my \index{waist}waist.

\chapter{}

I abandoned others. I felt ashamed of meeting an \index{acquaintance}acquaintance. I overcame an adversary. I dreamt that \index{friend}friends\footnote{You told me your friend was important. (They were in a fraternity house, and someone was within them.) You said that they were not warm-blooded.} or relatives was angry with me. I went bail for another. I saw John the Baptist baptizing Christ in the Jordan. I destroyed them. I saw. 

 I heard \index{bell}bells\footnote{You said your bell was not a chime, and this chime was in a roof.} tolling. I saw \index{blood}blood\footnote{Red. A drop was not in them, and they were seen in a person. You said my person was not a student. My student was creative and originative.} flowing from a \index{wound}wound\footnote{A bullet was in this wound. Our bullet was weird and uncanny. It appeared round. A bulletin. It was found in a war.}. I used blotting paper. I saw my own \index{brain}brain\footnote{We found an illness in my brain, and you said that it was not dangerous. (It was discovered in a skull, and you said this skull was a craniotomy.)}. 

 I broke a \index{window}window\footnote{We found a lizard in the window, and you said the lizard was not a skink. You said that this skink was scaly, and it was discovered in a forest.}. I saw them slaughtering cattle and much \index{blood}blood\footnote{A blood vessel was in this blood, and they were in an artery.}. I saw \index{canker}canker on anything. I met a thin. I saw a \index{cellar}cellar\footnote{This cellar was both expensive and cheap. It appeared dark and light, and it was found in a castle. You found a furnace in it.} stored with \index{wine}wines\footnote{You told me the wine was tasteless. I saw it in a winery. A cellar was within the winery. It did not appear terrible.} and \index{table}table\footnote{You said your table was not a desk, and a notebook was in the desk. It was opaque. (Small.) It was in a library.} \index{store}stores\footnote{You found this store in a street, and your street was outside but not outdoor. (It was a boulevard but not an avenue, and a bicycle was in it.) You told me it was dark.}. 

 I gave \index{charity}charity\footnote{Admirable. (We found someone within.) The someone was discovered in a theater.}. I played chess. I was going down a \index{chimney}chimney\footnote{The chimney was in a roof. This roof seemed dirty.}. I saw a \index{church}church\footnote{This church was seen in a city, and you told me it was noisy. A human was within it, and our human was a woman but not a char. The woman was not monogamous.} in the \index{distance}distance. I was a clairvoyant and seeing myself in the \index{future}future\footnote{You found a tomorrow in our future, and you found our tomorrow in a future.}. I visited a clairvoyant. I had plenty. I saw a coffee \index{mill}mill\footnote{We saw our mill in a farmyard. I found a cow in my farmyard.}. I saw a \index{corkscrew}corkscrew\footnote{Your corkscrew was discovered in a drawer, and it was mean and average.}. 

 I heard the \index{cry}cries\footnote{Your cry was found in a funeral. (It seemed bad.) We found someone in it.} of wild \index{beast}beasts\footnote{The beast was illegal, and they seemed weird. A beast of burden.}. 

 I cried. I leaved one. I saw me at \index{work}work\footnote{Our work was hard. It was in a school. You found a student there. The student was a college student. They appeared weird.} on a young \index{woman}woman\footnote{A pantie was within this woman, and this pantie was discovered in a suitcase. My suitcase was large and declamatory.}'s \index{tooth}teeth\footnote{We saw my tooth in a plate, and it looked white. A toothpaste was not in it.}. I saw others in despair. I ate my \index{dinner}dinner\footnote{A spoon was not in my dinner. It was not edible, and it was seen in a cabinet. It looked fresh. It was not a cereal.} alone. I saw my clothes soiled with unclean dirt. I drove a \index{donkey}donkey\footnote{The donkey did not seem competitive.}. I was bored with the \index{performance}performance\footnote{You told me your performance was good. We found a human within. It was seen in a show, and your show was a sitcom.} of a \index{drama}drama\footnote{Your drama was both human and nonhuman. A coincidence was not in it. (Your coincidence was found in a drama.)}. 

 I was dumb. I saw \index{elbow}elbows\footnote{I saw your elbow in an elbow pad.}. I flew over broken \index{place}places\footnote{You found your place in a dark. (Beautiful.) A fungus was within it. My fungus was a mushroom but not a mushroom-shaped cloud.}. I attacked a \index{fort}fort\footnote{Our fort was in a bank, and my bank appeared competitive. You found a dollar in it, and it was not a credit union.} and take it. I saw the \index{ghost}ghost\footnote{This ghost was peaceful. A spook. They were in a cellar.} of a dead \index{friend}friend\footnote{Your friend was in a fraternity house, and a men was not in this fraternity house. Our men was both warm-blooded and cold-blooded.}. I heard the \index{sound}sound\footnote{This sound was a music. I found a microphone boom within. You found your microphone boom in a concert. (Good.) It seemed loud.} of a \index{gong}gong\footnote{My gong was discovered in a museum.}. I saw \index{gooseberry}gooseberries\footnote{The gooseberry was in a jar.}. I had my \index{hair}hair\footnote{A hairpin was in the hair, and our hairpin was in a hair. Blond. It was an eyebrow but not a brow, and it was both possible and actual.} \index{cut}cut\footnote{Your cut was in a restaurant, and you said our restaurant was not a pizza parlor. We found someone there, and you told me this someone was guilty. (It was hard.)}. I ate the \index{heart}heart\footnote{You found a human there. You told me our human was monogamous. It was in a bathroom. You said it was a police officer.} of a \index{chicken}chicken\footnote{The chicken was edible, and they were not unhealthy. We found a chicken coop in them.}. I heard the roar and see a \index{hurricane}hurricane\footnote{You told me my hurricane was dangerous. It was discovered in a sea. Scary.} heading towards me with its frightful \index{force}force\footnote{You said the force was not a gravity, and you told me it was relentless.}. I was in a \index{house}house\footnote{The house was found in a residential area. You told me it was white. We found a carpet in it.} which was being blown to \index{piece}pieces\footnote{We found a piece of paper there. It was black. (It was discovered in a puzzle, and our puzzle was empty and hollow.) You said it was a cryptogram.} by a \index{hurricane}hurricane\footnote{We found the hurricane in a sea, and I found someone within. A seafood.}. I saw a \index{hyena}hyena\footnote{The hyena did not appear hairy.}. 

 I made \index{ice}ice\footnote{A flower. It was in a grocery store. Frigid. We found an icebox within.}. I was leading an idle existence. I was insane. I used \index{invective}invectives. I saw red-hot \index{iron}iron\footnote{Shiny. It was in a house. Magnetic.}. I saw broken \index{jar}jars\footnote{My jar was found in a pantry. A dish was not in my pantry.}. 

 I saw \index{ballet}ballet\footnote{Your ballet was in a theater. Romantic. A dancer was within it.} \index{girl}girls\footnote{The girl was hot and raging. They were not a niece. (Someone was not in them, and they appeared female and androgynous.) We found them in a school.} dancing a \index{jig}jig\footnote{You found a jigsaw in this jig, and the jigsaw was in a table. It was creative and originative.}. I appeared before the \index{judgment}judgment \index{bar}bar\footnote{A vodka was within this bar. You found this vodka in a cabinet, and it seemed colourless.} and heard the verdict of ` ` Guilty. I killed a defenseless \index{man}man\footnote{Our man seemed intelligent. They were not a boy. (A mouse was in our boy, and you told me they were different.) They were seen in a football game.}. I kissed illicitly. I used a \index{knocker}knocker. I saw a broken ladder. I saw them in a \index{winter}winter\footnote{A wintertime was within our winter. Cold. It was not a hockey. You found it in a drawer. My drawer was dark and dismal.} \index{storm}storm\footnote{Your storm was cold and stale, and you said it was a hurricane. You saw my hurricane in a sea, and your sea appeared salty and fresh.}. I felt lazy. 

 I melted \index{lead}lead\footnote{You found your lead in an electronic equipment. They appeared dense, and they were ductile and pliable.}. I was lending \index{money}money\footnote{My money looked mutual, and you found a home there. It was not a dollar. The dollar appeared fake. It was seen in a pocket.}. I bought \index{liquor}liquor\footnote{Our liquor was found in a pub, and it was a vodka. I found a bottle in this vodka. It looked colourless and colourful, and it was alcoholic but not alcohol-dependent.}. I saw ugly-mannered \index{person}persons\footnote{Distinct. You told me it was weird. You found it in a hospital. It was an astronaut.}. I made it. I saw a \index{midwife}midwife\footnote{Your midwife was competitive but not competitory.}. I was in a \index{mine}mine\footnote{You saw the mine in a metal. This metal did not seem enjoyable, and a brass was not in it. You said it was not a steel, and you told me your steel was impotent.}. I visited a \index{morgue}morgue\footnote{I found a corpse there. My corpse was found in a war, and our war looked terrible.} searching for some \index{one}one\footnote{You found someone there. This someone was both hard and easy. (It was discovered in a pool.) It seemed guilty and innocent. You said it was a criminal.}. I saw a \index{mouse-trap}mouse-trap. I saw \index{murder}murder\footnote{I saw this murder in a murderer, and this murderer was dangerous. They appeared stupid. They were a hitman.} committed. I saw rusty or broken \index{nail}nails\footnote{Someone was within the nail, and I found it in a jar. Large.}. I saw one nude. I played \index{ninepin}ninepins. I handled a \index{pane}pane of \index{glass}glass\footnote{I found our glass in a cabinet. Clear. An ice cube was within it, and my ice cube was both powerful and powerless.}. I heard the \index{voice}voice\footnote{Our voice was in a radio. We found someone in the radio.} of a panther. I inhaled the \index{odor}odor\footnote{You found this odor in an air.} of a \index{pole-cat}pole-cat on my \index{clothe}clothes\footnote{A tweed was not in our clothe. You said it was not a jacket. It was in a hamper.}. 

 I saw a pond. I saw a poor-house. I said \index{prayer}prayers\footnote{Your prayer was seen in a confession, and you told me they were effective. You found someone in them.}. I saw a broken \index{rake}rake\footnote{Our rake was in a garage. A mouse was not in this garage. Cute.}. 

 I was being carried over \index{rapid}rapids\footnote{We saw our rapid in a waterfall. Someone was within it. You said that it was not noisy, and you said it was not a tachycardia.}. I imagined that I was being carried over \index{rapid}rapids\footnote{This rapid was not a tachycardia. Deadly.}. I saw my \index{sweetheart}sweetheart with a \index{revolver}revolver\footnote{The revolver did not seem harmful. (Dangerous.) It was in a holster. I found a gun within.}. I had a \index{rival}rival\footnote{This rival was both safe and dangerous.}. I saw them falling. I imagined that one \index{haunt}haunts\footnote{A spirit was within the haunt.} me. I saw wounded soldiers. I climbed a \index{steeple}steeple\footnote{You said that my steeple was beautiful.}. I saw my \index{stocking}stockings ragged. I threw a \index{pebble}pebble\footnote{Your pebble was in a lake. Murky.} or \index{stone}stone\footnote{You saw our stone in a bridge. A homeless was within our bridge, and you said your homeless was not a homelessness.} at some belligerent \index{person}person\footnote{We saw our person in a bus stop. A cousin. Your cousin was creative but not originative.}. I saw or hear others committing this \index{deed}deed\footnote{Our deed was weird and unearthly.}. 

 I saw others in \index{terror}terror\footnote{This terror was fragile, and you found them in a terrorist. (They were bad, and you said they were not a terrorism.) I found a bomb there.}. I was pursued by \index{officer}officers\footnote{You said your officer was not a mayor. My mayor was in a town hall, and they seemed corrupt.}. 

 I was a \index{thief}thief\footnote{You told me this thief was safe. They did not appear violent, and they were a con artist but not a confidence man. We found them in a store.} and that I was pursued by officers. I used an open \index{end}end\footnote{Someone was within this end. Guilty. It was in a hospital.} \index{thimble}thimble\footnote{Your thimble was discovered in a cabinet.}. I saw a \index{tunnel}tunnel\footnote{We found a passageway in our tunnel, and you said your passageway was a door. (It was in a cave.) Underground.} \index{caving}caving in. I lent one. I received one. I heard weeping voices. I vomited a \index{chicken}chicken\footnote{This chicken was a hen but not a biddy. They were both unhealthy and healthy. You told me they were delicious. You found an egg in them. You saw my egg in a henhouse.}. I made a \index{wager}wager. I lost a \index{wager}wager. I saw a \index{wagtail}wagtail\footnote{The wagtail was both alive and unanimated.}. I blew them out. I married a widow. I was running about wild.

\chapter{}

I got into an abbey. 

 I saw an \index{abbess}abbess. I was a \index{party}party\footnote{You told me this party was comfortable, and they appeared enjoyable. We found a human there, and your human was discovered in a home.} to an \index{abortion}abortion\footnote{My abortion was in a clinic, and you said that our clinic was educational.}. I saw \index{woman}women\footnote{Our woman was a mother but not a female parent, and you said that they were sensitive. They were pretty. (You found a bobby pin in them.) My bobby pin was in a hair.} acrobating. I committed \index{adultery}adultery. I was afraid to proceed with some \index{affair}affair\footnote{We found the affair in a work.}. I felt that I was afraid to proceed with some affair. 

 I proceeded with some \index{affair}affair\footnote{This affair was in a work.}. I was accused of being older than I was. I was sleeping in an \index{attic}attic\footnote{Your attic was claustrophobic. (An antique was within it, and a skeleton key.) They were in a piece of paper.}. I made sad adieus on a \index{balcony}balcony\footnote{Safe. We saw it in a house. Your house was big but not vainglorious. A wall was within it, and my wall was a membrane but not a tissue layer.}. I saw inharmonious \index{influence}influences. I was in a \index{basement}basement\footnote{This basement was a first floor. I saw our first floor in a build. (I found a ceiling within, and you told me our ceiling was vertical.)}. 

 I pulled my beard. 

 I did not like my \index{bed}bed\footnote{This bed was in a bedroom. (A kitten was in it, and it was a cot but not a crib.) Our cot seemed flexible. You told me it was comfortable.} \index{fellow}fellow\footnote{You said our fellow was not a shipmate.}. I saw \index{anything}anything\footnote{A matter. The matter was in a universe, and you found a molecule there.} moving on the \index{belly}belly\footnote{You found a bellybutton in my belly, and my bellybutton was not pure.}. I saw \index{writing}writing in white chalk on a \index{blackboard}blackboard\footnote{You saw our blackboard in a school, and you said my school was a university. We found a girl in it, and our girl seemed bad and good.}. I used a hair-brush. I saw one pursuing me. I sold \index{butter}butter\footnote{A stick was in your butter. They were good and well, and they were in a pastry. This pastry was a cake but not a bar. (Sweet.)}. I snuffed a \index{candle}candle\footnote{My candle looked romantic. An egg. A light source was in it, and we saw my light source in a house.}. 

 I rode in a cart. I saw \index{cattle}cattle\footnote{My cattle was pure but not staring. You saw it in a fairground. You found a carnival within.} lean and shaggy. I used chalk on a \index{board}board\footnote{Our board was in a garage, and we found a garden hose in the garage.}. I saw me in the \index{temple}temple\footnote{I found someone in your temple, and it was seen in a city.} scourging the \index{trader}traders\footnote{My trader was fragile but not flimsy.}. I saw them with the \index{star}stars\footnote{A billion was not in the star. Evil. (You said it was a billionaire.) We found it in an existence.} shining. I saw or being commanded by a \index{colonel}colonel\footnote{The colonel appeared stupid.}. I was in a \index{coal-mine}coal-mine or \index{colliery}colliery and seeing \index{miner}miners\footnote{We found a molecule in your miner, and you said your molecule was not an ozone. (It was found in a substance.)}. I saw a \index{wife}wife\footnote{We found the wife in a marriage. The marriage looked sacred and profane, and you said it was not a same-sex marriage. A love was not in it.} or \index{husband}husband\footnote{Faithful. I saw them in a marriage.}. I saw hypnotic and \index{slight-of-hand}slight-of-hand performances. I saw a cooling board in my dreams. I reclined on a couch. 

 I saw them. I saw a \index{cross}cross\footnote{This cross was round. It was in a crosswalk.}. I saw a \index{hypnotist}hypnotist trying to hypnotize others. I hypnotized others. 

 I saw a dining-room furnished in \index{crystal}crystal\footnote{A chemical was within your crystal, and you told me it was opaque. You said it was a quartz.}. I saw my mother. I was in \index{despair}despair\footnote{I found a wife in our despair. You found it in a casino.}. I was diseased. I saw a divining \index{rod}rod\footnote{The rod was both warm and cool. It was a wand but not a scepter.}. I heard or ring a \index{door}door\footnote{You found your door in a house, and you found a window within. You said that it was not good. You said it was not a home, and you told me this home was uncomfortable.} \index{bell}bell\footnote{I found your bell in a front door. (You found a door within, and this door was an entrance but not an entry.) Rectangular.}. I saw others dying. I ascended in an elevator. I saw \index{embalming}embalming in process. I was under the \index{spell}spell\footnote{My spell was not a store. This store was large. It was in a city.} of \index{enchantment}enchantment. I saw \index{star}stars\footnote{You told me my star was beautiful. We found them in a space, and you said they were a red giant. Your red giant did not seem small.} shining out clear. 

 I lost an \index{eye}eye\footnote{You said the eye was not an eyeliner. (It looked green and ripe, and an eye socket was in it.) We saw it in a mammal.}. 

 I saw a one-eyed \index{man}man\footnote{You saw my man in a bedroom, and you told me our bedroom was round. (It was rectangular but not orthogonal, and a mirror was in it.)}. I felt fatigued. 

 I saw \index{chicken}chicken\footnote{You saw the chicken in a plate. (A beef was within our plate.) Important. Delicious.} \index{feather}feathers\footnote{I saw this feather in a cap, and you told me the cap was tasty. A captivity was not in it.}. I was feeble. I saw my \index{finger}fingers\footnote{The finger was messy, and I found a blister within. It was discovered in a finger bowl.} soiled or scratched. I caught a catfish. I saw a flying \index{machine}machine\footnote{Your machine was strong. (A machinery was within them.)}. I traveled through a dense \index{fog}fog\footnote{You saw this fog in a sea. The sea was blue.}. I saw \index{frog}frogs\footnote{Our frog was seen in a beach. (It was slimy, and it seemed green.) We found a gut there.} in low marshy \index{place}places\footnote{We found an anemone within, and we saw it in a city.}. I saw \index{fruit}fruit\footnote{The fruit was discovered in an orchard. A banana. I found a skin there, and the skin looked dangerous and safe.} ripening among its \index{foliage}foliage\footnote{Our foliage was seen in a forest. Cool.}. I ate green \index{fruit}fruit\footnote{A skin was within your fruit, and it was in a basket. It was a strawberry but not a strawberry mark, and the strawberry was nutritious.}. I saw \index{gleaner}gleaners at \index{work}work\footnote{Your work was a public servant. A paperwork was within it, and this paperwork was in an office.} at \index{harvest}harvest\footnote{The harvest was found in an oil. Your oil seemed opaque and clear.} \index{time}time\footnote{You found a confetti there, and we saw your confetti in a city.}. I was interested in common \index{gossip}gossip\footnote{Your gossip was a talk but not a talk of the town, and the talk seemed cheap and expensive.}. I was in my \index{nightgown}nightgown\footnote{You found a silk within. Your silk was weak and light. It appeared soft. You said it was not a foulard. It was in a tie.}. I returned for a corpse. I was shot. 

 I was thinning my \index{hair}hair\footnote{An eyebrow. (It did not seem possible, and we found a hair gel within.) You found it in a mammal. You told me it was thin.}. I had my \index{hair}hair\footnote{My hair looked blond and brunet. A shampoo was not in it. An eyebrow. (Flammable.) It was in a drain.} colored. I found myself handcuffed. I blew my hat off. I was oppressed by \index{heat}heat\footnote{We saw your heat in a fridge. We found someone in it, and your someone looked guilty.}. I saw a wounded \index{horse}horse\footnote{You said your horse was not a mustang. We saw it in a parade. Someone was in it. (Fast.) It was both cool and warm.}. 

 I mounted a horse bareback. 

 I saw me pale and careworn. I walked on \index{ice}ice\footnote{Your ice was transparent, and it was discovered in a grocery store. It was a water ice. It was pale blue but not light-blue, and you found an ice cream within.}. I saw \index{icicle}icicles\footnote{This icicle seemed cold, and it was creative and originative.} falling from \index{tree}trees\footnote{A leaf was not in this tree, and you told me my leaf was ripe. (It was seen in a compost pile.)}. I saw my \index{friend}friends\footnote{The friend was not curious. You told me they were noncrucial, and we found a tv set there. You saw your tv set in a house.} in \index{idleness}idleness. I saw the heavens illuminated. I saw \index{imp}imps\footnote{A bathroom. I found an impasse there.}. I came into the \index{possession}possession\footnote{You found a shark there.} of my income. I supported me. I was at a dilapidated and \index{ill}ill\footnote{We found an illness in the ill. (Delightful.) It was in a stomach, and it was pretty. An illness.} kept inn. 

 I intermarried. I was pierced by a \index{javelin}javelin\footnote{My javelin was not strange.}. I ate. I kissed a \index{person}person on the \index{neck}neck\footnote{You said your neck was not a choker, and our choker was discovered in a kennel.}. 

 I was in a labyrinth of \index{night}night\footnote{Our night was scary, and it was found in a bed. We found a nightclub in it.} or \index{darkness}darkness\footnote{Your darkness was seen in a movie. You said the movie was a thriller, and it was not fictional. It seemed excellent. An audience was in it.}. I bought \index{lace}lace\footnote{You told me this lace was white.}. I dropped a lighted \index{lamp}lamp\footnote{The lamp was in a table. Our table was rigid. (Hazardous.) You said it was not a desk. We found a food in it.}. I made wrong \index{entry}entries\footnote{This entry was alphabetical, and it was in an entryway. It was an entryway but not an entree. Small. You found a foyer there.} on my \index{ledger}ledger\footnote{We saw the ledger in a desk, and it appeared light.}. I saw them applied to others. I had \index{lodger}lodgers. I saw an idle \index{loom}loom. 

 I was mad. I was wearing a mask. I let them escape me. I saw a broken \index{mirror}mirror\footnote{A mirror image. It was in a wall, and it was reflective. We found someone in it.}. I saw a monk. 

 I found myself morose. I saw mortified \index{flesh}flesh\footnote{We saw my flesh in an inside, and you said this inside was a city. (I found a school in our city.)}. I found myself bewildered by some mysterious \index{event}event\footnote{I found someone within. You said it was a party. (You told me it was transient.)}. 

 I admired the neck of another. I saw my \index{neighbor}neighbors\footnote{You told me this neighbor was friendly, and a grocery store was within them. (They were discovered in a house, and you said the house was a basement.) The basement was not white.}. I unwillinglied see them. I was attacked with this hideous \index{sensation}sensation\footnote{Your sensation was transient but not short-lived. A hunger.}. I was on \index{shore}shore\footnote{You told me my shore was peaceful. (It was in an ocean.) We found a shoreline in it.} and see the waves of the \index{ocean}ocean\footnote{You saw this ocean in a beach. (It looked wet and dry, and a lobster was within it.)} \index{foaming}foaming against each other. I held \index{office}office\footnote{A cubicle was within my office, and the cubicle was in a corporation.}. I saw a \index{page}page\footnote{A title was within our page. You found our title in a magazine article, and you said that your magazine article was not useless.}. I was endeavoring to gain pardon for an \index{offense}offense which I never committed. 

 I gained pardon for an \index{offense}offense which I never committed. I neverred committed. 

 I went to a \index{pawn-shop}pawn-shop. I cracked and the \index{fruit}fruit was small. I lost them. I was worried over a \index{pest}pest\footnote{We found a mortar there. They were strange and foreign. (They were a mouse but not a shiner, and I found them in a jar.)} of any \index{nature}nature\footnote{A fruit. (I found a skin in your fruit, and it was in a market.)}. I was having my own photograph made. I saw an old-fashioned piano. 

 I saw a red hot \index{poker}poker\footnote{Popular. I found a person in it, and this person was seen in a theater.}. I played at \index{poker}poker\footnote{A person was in your poker. We found it in a casino.}. I imagined myself a \index{porter}porter\footnote{The porter was in a hotel.}. I saw a \index{prize}prize\footnote{A trophy. I found a gazelle in your trophy. You told me it was first, and it was seen in a cabinet.} fight. I was in a quarry and seeing the \index{workman}workmen busy. 

 I saw it raining on farm \index{stock}stock\footnote{A stockyard was within our stock.}. I saw or eat \index{roast}roast\footnote{You found our roast in a demonstration. Chicken.}. I saw a \index{rosebush}rosebush\footnote{My rosebush was found in a flower garden.} in \index{foliage}foliage\footnote{You said our foliage was a perennial, and it was in a forest.} but no blossoms. I found a safe \index{empty}empty\footnote{This empty looked full and empty, and we found a mouse in it. You found our mouse in a computer.}. I shook \index{hand}hands\footnote{The hand was in a house, and you told me they were dangerous. A finger was in them.} with a decrepit old man. I slighted any \index{person}person\footnote{My person was individualist, and we found a heart within. Your heart was in a hospital. It seemed mortal and immortal, and you said it was not a heart attack.} or friend. I saw or step on \index{snake}snakes\footnote{We found a mouse there, and this mouse was destructive. They were cool and nerveless. They were in a hole.} while wading or \index{bathing}bathing. 

 I saw my soul in another. I saw others with them on. 

 I killed a \index{squirrel}squirrel\footnote{Endothermic. It was in a countryside. (You told me my countryside was beautiful.)}. I saw \index{stain}stain\footnote{The stain was seen in a rug, and you told me it was nontoxic.} on my \index{hand}hands\footnote{This hand seemed subjective and transeunt, and we found a briefcase within. Your briefcase was in a business office.}. I walked among rocks. I saw and heard a \index{storm}storm\footnote{A thunderstorm. You said that it was unavoidable, and you told me it was dangerous. It was in a summer.} approaching. I committed \index{suicide}suicide\footnote{This suicide was tragic, and you said they were not an explosion.}. I cleared away the \index{table}table\footnote{Small. A desk. It was discovered in a conference, and I found a food in it.}. I saw \index{tassel}tassels\footnote{Our tassel was pure.}. I was brewing \index{tea}tea\footnote{The tea was in a teacher, and it did not appear liquid. (You said it was a black tea, and it was hot.) You found a tear there.}. 

 I killed a \index{toad}toad\footnote{A toadstool. You said that it was not slimy. It was found in a garden. You told me this garden was nice.}. I saw one \index{spinning}spinning. I was a \index{tourist}tourist\footnote{Our tourist was seen in a waterfall. (A hotel was within them.) Your hotel did not seem educational, and it seemed noisy and quiet. You said it was a motel.}. I saw a \index{tower}tower\footnote{Our tower was seen in a city. Dark. (It was tall, and someone was within it.) Our someone was a criminal but not a malefactor.}. I cut one down. I saw them sick. I ate \index{turnip}turnip\footnote{Our turnip appeared green, and we saw it in a refrigerator.} \index{green}greens\footnote{You told me the green was crispy, and a greenhouse was in it. You said that it was green, and it was in a grocery store.}. I saw \index{twine}twine. I carried an umbrella. I saw my \index{uncle}uncle\footnote{My uncle was seen in a family. Male. They were both male and female.} prostrated in \index{mind}mind\footnote{The mind was fragile, and we found a fatigue there. They were not a fundamentalism.}. I was unknown. 

 I felt that I was unknown. 

 I was thrown from one. I saw mourning \index{veil}veils\footnote{Your veil was stupid but not dazed.}. I saw others indulging in vice. I visited me. 

 I demolished one. 

 I heard a whistle. I scaped by one. I visited zoological \index{garden}gardens\footnote{The garden was not a lawn. Nice. It was found in a plant. We found a mouse in it.}.

\chapter{}

I abandoned. I saw \index{anything}anything\footnote{You told me the anything was infinite, and we found a sentence in it. (A finance.) The finance was seen in a wale.} \index{hanging}hanging above me. I had the \index{heartache}heartache. I saw \index{agate}agate. I was in \index{agony}agony\footnote{A human was within my agony, and this human was discovered in a school. It was distinct but not clear-cut.} over the \index{loss}loss\footnote{Someone was not in our loss.} of \index{money}money\footnote{This money appeared mutual. A time. A confetti was within my time. Mutual. It was in a timetable.}. I met another attired in a crimson dress with a crepe mourning \index{veil}veil\footnote{The veil was strange but not foreign.} over my \index{face}face\footnote{My face seemed possible and actual. A hair. An eye was within them.}. I was looking at an \index{atla}atlas\footnote{I found a landmass in my atla. Salty. It was seen in a country.}. I discussed any subject relating to \index{aura}aura\footnote{A sloth was in the aura. (We saw our sloth in a jungle.) Alive.}. I saw a bald-headed \index{man}man\footnote{You found a trouser there. A jean. You told me my jean was tight, and you said that it was dressy. It was in a store.}. I saw \index{bantam}bantam\footnote{The bantam was stupid but not stupefied.} chickens. I saw a \index{barometer}barometer. I was in \index{bed}bed\footnote{You told me my bed was uncomfortable. It was opaque but not unintelligible, and a kitten was not in it. I found it in an at home, and it was a cot but not a fingerstall.}. I saw \index{bedbug}bedbugs\footnote{Our bedbug was weird.} simulating death. 

 I saw one. I saw a bellowed. I was playing at blind \index{man}man\footnote{This man was discovered in a bedroom, and you told me they were impotent. (They were social.) I found an erection in them.}'s buff. I saw a \index{bookcase}bookcase\footnote{You found a shelf within. It was in a den, and our den appeared white. It did not appear dark.}. I drove a public \index{cab}cab\footnote{A cable. Our cable was both important and insignificant. (Someone was within it, and you saw it in a desk.)}. 

 I heard the \index{voice}voice\footnote{Your voice seemed loud and soft, and someone was within them. They were in a radio. A soprano.} of a \index{friend}friend\footnote{Our friend looked important, and they were in a school. (You said this school was not a university.) Your university was yellow, and someone was within it.} or relative. 

 I saw the water of a \index{canal}canal\footnote{This canal was in a bridge, and our bridge was addictive but not habit-forming. A hobo was within it.} muddy and \index{stagnant-looking}stagnant-looking. I saw a \index{cavern}cavern\footnote{We found a stalagmite in our cavern. A sinkhole.} yawning in the weird \index{moonlight}moonlight before me. I saw \index{chaff}chaff. I gave to charitable \index{institution}institutions\footnote{A student was within my institution. (You said it was not a museum.) You said that it was not yellow.}. I played \index{checker}checkers\footnote{You found a checkerboard there.}. I saw \index{ground}ground\footnote{This ground did not appear happy. We found someone in it. A neighbor.} coffee. I saw \index{convict}convicts\footnote{This convict was seen in a jail. (This jail appeared bad, and you said it was not a punishment.)}. 

 I saw a flight of \index{crane}cranes\footnote{My crane did not seem alive.} tending northward. I saw \index{cream}cream\footnote{My cream was found in a coffee. I found a creamery within.} served. I heard a \index{cricket}cricket\footnote{This cricket was in a refrigerator, and you said it was not a mole cricket. Our mole cricket seemed small.} in one's \index{dream}dream\footnote{I found our dream in a rainbow. It was a freedom but not an exemption. Important.}. I heard \index{cry}cries\footnote{I saw our cry in a fair. You found a food there. The food looked yummy. A salad.} of \index{distress}distress\footnote{I found a lemur in this distress. Our lemur did not seem alive. It was seen in a rain forest.}. 

 I saw a \index{crucifix}crucifix\footnote{My crucifix appeared slimy.}. I killed a \index{deer}deer\footnote{This deer did not seem hairy. You found an antler in it, and we found this antler in a deer.}. I was using a \index{desk}desk\footnote{This desk was sticky and gluey, and you told me it was opaque. I saw it in an office. I found a telephone there.}. I was innocent of \index{charge}charges\footnote{I found a captain in this charge.} preferred. I took \index{dinner}dinner\footnote{Someone was within your dinner, and you told me it was dull. It was edible and comestible. It was a cereal but not a grain, and it was in a room.} with my lover. I disputed with learned \index{person}people\footnote{The person was discovered in an apartment, and it seemed endothermic. (A liver was within it.) An astronaut. It was human.}. I received a \index{dowry}dowry. 

 I failed to receive a \index{dowry}dowry. I heard a duet sung. 

 I was done \index{eating}eating. I embraced. I tore the \index{entrail}entrails of another. I traveled in Europe. I saw happy and bright faced. I was famous. 

 I saw a \index{file}file\footnote{I found someone in the file, and our someone was not dangerous. You told me it was guilty. (A slave.) I found it in a theater.}. I was signaled by a \index{flag}flag\footnote{Your flag seemed stupid and smart, and a weasel was not in it. It was in a country.}. I flew with black \index{wing}wings\footnote{A flap was within the wing. They were in a flight.}. 

 I flew from one \index{city}city\footnote{This city was discovered in a country. The country was not expressive. An apple tree was within it.} to another. I chased a \index{fox}fox\footnote{A foxhole was within your fox.}. I climbed to a \index{garret}garret\footnote{This garret did not appear mean.}. I saw or passing through a \index{gate}gate\footnote{I found someone in my gate. Guilty. (I saw it in a museum.)}. 

 I saw a well. I was looking through \index{glass}glass\footnote{This glass was seen in a table, and I found a glasshouse in it. (Your glasshouse was big.)}. I was eating green \index{gooseberry}gooseberries\footnote{Our gooseberry was in a jar, and you found a jam there. Cool.}. 

 I saw a rugged \index{mountain}mountain\footnote{You told me the mountain was high. We found a climber there.} beyond the green \index{expanse}expanse of \index{grass}grass\footnote{Our grass was a wheat but not a wheat berry, and my wheat was not edible. (It was in a bread, and a wheat field was within it.)}. I read Greek. I saw one's hair \index{turn}turn\footnote{You found someone there. I saw your someone in a pool, and the pool was enjoyable and pleasurable.} perfectly white in one night. I saw a \index{hammer}hammer\footnote{Your hammer was hard, and you said it was not a mallet. It was important but not crucial. I saw it in a piano.}. I admired the \index{hand}hands\footnote{A briefcase was within this hand, and I found this briefcase in a courtroom.} of others. I admired my \index{hip}hips\footnote{I found a billfold within. Our billfold was in a money. Fake.}. I was in love with another \index{woman}woman\footnote{You said this woman was not a soprano. (We saw them in a store.) I found a dress in them. They did not seem emotional. You told me they were cold.}'s \index{husband}husband\footnote{This husband appeared faithful and unfaithful, and they were both evil and good. (They were in a city.)}. I saw illuminated \index{snake}snakes\footnote{You told me our snake was slimy, and you said that they were not competitive. A mouse was within them. A cobra.}. I felt an \index{iron}iron\footnote{Your iron appeared heavy and light. (You saw it in a chemistry lab, and it appeared heavy.)} \index{weight}weight\footnote{You found the weight in a gym. The gym was not a gymnastics. (It seemed expensive.)} bearing me down. I wore them. I saw them fell to the earth and \index{singing}singing as they fell. I was connected in any \index{way}way\footnote{You said my way was a run. My run looked fast. I found a pebble within, and I saw your pebble in a gravel.} with a \index{lawyer}lawyer\footnote{I found an attache case there, and we saw the attache case in a hospital.}. 

 I was a \index{member}member\footnote{Valuable. They were discovered in a cabinet.} of a \index{legislature}legislature. I wrote a letter. I was having one put up. I breathed the \index{fragrance}fragrance\footnote{Our fragrance was large but not gravid.} of \index{lily}lilies\footnote{Your lily appeared alive.}. I looked through a \index{magnifying-glass}magnifying-glass. I took malted \index{drink}drinks\footnote{Your drink did not seem wet, and a cup was not in it. This cup was a mug. I saw our mug in a kitchen, and you told me your kitchen was big.}. I saw an empty market. I married an old. I lost my \index{memorandum}memorandum. I was entangled in the \index{mesh}meshes\footnote{You said my mesh was not a net.} of a \index{net}net\footnote{My net was not an internet. You told me it was beige, and it was seen in a backpack. I found a compass there.}. I saw or passed a mile-post. I spilt \index{milk}milk\footnote{I found a cereal bowl there, and we saw it in a house. The house was a cellar but not a root cellar. (The cellar was blue and blueish.) Dark.}. I saw \index{mining}mining. I broke a \index{mirror}mirror\footnote{The mirror was discovered in a wall, and we found an electric socket in your wall. It was a membrane but not a tissue layer. Vertical.}. I saw a \index{moth}moth\footnote{The moth looked rectangular. We found it in a mother-in-law.}. I crossed a \index{mountain}mountain\footnote{You told me our mountain was beautiful. An alp. A bee was within our alp, and you said that it was big.} in \index{company}company\footnote{I saw this company in a suburb, and they were a corporation but not a potbelly. A human was not in them.} with my \index{cousin}cousin\footnote{A weasel. You told me your weasel was big, and I saw them in a chicken coop. They were alive but not awake.} and dead \index{brother}brother\footnote{My brother was found in a seminary.}. I saw others walking in \index{mud}mud\footnote{My mud was found in a waterfall. I found a moss in the waterfall.}. I ate them. I saw one dead. I passed through \index{nettle}nettles. I heard good news. I printed a \index{newspaper}newspaper\footnote{I saw this newspaper in a subway. (Skew.) Lightweight. We found a story in it.}. I saw \index{nightingale}nightingales\footnote{Our nightingale was cool and coolheaded.} silent. I saw one robbed of its \index{verdure}verdure by seeming \index{winter}winter\footnote{My winter was mild, and it was in a drawer. We found a wintertime in it. (A hockey.) Competitive.}. 

 I saw oyster \index{shell}shells\footnote{A snail was within the shell, and it was mathematical. You said it was not a bash, and we saw it in a can.}. 

 I saw one going out. I taught a parrot. I formed a partnership with a \index{man}man\footnote{You told me my man was happy. A boy. They were in a car. Warm-blooded. An erection was within them.}. I secured a \index{patent}patent\footnote{You saw my patent in a patent medicine.}. I was walking in a \index{narrow}narrow\footnote{The narrow was a neck but not a neck opening. A pain was within this neck. Pointless. It was in a bottle.} and rough \index{path}path\footnote{Our path was white and whitened, and it was unpredictable. It was a road.}. I saw a phantom fleeing from me. I received the \index{photograph}photograph\footnote{You said the photograph was not a photo, and our photo was in a waterfall. I found a beauty in our waterfall, and it seemed spectacular.} of my \index{lover}lover\footnote{Attractive. You found them in a bed, and a penis was in them.}. I was surrounded with the best \index{effort}efforts\footnote{A campfire was within our effort, and this campfire was in an effort.} of the old and modern \index{master}masters\footnote{You said my master was a poet, and I found a master bedroom within. We found my master bedroom in a house.}. I was walking across muddy \index{water}water\footnote{The water was discovered in a puddle. It looked neutral and positive. You said that it was not short. A rain. We found a seaweed within.} on a rotten \index{plank}plank\footnote{A plankton. My plankton was weird and eldritch, and you found it in a sea.}. 

 I ate them. I ridded myself of a \index{rival}rival\footnote{This rival seemed safe.} in this \index{way}way\footnote{The way was a sweat but not a sudor. It was discovered in a mountain. It was unpredictable but not irregular, and I found someone within.}. I saw police on \index{parole}parole. I ate \index{pork}pork\footnote{The pork was red but not crimson. I saw it in a dinner.}. I saw \index{quail}quails\footnote{Your quail was both alive and unanimated.}. I was at a church raffle. I registered under an assumed \index{name}name\footnote{You said your name was not an experience. Painful.}. I drove them. I saw a dead \index{reptile}reptile\footnote{My reptile was slimy. (It was discovered in a zoo.) It was a lizard. It was alive and live. You found a lizard in it.} come to life. I was rescued from any danger. I resigned any \index{position}position. I took \index{revenge}revenge\footnote{You told me the revenge was illegal.}. I saw \index{corpse}corpses\footnote{The corpse was seen in a graveyard.} in the \index{bottom}bottom\footnote{You said our bottom was not a lager.}. I was entertaining false \index{hope}hopes\footnote{A dream. They were pleasurable but not enjoyable. They were in a despair. A blanket was in them.}. 

 I saw \index{screw}screws\footnote{The screw was found in a motorcycle, and you told me my motorcycle was economical. Someone was in it. My someone was not a neighbor, and it seemed hard.}. I discharged one. I saw them sporting in clear \index{water}water\footnote{I found our water in a puddle.}. I walked among and \index{gather}gather shells. I saw empty \index{shelve}shelves\footnote{This shelve was in a pantry.}. I was shot. I heard the sighing of others. I walked over them. 

 I saw snow. I saw large. I saw snow-capped \index{mountain}mountains\footnote{A climber was not in my mountain. An alp. This alp appeared big, and it was in a mountain.} in the distance. I saw a socialist. I saw \index{soot}soot\footnote{Your soot seemed black and white, and you said it was a hunger. It appeared competitive.}. I saw sores. 

 I fell down them. I struggled. I dealt in \index{sugar}sugar\footnote{C. (It was a sucrose but not a saccharose.)} and saw large quantities of it being delivered to me. 

 I saw a cask of \index{sugar}sugar\footnote{The sugar did not appear dangerous, and we found it in a soft drink. The soft drink was a sprite. We found a sugar within.} \index{burst}burst and the \index{sugar}sugar\footnote{The sugar did not seem toxic. It was not a caster sugar. We found an ant in it. I saw it in a cupboard, and it was sticky.} spilling out. I saw my body appearing tattooed. I saw a \index{teakettle}teakettle\footnote{The teakettle appeared light and heavy, and we found it in a cupboard.}. I received a \index{telegram}telegram\footnote{Our telegram did not seem light, and I found a stop in it.}. I saw a broken \index{telescope}telescope\footnote{The telescope was not important.}. I admired me \index{thigh}thigh\footnote{The thigh was creative but not originative.}. I lost one. I saw old \index{velvet}velvet\footnote{Our velvet seemed flexible. It looked soft and hard. It was in a jewelry store.}. I had \index{walnut}walnut\footnote{You said your walnut was not a walnut tree.} \index{stain}stain\footnote{Your stain appeared toxic and nontoxic. It was in a rug.} on my hands. I found myself baling it out. 

 I fell into muddy \index{water}water\footnote{A seaweed was within our water. (I saw your seaweed in a beach.) It seemed nutritious. A kelp. My kelp seemed nutritious.}. I prepared or \index{eating}eating Welsh rarebitted. 

 I was a wet \index{nurse}nurse\footnote{An apple tree was in my nurse. This apple tree was found in a country.}. I heard the wind \index{soughing}soughing. I saw a \index{wreck}wreck. 

 I saw a yellow \index{bird}bird\footnote{I saw the bird in a sky. (You told me they were unanimated, and you said that they were not dead.) I found a birdbath there. They were a duck.} flitting about.

\chapter{}

I saw myself or \index{friend}friend\footnote{The friend was found in a door. A knob was not in this door. This knob was both difficult and manageable.} abandon a \index{ship}ship\footnote{We found this ship in a shipwreck.}. I saw an \index{abbey}abbey\footnote{The abbey was safe but not good.} in \index{ruin}ruins. I was an \index{abbot}abbot. I talked with an \index{abbot}abbot. I saw \index{blood}blood\footnote{The blood was discovered in a blood vessel. I found a blood in the blood vessel.} oozing from the \index{abdomen}abdomen\footnote{A navel was in my abdomen.}. I abhorred a \index{person}person\footnote{A heart was in my person. You said it was an atheist. My atheist was mean and average. They were in a school. Irreligious.}. I was abject. I changed my \index{abode}abode. I assented to abortion being committed on me. I rejoiced over the \index{absence}absence\footnote{You said our absence was a peace.} of \index{friend}friends\footnote{This friend was important. You said that they were not intelligent, and someone was within them. Our someone was a neighbor but not a neighbour, and your neighbor was in a neighborhood.}. 

 I came under the influence of absinthe. I looked into an \index{abyss}abyss. I was looking into an \index{abyss}abyss. 

 I visited an academy. I owned. I thought me owned. I avoided any \index{mode}mode\footnote{A machine was not in our mode. Warm-blooded. It was seen in a model.} of \index{travel}travel\footnote{You said that our travel was not one, and you told me it was wonderful. You found it in a traveller.} for a short \index{period}period\footnote{This period was in a woman. It was not a season.}. I befell \index{stock}stock\footnote{Our stock appeared young. It was in a suitcase. A nylon was within it.}. 

 I held \index{account}accounts\footnote{The account looked logical. A general ledger, and this general ledger was in an account. It did not appear logical.} against others. I had \index{ach}aches\footnote{Our ach was exceptional. You said it was an achievement.}. I drank aciduous \index{liquor}liquors\footnote{This liquor was found in a refrigerator. Your refrigerator was strong but not firm, and a beer was within it. (The beer was good.) A stout.}. I saw poisonous acids. I ate them. I saw green-growing \index{acorn}acorns\footnote{The acorn was seen in a forest.}. I pulled them green from the \index{tree}trees\footnote{Green. You found a shade there. This shade was not dark. We found it in a purse.}. I was acquitted of a crime. I saw others acquitted. I saw myself acrobating. I saw \index{acrobat}acrobats\footnote{Fragile.} in \index{tight}tights\footnote{Your tight was a choker but not a dog collar.}. I saw an \index{actress}actress\footnote{You saw the actress in a movie, and our movie seemed fictional. It was fictional and fancied.}. 

 I saw a dead \index{actor}actor\footnote{This actor was stupid and stupefied. We found them in a theater.}. I saw them wandering and penniless. 

 I was engaged to an \index{actor}actor\footnote{The actor was seen in a show, and this show appeared heavy.}. I saw or heard Eve conversing with the \index{serpent}serpent\footnote{You said that my serpent was not cold-blooded.}. I saw an adder \index{strike}strike. I pondered over \index{addition}addition\footnote{Commutative.}. I sought \index{adulation}adulation. I offered \index{adulation}adulation. I advanced in any \index{engagement}engagement\footnote{We saw this engagement in an engagement ring, and we found a diamond there.}. I met or engage with an \index{adversary}adversary\footnote{Your adversary was both strange and familiar.}. I was getting out \index{advertisement}advertisements\footnote{Our advertisement was not a preview. (Our preview was in a movie.)}. I sought legal advice. I was in Africa surrounded by \index{cannibal}Cannibals\footnote{You told me our cannibal was bad, and they were a cannibalism.}. I was affrighted. 

 I saw others affrighted. I saw others thus affected. I felt cold \index{air}air\footnote{My air did not appear flammable. It was seen in a sky. You said your sky was a river. A boat was within your river, and this boat was cool.}. I felt oppressed with humidity. I heard a bell in my \index{sleep}sleep\footnote{Your sleep was found in a motel. A room was within my motel. (My room was a bedroom but not a sleeping room.) You said that it was not unexplored, and you told me it was rectangular.}. I was an \index{alien}alien\footnote{Your alien was discovered in a universe, and our universe was fuzzy. It seemed infinite and finite.}. I wandered through an alley after dark. I lost an \index{amethyst}amethyst\footnote{The amethyst was not black.}. I was amorous. I heard \index{anecdote}anecdotes\footnote{Your anecdote was seen in a story.} related. I saw hot \index{iron}iron\footnote{You told me our iron was heavy. (We found it in a kitchen, and you said our kitchen was not a kitchen utensil.) Your kitchen utensil was solid.} with \index{spark}sparks\footnote{Your spark was edible and eatable.} flying. I saw fine \index{apparel}apparel. I rejected out-of-date \index{apparel}apparel. I walked with a \index{person}person\footnote{A bone was within your person, and you told me our bone was soft. I found it in a person.} wearing white. I saw myself. I saw many colored \index{apparel}apparel. I admired the \index{apparel}apparel of others. I saw an \index{architect}architect\footnote{We found a stamp pad within, and you saw our stamp pad in an office. It looked lightweight.}. I visited an art \index{gallery}gallery\footnote{Our gallery was tall and marvellous, and we found an artist within. (You saw our artist in a concert.)}. I visited Asia was \index{assurance}assurance of change. I was the one to receive the \index{assassin}assassin\footnote{Our assassin was not enjoyable.}'s \index{blow}blow\footnote{I found a blowfish there, and we found it in an ocean. (It was not a wind.) It was poisonous.}. 

 I received the \index{assassin}assassin\footnote{Educational.}'s \index{blow}blow\footnote{We found this blow in a bathroom. You found a blowfish in it. (The blowfish seemed poisonous.)}. I saw another. I was in an \index{attic}attic\footnote{You found our attic in a home. Claustrophobic. I found a rafter in it.}. I saw an attorney at the \index{bar}bar\footnote{I found an alcoholic there, and the alcoholic was not strange. They were in a pub, and you said the pub was not a statement. False.}. I saw augured. I saw my \index{aunt}aunt\footnote{You found an uncle within, and they were stupid but not dazed. They were in a home.}. I was awake. I saw one. I back-bited me. I saw them decaying. I traded in them. I saw one's \index{country}country\footnote{Expressive. It appeared beautiful. It was in a war. A human was not in it.}'s \index{banner}banner\footnote{I saw my banner in a demonstration. An activist was within the demonstration.} floating in a clear sky. I was an \index{applicant}applicant. I was being baptized with the Holy \index{ghost}Ghost\footnote{The ghost was a spook but not a ghost. They were found in a cemetery, and we found a graveyard there. It looked quiet and unquiet.} and \index{fire}fire\footnote{I found a coal in our fire. You told me the coal was black. We saw it in a mine.}. I was playing \index{baseball}baseball\footnote{Our baseball seemed hard, and it appeared healthy. It was seen in a baseball game. We found an outfield in it.}. I had a bass voice. I saw white roses in a \index{bathroom}bathroom\footnote{You found a mouthwash in this bathroom, and you saw it in an at home. You told me it was dark. It was a restroom. It was rectangular.}. I was defeated in \index{battle}battle\footnote{You told me our battle was expensive, and you said it was a destroyer.}. I killed a \index{bear}bear\footnote{The bear was discovered in a countryside. They were pure but not virginal, and you found a beard in them.}. I saw a \index{beard}beard\footnote{This beard was found in a carnival.}. I was beaten by an angry \index{person}person\footnote{You told me your person was mean, and you said it was not an astronaut. You said that it was individualist, and you found it in a conference. (We found a soul within.)}. I saw a \index{friend}friend\footnote{Our friend appeared important and noncrucial. They were not warm-blooded, and we saw them in a door. (A neighbor was within our door.) An entrance.} looking very pale. I had a strange bed \index{fellow}fellow\footnote{The fellow was not a shipmate. They were murky and mirky.}. I saw an old. I gave to a beggar. I was beheaded. I heard one. 

 I had a new \index{style}style\footnote{A makeover.} \index{belt}belt\footnote{Our belt was in a garage.}. I villified the \index{teaching}teachings of the Bible. I saw a wounded \index{bird}bird\footnote{My bird was both cool and warm, and you said they were not a parakeet. (I found a birdhouse there.) They were in an air, and my air was translucent.}. I caught \index{bird}birds\footnote{Competitive. You found them in a sky, and a plane was in my sky. (A glider.)}. 

 I killed than with a gun. I saw a blacksmith. 

 I was blind. I saw \index{blood}blood on my \index{hand}hands\footnote{You told me our hand was worthless. We saw them in a house. A carpet was in our house.}. I saw \index{tree}trees\footnote{A shade was in the tree, and we found your shade in a forest. Cool.} and shrubs in blossom. 

 I defended myself. I saw \index{worn}worn blotting \index{paper}paper\footnote{I saw my paper in a school. You found a pen in it. Fancy. You said it was not a marker, and the marker seemed cylindrical.}. I blushed. I heard boasting. I saw my \index{bone}bones\footnote{Strong. It was seen in a museum. I found a sword there.} protruding from the \index{flesh}flesh\footnote{You said that my flesh was green. A meat. It seemed sour. I found it in an inside.}. 

 I saw a \index{pile}pile\footnote{A kitten was within the pile, and the kitten was discovered in a shelter. It was hairy but not hirsute.} of \index{bone}bones\footnote{Our bone was in a hand. A cigarette was within my hand. They were dangerous.}. 

 I saw my \index{boot}boots\footnote{A foot was in your boot, and it seemed essential. I found it in a bedroom. You told me it was black.} on another. I saw a withered bouquet. I came close to a \index{person}person\footnote{A heart was in our person. You said your heart was a sex, and you found it in a hospital. (It was genetic.)} ing with a pure and sweet \index{breath}breath\footnote{A sigh. You said that my sigh was drunk. (We found a gazelle there.)}. 

 I was in a vast brewing \index{establishment}establishment\footnote{A restaurant.}. 

 I willed be deceived by some wily \index{enemy}enemy\footnote{You told me your enemy was good, and I found them in a war.}. 

 I saw fires of \index{brimstone}brimstone\footnote{Our brimstone was evil.}. I was in a \index{brothel}brothel\footnote{I found a prostitute within.}. 

 I was busy brushing my clothes. I saw large and magnificent \index{building}buildings. I saw a \index{bull}bull\footnote{This bull was strange but not unusual. They appeared bully. They were in a magazine, and a bullet was within them. Your bullet was a bulletin.} goring a \index{person}person\footnote{Your person was discovered in a bus stop, and it looked creative and uncreative. (It was not an astronaut, and a blood was within it.) Clear.}. I entered strange \index{premises}premises and had a bulldog \index{attack}attack\footnote{Graceful. It was in an attacker. A punch.} me. I ate rancid \index{butter}butter\footnote{The butter was edible and comestible, and they seemed edible. We saw them in a store. (You found a butterfly there.)}. I received \index{cablegram}cablegrams. I heard the \index{cackling}cackling of \index{hen}hens\footnote{An egg was not in this hen, and the egg was both unhealthy and healthy. It was seen in a supermarket. You told me your supermarket was light.} denoted a sudden \index{shock}shock produced by the \index{news}news\footnote{A newspaper was within my news. You found it in an airport. Readable.} of an unexpected \index{death}death\footnote{Our death was found in a battlefield. A soldier was not in this battlefield.} in my \index{neighborhood}neighborhood\footnote{We found our neighborhood in a glove compartment, and a map was within my glove compartment.}. 

 I saw wild \index{animal}animals\footnote{A nerve was within this animal. You told me it was warm, and it was in a wild. It was an elephant.} caged. I saw calm \index{sea}seas\footnote{You told me the sea was fresh, and you found a storm in it. It was found in a ship, and our ship was not an oil tanker.}. I felt calm and happy. I was the \index{subject}subject\footnote{You told me the subject was novel. You said they were not a geometry. A square was within our geometry. You found this square in a geometry.} of \index{calumny}calumny. 

 I saw a \index{herd}herd\footnote{Our herd was not a herdsman. (A cow was within it.) Black and white, and we saw them in a countryside.} of \index{camel}camels\footnote{Our camel was in a desert. The desert was a cake. It was sandy.} on the \index{desert}desert\footnote{Our desert was in a plate. It was an ice cream but not an icecream. The ice cream was sweet and perfumed. It was delicious.}. I was interested in a \index{campaign}campaign\footnote{We found the campaign in a table.} against fallen \index{woman}women\footnote{Our woman was found in a store. We found a toy within. (Your toy was a double bass.)}. I saw \index{cane}cane\footnote{This cane seemed yellow.} growing. I glided in a \index{canoe}canoe\footnote{You said my canoe was a kayak. We found a woman in the kayak, and it did not seem cool.} across a \index{canal}canal\footnote{We saw your canal in an ocean.}. I saw them burning with a clear and steady \index{flame}flame\footnote{The flame did not seem dangerous, and it was hot. (We saw it in a chemistry lab, and a chemical was in our chemistry lab.)}. I saw a \index{candle}candle\footnote{The candle seemed romantic. An egg. You saw the egg in a grocery store. An egg was within this grocery store.} \index{wasting}wasting in a \index{draught}draught\footnote{Our draught did not seem enjoyable.}. I heard or see \index{cannon}cannons\footnote{We found a cannonball in the cannon. Evil. Heavy. It was in a warship.}. I made \index{candy}candy\footnote{You said my candy was a nerd, and the nerd was found in an office. You told me they were smart, and they did not appear sticky.}. I ate crisp. I received a \index{box}box\footnote{This box was a coffin but not a casket, and a toy was not in it. Opaque. It appeared healthy. (It was seen in a basement.)} of \index{bonbon}bonbons\footnote{Sticky.}. I saw a \index{cap}cap\footnote{Tasty. (You found a marmoset in it, and it was seen in a ship.)}. I saw a \index{prisoner}prisoner\footnote{A person was within my prisoner, and they were found in a war.}'s \index{cap}cap\footnote{My cap was in a suitcase. I found a government in it. (My government was not a democracy, and this democracy seemed unreliable.)}. I saw a \index{miner}miner\footnote{You said that my miner was not hard, and they were in an ore. (You told me they were mineral.) I found a mineral within. You said they were not a fossil.}'s \index{cap}cap\footnote{A marmoset was in your cap. Your marmoset was both pure and impure, and you saw it in a zoo.}. I was a \index{captive}captive. I took any one \index{captive}captive. I was a \index{captive}captive. I missed one. I saw street-cars. I stood on the \index{platform}platform\footnote{This platform was red and ruby. (It was in a museum.) It was hazardous. A table.} of a \index{street-car}street-car while it was running. I drove a \index{cart}cart\footnote{This cart was seen in a store. Big. It was a shop but not a store. A clerk was within our shop.}. I saw \index{carpenter}carpenters\footnote{A level was within my carpenter. Important.} at their \index{labor}labor\footnote{I found a fungus in the labor, and it was seen in a work. It seemed hazardous. (It was not hazardous.)}. I saw a \index{carriage}carriage\footnote{Someone was within your carriage, and our someone was discovered in a museum.}. I was spending borrowed \index{money}money\footnote{Our money was found in a wallet. It was not a coin. A token was in this coin.}. I saw an old and vine-covered \index{castle}castle\footnote{Our castle was both white and black, and it was found in a fairy tale. A tower was not in it, and it seemed big.}. I was leaving a \index{castle}castle\footnote{The castle was dark and sullen. I saw it in a fairy tale. You found a tapestry in it.}. I saw \index{cattle}cattle\footnote{This cattle was in a country. Your country appeared expressive, and it looked beautiful. We found a government within.} stampeding. I saw this \index{vegetable}vegetable\footnote{Your vegetable was in a fridge. It did not appear yummy, and a vegetable garden was within it. You said it was a pea, and it appeared green and ripe.} in a \index{garden}garden\footnote{You told me this garden was nasty. A lawn. A lizard was in it, and my lizard was in a jungle.}. I saw a division of \index{cavalry}cavalry. I saw them dead or blighted. I saw it decaying. I was bound in \index{chain}chains\footnote{You found a chain gang there, and it was in a dungeon.}. I saw \index{chain}chains\footnote{I found a chain gang in our chain.}. I saw a \index{chair}chair\footnote{Your chair was comfortable, and they appeared opaque. An arm was not in them, and you found them in a table. They were a wheelchair.}. I saw a \index{friend}friend\footnote{My friend was seen in a door. You said this door was not an entrance, and my entrance was rectangular and orthogonal. We found a lock in it.} sitting on a \index{chair}chair\footnote{Your chair was opaque and unintelligible, and an arm was within them. You told me the arm was unportable. (A tank.) It was in a coat.} and remaining motionless. I was a \index{chairman}chairman\footnote{We saw the chairman in a meet, and a boss was within your meet. A supervisor. My supervisor was both unnecessary and necessary.}. I chalked my face. I was challenged to fight a duel. I fought a \index{duel}duel. I found myself in a beautiful and richly furnished \index{chamber}chamber\footnote{A cello was in our chamber.} implied sudden \index{fortune}fortune\footnote{You found a fortune cookie in our fortune. The fortune cookie was yummy.}. I made \index{love}love\footnote{This love was pleasant, and I found a human there. (You told me your human was incurious, and I saw it in a love.)} to a \index{chambermaid}chambermaid. 

 I saw a broken or ill-kept one. I was chastised. I administered \index{chastisement}chastisement to another. I was cheated in \index{business}business\footnote{A committee was within this business. It was in a business district.}. I palmed off false checks on my \index{friend}friends\footnote{My friend was in a door, and our door appeared underground. It looked large and little. An entrance. We found a couch within.}. I payed out \index{check}checks\footnote{We found a checkbook in our check, and we found our checkbook in a purse. It was lightweight.}. I ate \index{cheese}cheese\footnote{You said my cheese was not a cottage cheese. Good. It was edible. It was in a refrigerator, and you found a dirt within.}. I saw or \index{search}search\footnote{We found a search engine in your search.} through a chiffonier. I saw them in \index{bouquet}bouquets\footnote{I found a bee there.}. 

 I was in a \index{churchyard}churchyard\footnote{A confetti was not in this churchyard, and it was in a country.} meant they will never marry each other. I churned. I was in a strange \index{city}city\footnote{I found a theater within. Your theater did not appear tall. Dirty. (It was seen in a city.)}. I climbed up a \index{hill}hill\footnote{A sand dune.} or \index{mountain}mountain\footnote{Our mountain was an alp, and this alp was in an encyclopedia. You found a marmoset there.} and reaching the \index{top}top\footnote{I saw our top in a suitcase. (Large.) You found a shirt there, and you said this shirt was an undershirt.}. I rode in a coach. I wore another's coat. I lost my \index{coat}coat\footnote{Your coat seemed skinny. A button was not in it, and I found the button in a coat.}. I heard one at night was \index{despair}despair\footnote{I found your despair in a jail, and we found a wife in it.}. I saw \index{cock}cocks\footnote{You said this cock was a lemon juice. It did not seem cute. I found it in a cockroach. I found someone there.} fight. I drank a \index{cocktail}cocktail\footnote{A cocktail party was not in your cocktail. It was in a house, and your house was comfy and comfortable. It was a home but not a habitation.}. I saw my own \index{coffin}coffin\footnote{This coffin was in a graveyard. I found a spirit there.}. I was a \index{colonel}colonel\footnote{The colonel was creative and originative.}. I wore a collar. I combed one's \index{hair}hair\footnote{The hair was discovered in a mammal. A mammal family was not in my mammal.}. I was at a \index{light}light\footnote{We saw the light in a desk. (I found a lighthouse in them, and they looked electrical.) Useful. You said they were not a laser.} \index{play}play\footnote{A playground was within this play, and it was a musical but not a musical comedy. (I saw my musical in a musical composition.)}. I was commanded. I gave a command. I was engaged in \index{commerce}commerce. I saw one pointing awry. I had completed a garment. I completed a \index{journey}journey\footnote{We found a crossroad within. An adventure.}. I saw a composing \index{stick}stick\footnote{Your stick appeared yellow. Someone was within it, and your someone was found in a theater.}. I was under strange \index{influence}influences. I had \index{consumption}consumption\footnote{This consumption was commonplace.}. I was in \index{contempt}contempt of \index{court}court\footnote{This court appeared outside, and a courthouse was in it. It was found in a build.}. I saw my \index{brother}brother\footnote{This brother was in a seminary, and they seemed female. You said they were not an uncle.}. I copied. I saw a \index{fishing}fishing\footnote{I found a net in this fishing.} \index{cork}cork\footnote{Your cork was discovered in a corkscrew.} resting on clear water. I was corking bottles. I had \index{corn}corns\footnote{You found the corn in a country. It was green and greenish, and it was yellow.} on my \index{foot}feet\footnote{You told me the foot was fast. You found them in a desk, and the desk was both small and big. You found a lamp within.}. I broke a \index{corkscrew}corkscrew\footnote{We saw our corkscrew in a drawer. (This drawer was large but not heavy.) They were rectangular.} while using it. I saw a corpse placed in its \index{casket}casket\footnote{A human was within this casket, and the human was not a police officer. The police officer was in a beat.}. I saw a \index{battle-field}battle-field strewn with \index{corpse}corpses\footnote{This corpse was found in a war.}. I saw the corpse of any one of my immediate \index{family}family\footnote{Your family was important. They seemed loud. (They were a husband but not a hubby.) I found your husband in a marriage.}. I put \index{money}money\footnote{My money was discovered in a pocket. We found a purse there. Your purse was a handbag, and my handbag did not appear tough.} on the eyes of a \index{corpse}corpse\footnote{Our corpse was in a funeral parlour.}. I saw \index{person}persons\footnote{The person was in a hospital, and a wind was in your hospital. It was dirty.} talking in a \index{corner}corner\footnote{A table was not in the corner. It was discovered in a box, and you said that our box was glorious. You said it was a cart, and it appeared opaque and clear.}. 

 I saw cotton \index{cloth}cloth\footnote{You found a velvet there, and this velvet looked smooth. I saw it in a jewelry store.}. 

 I was aggravated by a constant \index{cough}cough\footnote{This cough was discovered in a cough drop.} indicated a \index{state}state\footnote{You found this state in a statement, and it looked false and true. (I found a highway in it.)} of low \index{health}health\footnote{Good. I found a spa within, and you said it was not a mental health. It was found in a city.}. I was crawling on the \index{ground}ground\footnote{Someone was within our ground. Our someone was both hard and soft. A neighbor. (Your neighbor was friendly.)}. I crawled over rough \index{place}places\footnote{You found a landmark in this place, and the landmark was seen in a city.} and \index{stone}stones\footnote{The stone seemed opaque, and I found it in a bridge. (A river was within our bridge.)}. I crawled in \index{mire}mire with others. I saw a criminal fleeing from \index{justice}justice\footnote{My justice looked blind, and they were creative and originative.}. I did crochet work. I was in a \index{crockery}crockery\footnote{We saw my crockery in a cupboard. You found a food there.} \index{store}store\footnote{Your store was white but not blank. It was a shop but not a store. A food was within it, and your food was found in a restaurant. You told me it was edible.}. I saw a \index{person}person\footnote{The person was in a bus stop. A heart was within it. (You told me our heart was immortal.) You said it was a love.} bearing a \index{cross}cross\footnote{Our cross appeared difficult and manageable. A crosswalk was not in it, and it was seen in a crosswalk.}. I saw cross-bones as a \index{monogram}monogram on an \index{invitation}invitation\footnote{My invitation was seen in a party. Our party was not sad. Uncomfortable. A human was in them.} to a funeral. I saw a \index{crowd}crowd\footnote{Your crowd was both powerful and powerless, and a human was within it. (You saw it in a fistfight.)} in a \index{church}church\footnote{This church was in a community. (You told me it was active, and it seemed tall.) A cathedral. A prayer was in my cathedral.}. I was heard in a crowd. I tried to be heard in a \index{crowd}crowd\footnote{A human was within this crowd, and it was seen in a demonstration. (It was both powerful and powerless.)}. I saw a crowd was usually good. I wore a \index{crown}crown\footnote{Your crown did not seem pretty.}. I saw others on \index{crutch}crutches\footnote{Our crutch was seen in a city.}. I heard a \index{cuckoo}cuckoo\footnote{My cuckoo was in a cuckoo clock.}. I saw a \index{cupboard}cupboard\footnote{A plate was in our cupboard. It was in a kitchen.}. I stepped on a \index{curbstone}curbstone. I reclined on silken \index{cushion}cushions\footnote{You said that the cushion was competitive. It was in a room.}. I saw a cuspidor. I spit in one. I entered a custom-house. I saw these \index{tree}trees\footnote{This tree was tall, and an apple tree. It was found in a mountain. I found a peak in your mountain.} lifting their branches loaded with rich purple \index{fruit}fruit\footnote{My fruit was discovered in an orchard, and a bee was not in this orchard. (You told me the bee was gaseous.)} and dainty \index{foliage}foliage\footnote{You said this foliage was a perennial, and I saw it in a forest.}. I saw older \index{person}people\footnote{This person was hairy and hirsute, and a heart was within it. An astronaut. You found our astronaut in a space shuttle.} dancing. 

 I was in a perilous situation. I watched the \index{day}day \index{break}break\footnote{We found our break in a repair shop, and I found someone there. You told me it was bad.}. I was conversing with a dead relative. 

 I saw any of my \index{person}people\footnote{I found our person in an apartment. (A human was not in your apartment.) This human was a vintner but not a wine maker. Your vintner did not appear emotional.} dead. I saw the graves or \index{casket}caskets\footnote{A human was not in our casket. It was in a funeral.} of the dead decorated with white \index{flower}flowers\footnote{The flower was not a tulip. (You found a bee in this tulip.) It did not appear fragrant, and it was pink.}. 

 I saw or signing \index{deed}deeds\footnote{The deed was both stupid and intelligent.}. I was delayed. I saw my \index{lover}lover\footnote{A penis was not in our lover, and the penis was in a short.} throwing \index{dice}dice\footnote{Random. I saw it in a casino. It did not seem educational.}. I dug. I saw freshly stirred \index{dirt}dirt\footnote{My dirt was seen in a carpet, and the carpet seemed soft and hardened. A stain was within it.} around flowers or trees. I was in any \index{disaster}disaster\footnote{Your disaster appeared bad.} from public conveyance. 

 I was not a \index{participant}participant. I was incurably diseased. I was disinherited. I fell in a ditch. I owned a dog with \index{fine}fine\footnote{The fine was seen in a fine art. A still life.} qualities. I heard the barking of \index{dog}dogs\footnote{The dog was discovered in a table. (You told me our table was flat.) It was hazardous and risky. A desk. A blotter was in my desk.}. I saw fancy \index{pet}pet\footnote{This pet was strange and foreign. A parakeet. You told me they were sick, and I found someone there. They were in a table.} dogs. 

 I heard the lonely baying of a \index{dog}dog\footnote{This dog was not warm-blooded, and they were in a beach. They appeared friendly and unfriendly, and you said they were not a beagle. (Someone was within them.)}. I was in the \index{dome}dome\footnote{Your dome was a domestic animal.} of a \index{building}building. I played at \index{dominoes}dominoes. I was the \index{winner}winner\footnote{Your winner looked happy and unhappy.} of the \index{game}game\footnote{You told me your game was enjoyable. Someone was not in it. A student. (My student was both creative and uncreative.) They were in a college.}. 

 I saw myself riding on a \index{donkey}donkey\footnote{The donkey was not competitive.}. I saw others riding \index{donkey}donkeys\footnote{My donkey did not appear competitive.}. I led one by a \index{halter}halter\footnote{Your halter was cute but not precious.}. I drank the \index{milk}milk\footnote{Wide. (You told me it was white.) A heifer was not in it. It was seen in a fridge.} of a \index{donkey}donkey\footnote{You said that the donkey was not strange.}. I saw a strange \index{donkey}donkey\footnote{My donkey was competitive and free-enterprise.} among my \index{stock}stock\footnote{My stock looked risky. We found a paper in it. This paper was a parchment.}. I came into the \index{possession}possession\footnote{A marmoset was not in our possession.} of a \index{donkey}donkey\footnote{You said that our donkey was not alive.} by \index{present}present\footnote{A gift. It was in a meet. Your meet did not appear hard, and you found a chair there. You told me your chair was man-made.}. I saw others go through a \index{doorway}doorway\footnote{We found a knob in your doorway, and it was not an archway. Our archway was in a build.}. I saw a dead \index{dove}dove\footnote{The dove appeared safe. A dovecote.}. I saw white \index{dove}doves\footnote{A dovecote. They were safe and dependable.}. I wrote one. 

 I was given to dram-drinking. I saw or use a draw-knife. I drove a public \index{cab}cab\footnote{This cab was green and unripened. A cabin was not in it, and your cabin was found in a cabinet.}. I drowned. 

 I saw my sweetheart drowned. 

 I heard the muffled \index{beating}beating of a drum. 

 I was drunk on heavy \index{liquor}liquors\footnote{The liquor seemed empty and full, and I saw it in a cupboard. You found a dish there. Our dish seemed large. They were a plate.}. I saw them shot. I saw them flying. I saw the \index{dyeing}dyeing of cloth or \index{garment}garments\footnote{My garment was not a coat, and we saw it in a garment bag.} in \index{process}process\footnote{The process was in a computer, and I found a mouse there.}. I saw \index{dynamite}dynamite\footnote{Our dynamite appeared loud. It appeared dangerous. It was in a coal mine.}. I saw one soaring above me. I saw one perched on distant heights. I killed an eagle. I rode on an \index{eagle}eagle\footnote{Free.}'s back. I saw or feel the earthquake. I saw a crate of \index{egg}eggs\footnote{An embryo was within the egg. My embryo was in an egg.}. I saw bird \index{egg}eggs\footnote{You told me my egg was fragile. We found an embryo in it. The embryo was in an egg. Yummy.}. I saw \index{elderberry}elderberries on \index{bush}bushes\footnote{You told me our bush was alive. I found a paper within, and your paper was in a school. You said our school was not a kindergarten. It was large and big.} with their \index{foliage}foliage\footnote{This foliage was in a forest, and you said it was not a perennial.}. I was at an election. I saw many \index{elephant}elephants\footnote{This elephant was found in a zoo.}. I feeed one. I did not approve. I embraced my \index{husband}husband\footnote{I saw our husband in a bed. Flammable. (It seemed flat, and you said it was a cot.)} or \index{wife}wife\footnote{My wife was both important and insignificant, and we saw them in a despair.}. I embraced \index{relative}relatives\footnote{You told me my relative was unhelpful. They were not a kin. A grandmother was in them, and this grandmother did not appear sensitive.}. I embraced a \index{stranger}stranger\footnote{My stranger was in a bus stop, and I found someone in our bus stop.}. I saw an emerald or emeralds on the \index{person}person of my affianced. 

 I went abroad and meeting the emperor of a \index{nation}nation\footnote{A national park was in our nation. You told me this national park was ugly.} in my \index{travel}travels\footnote{One. (A train ticket was in it.) Our train ticket was discovered in a purse.}. I was out of \index{work}work\footnote{A public servant, and the public servant was seen in a desk.}. I saw an \index{engineer}engineer\footnote{I found the engineer in a vacation. They did not seem human.}. I wore \index{epaulet}epaulets\footnote{The epaulet was not alive.}. I was introduced to a \index{person}person\footnote{My person was seen in a conference, and an attendee was within our conference.} wearing \index{epaulet}epaulets\footnote{The epaulet was cute and precious.}. I tried to satisfy an epicure. I satisfied an \index{epicure}epicure. I wore this beautiful and costly \index{raiment}raiment. I saw my sweetheart clothed in \index{ermine}ermine\footnote{My ermine was small but not small-scale.}. I scaped from some \index{place}place\footnote{My place was a restaurant but not an eatery. (Our restaurant was in a hotel.) You told me your hotel was uncomfortable. A bathroom was within it.} of \index{confinement}confinement. 

 I scaped from any \index{contagion}contagion. I came into the \index{ownership}ownership\footnote{My ownership was separate.} of a vast \index{estate}estate\footnote{Someone was within my estate, and it was both useful and useless.}. I impersonated Eve. I walked in the \index{evening}evening. I saw an \index{execution}execution. I was about to be executed. I was executed. I was exiled. I was enveloped in the \index{flame}flames\footnote{This flame was discovered in a chemistry lab, and a castanets was within it. Our castanets looked lightweight.}. I thought I was enveloped in the \index{flame}flames\footnote{You told me the flame was hot, and a castanets was within it. It was not a flamethrower. (I found it in a chemistry lab.) Your chemistry lab seemed dark.}. I saw an \index{eye}eye\footnote{A monocle was within my eye, and the monocle was seen in an eye. (This eye appeared blue, and it was an eye doctor.)}. I saw a strange and weird-looking \index{face}face\footnote{Our face was a hair. Your hair was possible but not potential, and it was in a mammal. You told me our mammal was exothermic. An eye was within it.}. I saw my \index{enemy}enemies\footnote{Your enemy was in a war. You told me they were bad. (They were not human.)} perishing by \index{famine}famine\footnote{The famine did not appear strange.}. I was famishing. I bid my \index{lover}lover\footnote{A penis was in our lover, and we found them in a backyard. They looked attractive and unattractive.} \index{farewell}farewell\footnote{We found someone within, and my someone was a neighbor.}. I saw others fat. 

 I saw \index{eagle}eagle\footnote{Free.} feathers. I saw ostrich and other ornamental \index{feather}feathers\footnote{My feather looked light and heavy. You found it in a pillow. (It was a quill.)}. I washed my \index{foot}feet\footnote{Your foot was in a shoe, and you said they were not a boot. I found a kitten in the boot, and my kitten was adorable.}. I fell from a \index{fence}fence\footnote{An apple tree was within this fence, and you said that they were not smart.}. I climbed through a \index{fence}fence\footnote{You found a garden within. The garden was perennial. You found it in a fence.}. I saw \index{stock}stock\footnote{You told me this stock was young. It was discovered in a market. A stock market was in it. (You said the stock market was not a market.)} jumping a \index{fence}fence\footnote{An apple tree was not in our fence, and they did not appear smart.}. 

 I waited at a \index{ferry}ferry\footnote{A train was not in our ferry.} for a \index{boat}boat\footnote{You told me this boat was cheap, and you said it was a tugboat. You said that this tugboat was expensive.} and see the \index{water}waters\footnote{A dolphin was within my water, and it was discovered in a pool. Educational.} \index{swift}swift\footnote{We found our swift in a webcam.} and muddy. 

 I was at a \index{festival}festival\footnote{Someone was not in my festival. This someone was a student but not an educatee. It was dangerous and severe. You found it in a museum.}. I saw some of my \index{family}family\footnote{You found a person in the family. Useful. They were important, and they were found in a supermarket.} sick with \index{fever}fever\footnote{This fever was an antipyretic but not a febrifuge.}. I played one myself. I saw \index{fighting}fighting\footnote{This fighting seemed transient.}. I saw me \index{lover}lover \index{fighting}fighting\footnote{Your fighting was transient.}. I saw two men fighting with \index{pistol}pistols\footnote{You said that this pistol was automatic, and a bullet was not in it. It was dangerous. It was seen in a pant.}. 

 I saw a fire-engine. I saw the \index{firmament}firmament illuminated and filled with the heavenly \index{host}hosts\footnote{Your host was found in a hostess.}. I visited a fish \index{market}market\footnote{Your market was in a city. I found a car in the city.}. I saw \index{flax}flax\footnote{Our flax did not seem green.}. I saw a large \index{fleet}fleet moving rapidly. I saw \index{anything}anything\footnote{A sentence was not in your anything, and it was a ladder. The ladder was discovered in a roof, and this roof looked red.} fleeing from me. 

 I saw \index{flower}flowers\footnote{You told me the flower was alive, and it was seen in a table. (It was both organic and functional, and an apple tree was not in it.) It was a violet but not a reddish blue.} blooming in \index{garden}gardens\footnote{You told me your garden was spacious, and you said it was not a lawn. (A bug was not in it.) I found it in an outside.}. I saw \index{flower}flowers\footnote{I found the flower in a vase. You said this vase was a vasectomy.} blooming in barren \index{soil}soil\footnote{I found my soil in a garden. We found a fungus there.} without \index{vestage}vestage of \index{foliage}foliage\footnote{The foliage was found in a forest. You found a squirrel there. You told me it was warm.}. I flew high through a \index{space}space\footnote{Your space was in a box, and it did not seem noisy. It was a hallway but not a hall. (Flat.) Someone was within it.}. I flew low. I flew over muddy water. I flew through the \index{firmament}firmament passing the moon and other \index{planet}planets\footnote{The planet seemed pretty. (I found a landmass there, and our landmass was in an ocean.)}. I was in a \index{fog}fog\footnote{My fog was in a valley. The valley was low.}. I fell from a \index{foot-log}foot-log into clear water. I saw a \index{forest}forest\footnote{This forest was seen in an outdoors, and a sky was not in our outdoors. You told me it was beautiful. (It was an amphitheater.)} of stately \index{tree}trees\footnote{A pine tree, and a bee was within this pine tree.} in \index{foliage}foliage\footnote{Your foliage was in a forest. You said it was a perennial.}. I kissed the \index{forehead}forehead of my \index{lover}lover\footnote{We found a penis there. They were seen in a restaurant. Attractive.}. I was confined in a \index{fortress}fortress\footnote{Your fortress was both big and little.}. I put others in a \index{fortress}fortress\footnote{This fortress was high but not eminent.}. I saw a sparkling \index{fountain}fountain\footnote{A fountain pen was within your fountain. My fountain pen did not appear large. Classy. It was discovered in a desk.} in the \index{moonlight}moonlight. 

 I saw \index{fowls}fowls. I saw a \index{fox}fox slyly coming into my yard. I was defrauding a \index{person}person\footnote{My person seemed distinct. (A soul was not in it.) This soul was found in a human.}. I saw my \index{friend}friend\footnote{We found my friend in a school, and this school did not appear large. You said it was not a college. You found a professor within. It looked expensive.} troubled and haggard. I saw my friends dark-colored. I saw a friend standing like a \index{statue}statue\footnote{Our statue was in a zoo. A monument. This monument was green and gullible.} on a hill. I was shaking \index{hand}hands\footnote{A cigarette was in our hand. I saw them in a pocket. You said this pocket was not a pocket watch. Small.} with a \index{person}person\footnote{I saw the person in a conference, and I found an ass in the conference.} who had wronged me. I was frightened at \index{anything}anything\footnote{You told me my anything was finite. You said it was not a toy, and the toy was seen in a box. (I found a sheet of paper in the box.)}. 

 I caught \index{frog}frogs\footnote{Our frog did not seem cute, and I found a wart within. (It was found in a field, and you told me my field was beautiful.)}. I saw \index{frost}frost\footnote{This frost was found in a frostbite. Preventable.} on a dark gloomy \index{morning}morning\footnote{Painful. It was a breakfast. Our breakfast was in a table.}. I saw \index{frost}frost\footnote{This frost was in a frostbite, and it appeared preventable.} on a small \index{sunlit}sunlit \index{landscape}landscape\footnote{This landscape was breathtaking. It was discovered in a university. I found a science there. Yellow.}. I saw a \index{friend}friend\footnote{My friend was in a fraternity house. I found a college student there, and your college student was not tough.} in a frost. I bought or sell fruit. I saw or eat ripe fruit. I attended a funeral in black. I was dressed in \index{fur}fur\footnote{You said my fur was not a hair. The hair seemed lightweight, and I found it in a mammal. We found a ribbon in it.}. I was caught in a \index{gale}gale. 

 I saw my \index{lover}lover executed by this meant. I rescued any one from the \index{gallows}gallows\footnote{This gallows seemed murky.}. I hung an \index{enemy}enemy\footnote{My enemy did not appear fragile, and they were in a war. Bad. You found a battle in it.}. I was gambling and win. I saw any one afflicted with \index{gangrene}gangrene\footnote{This gangrene was both infectious and noninfectious.}. I saw \index{heap}heaps\footnote{My heap seemed weird, and a kitten was within it.} of \index{garbage}garbage\footnote{Our garbage was discovered in a landfill, and a fly was not in it. (My fly was small and pocket-sized, and it looked small and big.)}. I ate \index{garlic}garlic\footnote{This garlic was found in a cupboard. I found a coffee cup within.}. I found my lady's \index{garter}garter\footnote{This garter was in a drawer. My drawer did not appear dark. You told me they were rectangular.}. I lost my \index{garter}garter\footnote{My garter was seen in a drawer.}. I was admiring beautiful jeweled garters on my \index{limb}limbs\footnote{We found a limbo within. You said it was a finger. It was not nice.}. 

 I saw a closed \index{gate}gate\footnote{This gate was seen in a backyard. A garden was in your backyard.}. I was annoyed by the \index{quacking}quacking of \index{goose}geese\footnote{Your goose was cute. They were in a sky. You told me this sky was blue. You found a planet within.}. 

 I saw them in grassy \index{place}places\footnote{The place was in a city. I found a landmark in it, and the landmark was memorable.}. I was picking them. I spoke to me. I saw an \index{angel}angel\footnote{The angel was stupid and stupefied, and you said they were not a cherub. They appeared good, and they were discovered in an aquarium.} or a \index{ghost}ghost\footnote{This ghost was found in a cellar. You said that your cellar was not white, and we found a spider there. You told me this spider was fatal.} appear in the \index{sky}sky\footnote{An airplane was within my sky. You told me my airplane was small. Mechanical. We found it in a hanger, and you said it was not an airliner.}. I saw the \index{ghost}ghost\footnote{The ghost was discovered in a cemetery. They were peaceful and peaceable. (You said they were not a ghost town.)} of a living relative or \index{friend}friend\footnote{We found a comfort within. (You told me they were noncrucial, and they did not appear mortal.) I saw them in a school.}. 

 I wore a \index{girdle}girdle\footnote{You said this girdle was a cinch.}. I received one. I was a \index{girl}girl\footnote{This girl was weird, and we saw them in a movie. You said they were not a niece. You said that our niece was not weird.}. I saw my \index{image}image\footnote{My image was blurry. They were not a photograph, and you said that the photograph was pretty. We saw it in a newspaper. A scenery was in it.} in a mirror. I received cut \index{glass}glass\footnote{The glass was both white and black, and it was in a table. You told me the table was flat. You found a silverware in it.}. I saw me lover in a \index{mirror}mirror\footnote{A reflection was in the mirror. It was a mirror image but not a reflection, and it was reflective. (It was in a house.)}. I saw strange \index{woman}women\footnote{Our woman was a girl. They were emotional and worked up, and they were beautiful. I found a vagina there, and we saw this vagina in a woman.} in a \index{mirror}mirror\footnote{I saw this mirror in a reflection, and a mirror was in this reflection.}. 

 I saw a \index{glass}glass\footnote{We found an ice cube there, and it seemed white. It was in a window. Recyclable.} \index{house}house\footnote{Your house was in a subdivision, and a roadway was in the subdivision. It was not a city.}. I was surrounded by many gloomy \index{situation}situations. I wore old or ragged \index{glove}gloves\footnote{You said this glove was not a mitten. You saw this mitten in a cold, and it was soft and diffuse.}. I fastened a \index{lady}lady\footnote{The lady looked sexy, and they were in a supermarket. I found a bag within.}'s \index{glove}glove\footnote{The glove was a baseball mitt but not a glove, and our baseball mitt was cold.}. I rode a billy \index{goat}goat\footnote{Endothermic. They were in a barn.}. I drank \index{water}water\footnote{My water was in a waterfall. (It looked fluid.) A coral reef was within it, and it was a rain but not a rainwater. Your rain was unavoidable and ineluctable.} from a silver \index{goblet}goblet\footnote{This goblet was both pure and impure. You saw it in a bookstore, and I found a novel in this bookstore.}. I saw \index{goblet}goblets\footnote{You found this goblet in a bookstore.} of ancient \index{design}design\footnote{My design appeared faddish. (It was found in a plate, and someone was not in it.) Our someone was dangerous but not severe.}. I gave a man a \index{glass}glass\footnote{My glass was both white and black. It was discovered in a cupboard, and I found a dish in our cupboard.} goblet full of \index{water}water\footnote{I found your water in a puddle, and I found a coral reef there. You said that it was fleet, and it was not a rain. (You told me our rain was cold.)}. I lost \index{gold}gold\footnote{The gold was found in a ring. (Heavy.) Blue. A diamond was within it.}. I found a \index{gold}gold\footnote{Your gold was hard and punishing, and it was found in a ring. It appeared expensive, and a gold mine was in it.} \index{vein}vein\footnote{A blood was within my vein.}. I contemplated working a gold \index{mine}mine\footnote{This mine was hard, and a coal was within it. (I found our coal in an underground.)}. I was the \index{object}object\footnote{My object seemed heavy, and it seemed solid and liquid. It was in a desk, and a paper clip was within your desk.} of \index{gossip}gossip\footnote{This gossip was not a talk.}. I heard the \index{gramophone}gramophone\footnote{My gramophone was powerful.}. 

 I saw \index{grasshopper}grasshoppers\footnote{You said that your grasshopper was not competitive, and it was seen in a meadow.} between me and the \index{sun}sun\footnote{Your sun was seen in an outer space. I found an astronaut within, and you told me it was cold. It was loud and forte.}. I saw a newly made \index{grave}grave\footnote{My grave was a duty, and the duty was in an airport. A return ticket was in your airport.}. I saw a \index{person}person\footnote{You said that the person was not distinct. A student. Our student looked tough and tender. They were in a school, and I found a computer within.} in a \index{grave}grave\footnote{You told me our grave was grey, and it was seen in a gravel. A pebble was within the gravel.} with the earth covering me. I saw my own \index{corpse}corpse\footnote{The corpse was seen in a funeral. A dead person was not in the funeral. You told me it was sad.} in a \index{grave}grave\footnote{We found a graveyard within. It was in a gravel.}. 

 I saw gravel mixed with \index{dirt}dirt\footnote{You told me your dirt was opaque, and you found an anemone within. This anemone was in an ocean. You said that it was pure.}. I played on a \index{guitar}guitar\footnote{A string was within the guitar. It was an electric guitar, and it appeared expensive and cheap. It was in a concert, and my concert appeared beautiful.}. I shot a \index{person}person\footnote{The person seemed warm, and it was in an apartment. I found a kitten in my apartment, and your kitten seemed adorable.} with a \index{gun}gun\footnote{A pistol was within my gun. (You told me my pistol was dangerous.) We saw it in a police station.}. I saw my own \index{face}face\footnote{Possible. We found a mouth there, and you said this mouth was a mouth organ.} haggard and distressed. I heard \index{hail}hail\footnote{Our hail appeared cold. It was discovered in a thunderstorm.} \index{beating}beating the house. I saw my \index{hair}hair\footnote{This hair was seen in a sink, and a faucet was in my sink.} turning gray. 

 I saw well kept and neatly combed \index{hair}hair\footnote{An eyebrow. You saw this eyebrow in a cabinet, and it did not appear thin.}. I cut my \index{hair}hair\footnote{A hair gel was within your hair. I found my hair gel in a bottle. My bottle was recyclable.} close to the \index{scalp}scalp\footnote{Our scalp was discovered in a hospital. It seemed useful, and a hair follicle was in it.}. 

 I saw tangled and unkempt \index{hair}hair\footnote{Our hair was found in a sink. We found a hair within.}. I saw flowers in my \index{hair}hair\footnote{We found a hairpin in my hair, and I found this hairpin in a bathroom.}. I saw my \index{hand}hands\footnote{A briefcase was within my hand. They appeared reusable. They were in a keyboard.} covered with \index{hair}hair\footnote{We found a hair gel in the hair. Sticky. We saw it in a beauty salon.}. I saw my \index{hand}hands\footnote{We found a briefcase in our hand. We saw this briefcase in a business office.} soiled. I washed my hands. I distributed \index{handbill}handbills over the \index{country}country\footnote{You told me your country was beautiful. I found a city in it. The city was seen in a country, and the country did not appear expressive.}. I saw handcuffs. 

 I saw them soiled. I saw them colored. I saw and recognize my own \index{handwriting}handwriting. I saw a \index{hare}hare\footnote{You said this hare was not a harem, and it looked flighty. Pure.} escaping from me. I saw \index{hare}hares\footnote{A harem.} chased by \index{dog}dogs\footnote{This dog was both pure and impure, and a dog show was in them.}. I was dressed as a \index{harlequin}harlequin. I was in the \index{company}company\footnote{You said this company was a corporation, and I found an employee there.} of a \index{harlot}harlot\footnote{My harlot was in a street corner.}. 

 I willed probably be troubled with various little \index{jealousy}jealousies\footnote{The jealousy was a sarcasm but not a satire.} and \index{contention}contentions over mere \index{trifle}trifles. I lost my \index{hat}hat\footnote{A hatpin was in the hat. (It was opaque, and it was a derby but not a plug hat.) It was in a build.}. I hated a \index{person}person\footnote{You told me our person was native. It was warm but not tender, and it was in a bus stop. It was an astronaut.}. I saw a dead hawk. I saw the heart of an animal. I saw my \index{friend}friends\footnote{My friend was seen in a school, and we found a girl there. You said it was a college. It seemed yellow, and it appeared white.} in \index{hell}hell\footnote{I saw the hell in a hellhole, and it was a war. You found a demon there.}. I cried in \index{hell}hell\footnote{You said this hell was a hello.}. I saw hemp \index{seed}seed\footnote{The seed was an acorn. My acorn was in a roof.}. I found myself in the \index{abode}abode of a \index{hermit}hermit\footnote{Our hermit was found in a fish tank.}. I saw \index{herring}herring\footnote{A herringbone was in our herring, and it was seen in a herringbone.}. I had hidden away any \index{object}object\footnote{My object was heavy, and it was solid. I found an object program there, and it was a pen but not a penitentiary. It was found in a drawer.}. 

 I admired well-formed hips. I saw a \index{hoe}hoe. I hoeeed. I feeed my own \index{hog}hogs\footnote{This hog did not seem warm-blooded, and a quill pen was in them.}. I was dealing in \index{hog}hogs\footnote{My hog seemed hairy. (A quill pen was not in them.)}. I was taking part in the Holy Communion. 

 I was in a \index{body}body\footnote{You found a blood in our body, and the blood was discovered in a person. They did not seem fluid, and they seemed liquid and gaseous.} of \index{baptist}Baptists\footnote{This baptist was white but not lily-white.} who was taking \index{communion}communion. I saw my old \index{home}home\footnote{You found a human there. It seemed big. You told me it was safe, and we found it in a leather.} in a dilapidated \index{state}state\footnote{We found a county within. (It was false.) It was discovered in a statement.}. I went \index{home}home\footnote{Your home seemed noble. (It was in a leather.) It was a condominium but not a condo. I found a sofa in it, and our sofa was man-made but not synthetic.} and find \index{everything}everything\footnote{Your everything was adjustable, and a plastic was within it. I saw it in a universe. A win. You said that it was not deaf.} cheery and comfortable. I saw strained honey. 

 I was wearing a \index{hood}hood. I heard the \index{sound}sound\footnote{Our sound was a music but not a medicine, and my music was found in a movie. (Our movie was fictional.) An audience was within it.} of a \index{horn}horn\footnote{We saw our horn in an orchestra, and someone was within it. It was a trumpet but not a trump. (It was gold.)}. I saw a broken \index{horn}horn\footnote{The horn was discovered in an automobile. Your automobile was fast but not debauched. You said it was not a limousine.}. I had my \index{horoscope}horoscope drawn by an \index{astrologist}astrologist. I rode or see \index{passing}passing \index{horse}horses\footnote{Fast. (I found a cowboy in it.) A cowboy boot.}. 

 I rode a runaway \index{horse}horse\footnote{My horse was strong. (You found a barn within.) A mustang. Our mustang was useful and utilitarian.}. 

 I saw a horse running away with others. I rode a horse that \index{buck}bucks\footnote{You said our buck was not a bucket. (I found a mouse within, and you told me it was unsafe.) It was not large, and it was in a well.}. 

 I caught a \index{horse}horse\footnote{Our horse was a palomino.} to bridle and saddle. I saw spotted \index{horse}horses\footnote{Brown. You said it was a pony, and I found your pony in a carnival. I found a game of chance in my carnival.}. I killed a \index{horse}horse\footnote{My horse looked fast and slow. A palomino.}. I curried a \index{horse}horse\footnote{A pony. My pony was in a carnival.}. I fitted a broken shoe which was too small for the \index{horse}horse\footnote{You found a barn in our horse. A mustang. (Our mustang seemed expensive.) It looked wild and tame.}'s \index{foot}foot\footnote{You found a boy in your foot, and they were a cowboy boot. They seemed fast. (They were in a body.)}. I attempted to fit a broken \index{shoe}shoe\footnote{I found an arch in this shoe. The arch was in an archway, and the archway was both light and heavy.} which was too small for the \index{horse}horse\footnote{My horse was not cool, and it was a mustang. (This mustang seemed wild and tame, and we found a radiator in it.) Our radiator was found in a house.}'s foot. 

 I was riding a white \index{horse}horse\footnote{You told me my horse was strong. A mustang. It was in a cavalry.} up and down \index{hill}hill\footnote{Your hill looked steep and gradual. It was in an outside, and we found a lizard in it. (You said it was a sand dune.)}. I saw a \index{horse}horse\footnote{A cowboy was not in the horse. Our cowboy seemed popular and unpopular. (They were in a cowboy boot, and a cowboy boot.)} in human \index{flesh}flesh\footnote{You told me our flesh was sweet. A meat. It was blue, and I saw it in an inside.}. 

 I picked one up in the \index{road}road\footnote{You told me the road was urban, and I found a fork in it. Your fork was seen in a plate, and it was wooden.}. I visited women in a hotel. I saw a fine \index{hotel}hotel\footnote{A concierge was within your hotel. (My concierge was in a hotel.)}. I was the \index{proprietor}proprietor\footnote{The proprietor did not appear large.} of a \index{hotel}hotel\footnote{You said this hotel was a motel, and this motel was in a country. This country seemed expressive. A citizen was within it.}. I was a \index{housekeeper}housekeeper\footnote{You told me my housekeeper was dirty.}. I was hurt. I saw me gay and handsome. I was in \index{love}love\footnote{You told me my love was emotional. Unpleasant. We found them in an at home. I found a bed within, and it was a gene but not a factor.} with another woman. 

 I saw my \index{husband}husband\footnote{Your husband was in a bed, and they were enjoyable and gratifying. They looked faithful and unfaithful.} \index{depart}depart\footnote{You found a shower curtain in the depart. We found this shower curtain in a hotel.} from me. 

 I saw. I was afflicted with \index{hydrophobia}hydrophobia. 

 I saw others thus afflicted. I walked on \index{ice}ice\footnote{You told me the ice was frigid, and it was not a flower. We found a flower garden in our flower. This flower garden was found in a university.}. I saw \index{icicle}icicles\footnote{You said that my icicle was not fragile, and it looked cold and hot.} on the \index{fence}fence\footnote{This fence was smart but not bright, and a gate was within them.}. I saw them on \index{tree}trees\footnote{The tree was organic but not constitutional. It was found in a forest, and the forest appeared dirty and clean. We found a moss in it.}. I saw them on \index{evergreen}evergreens\footnote{My evergreen was both dark and light. It looked green. It was not a fir, and a fire was within your fir. My fire was in a kitchen.}. I upset my \index{ice}ice\footnote{You found my ice in a supermarket, and I found an iceberg within. You told me it was voiced. It was not pale blue. It was not a water ice.} \index{cream}cream\footnote{A creamery was within the cream. (It was in a coffee.)} in the \index{presence}presence\footnote{Our presence was a cholelithiasis. It was both creative and uncreative.} of my \index{lover}lover or \index{friend}friend\footnote{Your friend was both intelligent and unintelligent, and a comfort was within them. They were discovered in a door, and your door looked rectangular.}. 

 I was an idiot. 

 I saw strange and weird \index{illumination}illuminations. 

 I saw illuminated human \index{figure}figures\footnote{You said my figure was a hexagon.} or animals in the \index{heaven}heavens\footnote{Fuzzy. I saw it in a sky, and my sky was up. (I found a planet within.)}. I set up an \index{image}image\footnote{Our image was blurry, and they were a paint but not a key. (Your paint was both empty and full.) A scenery was within it.} in my \index{home}home\footnote{Noble. I found a comfort in it. It was in a money, and my money was a time.}. I was an \index{imp}imp\footnote{Our imp was found in an impression.}. 

 I was using \index{incantation}incantations. 

 I lost my \index{income}income. I was very independent. I saw indigo. I saw objects indistinctly. I was industriously at \index{work}work\footnote{A challenge was within my work. You found my challenge in a work.}. I saw others busy. I saw others infirm. I had ink on my fingers. I made \index{ink}ink\footnote{My ink was in a squid, and a theater ticket. (You told me this theater ticket was cheap.) You said that it was not red.}. I saw \index{bottle}bottles\footnote{Our bottle was discovered in a nursery. My nursery was cute but not cunning. You found an anemone in it.} of \index{ink}ink\footnote{You told me our ink was green. We found it in a calligraphy, and you found an ink in my calligraphy. (Our ink was a theater ticket, and the theater ticket appeared red.)}. I saw them filled with \index{ink}ink\footnote{Our ink was green, and a quill was not in it. This quill was soft. (It was not a quill pen.)}. I saw others insane. I was \index{intemperate}intemperate in \index{love}love\footnote{The love seemed painful. A human was within them. (Our human was in a love, and your love was bad but not speculative.)}. I saw \index{intestine}intestines. I saw \index{city}cities\footnote{A theater was within this city. (Our theater was seen in a mall.)} or \index{country}country\footnote{Your country seemed beautiful and ugly, and it was discovered in a war. It was expressive, and a citizen was not in it.} submerged in dark. I saw human \index{being}beings swept away in an \index{inundation}inundation. I saw a large \index{area}area\footnote{I found a motel in this area, and our motel was in a shower.} inundated with clear \index{water}water\footnote{You found a boat there. You told me your boat was cheap, and it was in a river.}. I visited me. 

 I invited \index{person}persons\footnote{This person was in a hospital. (Your hospital seemed clean.) A bed was within it. You said your bed was not a cot, and it did not appear flammable.} to visit me. 

 I struck with \index{iron}iron\footnote{You found the iron in a golf bag. Blue. (A club was in it.)}. I manufactured \index{iron}iron\footnote{This iron was in a golf bag, and a club was within my golf bag. (You told me it was blue.)}. I sold \index{iron}iron\footnote{Smooth. Cold. It was in a house.}. 

 I ironed. 

 I had the itch myself. I killed one. 

 I saw others in jail. I bought \index{jar}jars\footnote{The jar was large and expectant, and a pickle was not in it. We saw it in a pantry.}. I had the \index{jaundice}jaundice. I saw others carrying \index{javelin}javelins\footnote{My javelin seemed cool.}. I caught a jay-bird. I was jealous of my \index{wife}wife\footnote{Female. They were female but not distaff. They were in an at home.}. I was in \index{company}company\footnote{Your company was in a city, and a telephone booth was within the city.} with a Jew. I argued with them. I saw others wearing them. I received jewelry. I saw my \index{sweetheart}sweetheart dancing a jig. I went on a \index{journey}journey\footnote{This journey was an adventure but not a dangerous undertaking, and we found a crossroad in it.}. I expected. I made a \index{long-distance}long-distance \index{journey}journey\footnote{This journey was not an adventure, and I found a crossroad there.} in a much shorter time than I expected. I felt \index{joy}joy\footnote{This joy was both unpleasant and pleasant. It seemed good, and it was in a joystick.} over any event. I took an unpleasant \index{drink}drink\footnote{A cappuccino. Healthy.} from a \index{jug}jug\footnote{You said your jug was not a religion, and you found a sexism there. It was in a cathedral. My cathedral appeared educational.}. I jumped down from a \index{wall}wall\footnote{My wall was seen in a refrigerator. (A fridge.) It seemed man-made. White. We found a fungus in it.}. I saw a \index{juniper}juniper\footnote{Our juniper did not seem green.} tree. I was on the \index{jury}jury\footnote{This jury was both violent and nonviolent. We found someone in it. Innocent.}. I killed one. I saw them. I saw a \index{kettle}kettle\footnote{A spout was within our kettle, and the spout was in a kettle.} of boiling \index{water}water\footnote{Your water was a rain but not a rainfall, and it appeared beautiful. It was found in a river, and a seaweed was not in it. Nutritious.}. I found \index{key}keys\footnote{We found a keyboard there. It was in a piano, and you said this piano was a clavichord.}. I cannotted find the \index{keyhole}keyhole\footnote{The keyhole appeared big.}. I killed one in \index{defense}defense. I was crowned \index{king}king\footnote{The king looked royal. They were rich but not racy. (They were found in a monarchy.)}. I was censured by a \index{king}king\footnote{Your king appeared royal, and they were an automobile but not an auto. I found your automobile in a shop. (It was beautiful.)}. I was in the \index{presence}presence\footnote{A cholelithiasis. It was weird and unearthly.} of a \index{king}king\footnote{This king looked royal. They were rich but not deep. They were in a palace. They were an automobile.}. I saw my rival \index{kiss}kiss\footnote{You said my kiss was not a lip, and it was in a movie. It looked free.} my \index{sweetheart}sweetheart. I saw \index{snake}snakes\footnote{You said my snake was not a cobra. You said that the cobra was dangerous.} kill kittens. I saw rusty \index{knife}knives\footnote{This knife was a scalpel. (It was seen in a kitchen, and you told me it was useless.) It did not seem many. You found a metal in it.}. I was in a \index{kniting-mill}kniting-mill. I knitted. I heard knocking. I tied a \index{knot}knot\footnote{We found someone within, and the someone was hard and arduous. It was seen in a fair. It appeared guilty and innocent.}. I watched domestic \index{animal}animals\footnote{A nerve was not in my animal, and it was in a cafe. You told me this cafe was cold.} laboring under heavy \index{burden}burdens. I thought myself an \index{alchemist}alchemist\footnote{Your alchemist was both powerful and powerless.}. I sold laces. I grew dizzy as I ascend a \index{ladder}ladder\footnote{The ladder was a stepladder, and you said that it was not useful. It was seen in a hardware store.}. I ascended a \index{ladder}ladder\footnote{My ladder was a stepladder but not a step ladder, and it was in a toolshed. It was both important and insignificant.}. I saw slimy and uncanny \index{inhabitant}inhabitants\footnote{Our inhabitant was seen in a country. You told me my country was beautiful, and I found a field within. It did not seem expressive.} of the \index{lake}lake\footnote{Our lake was in an outside, and the outside appeared cold and hot. We found a sky there. You said it was a satellite.} rise up and \index{menace}menace me. I saw a dead lamb. I saw \index{lamb}lamb\footnote{This lamb was discovered in a farm, and you said that they were expensive. (I found someone within.)} \index{skin}skins\footnote{You told me our skin was yellow. We saw it in a person. We found a heart in our person, and it was individualist.}. I heard the bleating of \index{lamb}lambs\footnote{We found someone in my lamb. The someone seemed guilty and innocent. It was discovered in a zoo. Dangerous. It was a slave.}. I saw \index{lamp}lamps\footnote{I found our lamp in an office. (This office was ugly.) We found a computer user there.} filled with \index{oil}oil\footnote{Large. It was found in an underground. A well was not in it.}. 

 I lighted a lamp. I carried a lamp. I saw a lamp-post. I fell against a \index{lamp-post}lamp-post\footnote{The lamp-post was in a street corner.}. I was wounded by a \index{lance}lance\footnote{Our lance was not skew.}. I broke a \index{lance}lance\footnote{The lance appeared skew.}. 

 I lost a \index{lantern}lantern\footnote{This lantern was in a campsite.}. I saw a \index{serpent}serpent\footnote{Our serpent was cold-blooded and insensate.} in my \index{lap}lap\footnote{A laptop. We found a tabby cat in it. It was in a laptop.}. I lost one. I killed a \index{lark}lark\footnote{Alive.}. I saw them eating. I studied this \index{language}language\footnote{You said this language was a sheet music. You told me it was simple. I found it in a language barrier.}. I gave it. I saw \index{laundry}laundry\footnote{You saw my laundry in a cellar. You found a spider in my cellar.} \index{wagon}wagons\footnote{A wagon train was in your wagon.}. I waited upon a green \index{lawn}lawn\footnote{Cool. It was a lawn chair but not a garden chair, and my lawn chair was in a lawn.} for the coming of a \index{friend}friend\footnote{Intelligent. You told me they were important. A tv set was not in them, and you saw my tv set in a garage.} or \index{lover}lover\footnote{We found a penis there, and they were seen in a restaurant. You told me your restaurant was crooked.}. I hunted for lead. I entered \index{hall}halls\footnote{My hall seemed dark and light, and it was a hallway. It was in an inside. A calendar was within it.}. I got my \index{ledger}ledger\footnote{The ledger seemed skew. It was in an office.} misplaced. 

 I kept my ledger. I had a \index{woman}woman\footnote{We found the woman in a bed, and the bed was not a cot. This cot seemed absorbent, and it was both flexible and uncompromising. A human was within it.} to keep my ledger. 

 I practised legerdemain. I saw misshapen \index{leg}legs\footnote{Our leg looked yellow, and a legal document was not in it.}. I could n't use my \index{leg}legs\footnote{Fragile. It was discovered in a table, and your table was hazardous and risky. A floor was in it.}. I had a \index{leg}leg\footnote{We found a statement there, and it was seen in a chair. It was yellow.} amputated. I admired me own legs. I drank \index{lemonade}lemonade\footnote{Our lemonade was both liquid and unmelted. It was in a concert, and we found a piano in my concert.}. 

 I ate \index{lemon}lemons\footnote{Your lemon was discovered in a jar. We found a mayonnaise there, and it did not appear large.}. I lent other \index{article}articles\footnote{The article was seen in a newspaper. Lightweight. It looked readable, and you found an editorial there.}. I lent \index{thing}things\footnote{You said our thing was a pillow. This pillow appeared fuzzy, and we found a feather within. We found your feather in a nest. (You told me it was soft.)}. I refused to lend \index{thing}things\footnote{Our thing did not seem heavy. It seemed fuzzy, and an attribute was within it. It was an object but not an aim, and the object was in a desk.}. I lent me \index{article}articles\footnote{The article was found in a newspaper.}. I offered to lend me \index{article}articles\footnote{You found the article in a newspaper.}. I killed one. I was infected with this \index{dread}dread\footnote{You said this dread was not a dreadnought.} \index{disease}disease\footnote{Our disease was a diabetes, and it was contagious. We found it in a lab.}. I saw a registered \index{letter}letter\footnote{Sharp. I found a statement within, and we saw them in a mail.}. I read the \index{letter}letter\footnote{My letter was in an envelope. We found a statement in them. You told me they were thin.}. I failed to read the \index{letter}letter\footnote{The letter was discovered in a mailbox, and you told me they were full. You found a statement there.}. 

 I had my \index{letter}letter\footnote{I found a statement in our letter. You told me they were dull, and I found them in a mailbox.} intercepted. I received a \index{letter}letter\footnote{A statement was not in your letter. (They were sharp.) I saw them in a mail.} written on black \index{paper}paper\footnote{A piece was within my paper, and it was cold but not insensate. A document. (It was seen in a notebook.) Opaque.} with white \index{ink}ink\footnote{A stylus was in the ink. (It seemed blue, and it was a theater ticket but not a theatre ticket.) It was in a well.}. I received a \index{letter}letter\footnote{A statement was in your letter, and you told me our statement was false. It was in a letter.} by \index{hand}hand\footnote{Your hand seemed black, and you found a bone in them. This bone was seen in a hand.}. I mailed. I gave me \index{letter}letters\footnote{You saw the letter in a mail. (My mail was open.) It was important and significant. I found an advertisement in it.} to mail. 

 I conversed with a letter-carrier. I saw a \index{letter-file}letter-file. I ate \index{lettuce}lettuce\footnote{The lettuce was green. It was in a refrigerator. A food was within my refrigerator, and my food was good.}. I gathered it. I thought people was \index{liar}liars\footnote{This liar was in a government.}. I thought my \index{sweetheart}sweetheart a \index{liar}liar\footnote{We saw this liar in a government.}. I was in a \index{library}library\footnote{I found a magazine within. Our magazine was in a table. Your table did not seem hazardous, and you told me it was rigid. It was not a desk.}. I caught \index{louse}lice\footnote{You said that our louse was not small.}. I saw a \index{life-boat}life-boat \index{sinking}sinking. I saw \index{life-insurance}life-insurance men. I saw a dim \index{light}light\footnote{Your light was both useful and useless, and you told me they were off. (They were found in a car, and a passenger was within your car.)}. I saw a \index{lighthouse}lighthouse\footnote{A lantern was in my lighthouse.} through a \index{storm}storm\footnote{We saw our storm in a sea. A summer. It was wide, and we found a blowfish within.}. I saw livid \index{lightning}lightning\footnote{Powerful. (It was seen in a cloud.) My cloud appeared fluffy.} parting black \index{cloud}clouds\footnote{We found an aeroplane within. You told me it was light, and it was in a sky.}. I saw \index{lightning}lightning\footnote{I saw my lightning in a cloud, and I found a marmot in this cloud. You told me it was black.} in the south. I saw a \index{lightning-rod}lightning-rod. I limped in my \index{walk}walk\footnote{Your walk was healthy but not goodish. It was restful. I found someone in it.}. I saw others limping. I saw \index{linen}linen\footnote{The linen was in a cabinet, and you found a bowl within. It was large and bombastic.}. 

 I dressed in \index{linen}linen\footnote{A bed sheet, and your bed sheet was in a bed.} \index{garment}garments\footnote{A coat. The coat was discovered in a backpack, and I found a flashlight in this backpack.}. I subdued the \index{lion}lion\footnote{The lion was feline. You found them in a veldt, and a gazelle was within your veldt. Your gazelle was cool.}. I saw a \index{lion}lion\footnote{You found my lion in a paint. A cub. Feline. A gazelle was within them, and they were strange.}'s \index{head}head\footnote{You found a hair in your head. (They were in a shoulder.)} over me. I rode one. I fell under a load. 

 I put a \index{lock}lock\footnote{A door was within your lock, and it was not a padlock.} upon my \index{fiance'e}fiance'e's neck and arm. I had lockjaw. I heard one coming. I lost in a \index{lottery}lottery\footnote{A ticket was in this lottery.}. I played on one. 

 I saw a mad \index{dog}dog\footnote{You told me our dog was agile, and a dog pound was not in them. You said that they were not cool. They were in a house. (You said they were a golden retriever.)}. I saw a \index{madstone}madstone applied to a \index{wound}wound\footnote{We found a bullet in our wound. It was in a war.} from the fangs of some mad \index{animal}animal\footnote{We saw your animal in a cafe. I found a waiter within.}. I saw others practising this \index{art.}art. I was in a \index{mansion}mansion\footnote{This mansion was in a city. A jewelry was in it. It was not good.} where there was a haunted \index{chamber}chamber\footnote{A cello was not in this chamber, and the cello was in an orchestra.}. 

 I saw a \index{mansion}mansion\footnote{My mansion was comfy and comfortable, and a foyer was not in it. It was seen in a city.} from distant points. I saw a \index{mantilla}mantilla. I saw it broken. I marched to the \index{strain}strains\footnote{Your strain was seen in a school, and it was deadly and lethal.} of \index{music}music\footnote{We saw my music in a night club. A rap. Dangerous. (You found someone within.) It was both good and evil.}. 

 I saw \index{man}men\footnote{This man was both emotional and cerebral. I found a mansion in them. (You said they were a boy.) They were strong, and we found them in a bedroom.} marching. I saw \index{marigold}marigolds. I was a \index{mariner}mariner\footnote{My mariner was seen in a sea.}. I saw my \index{vessel}vessel\footnote{Your vessel was discovered in a harbor, and a boat was in your harbor. It was not a home.} \index{sailing}sailing without me. I saw decayed \index{vegetable}vegetables\footnote{I found the vegetable in a grocery store. You found a vegetable garden in it.} or \index{meat}meat\footnote{You saw this meat in a food. You told me the food was edible. A meat was within it. A butter.}. I felt myself drawn up toward the \index{planet}planet\footnote{This planet was in a space, and my space seemed big and little. I found a meteor in it, and you said it was a hallway. It was loud but not cheap.}. I was a \index{martyr}martyr\footnote{You found a letter opener there. They were small and lowly.}. I saw others masking. 

 I saw a mask. I attended a \index{masquerade}masquerade. I participated in a masquerade. 

 I saw the \index{mast}masts\footnote{Your mast appeared rectangular, and it was a poet. You told me our poet was ugly. They were in a classroom, and we found a person within.} of wrecked \index{ship}ships\footnote{This ship was discovered in a shipwreck. Safe. (I found a person within.) It was not a schooner.}. I slept on a new \index{mattress}mattress\footnote{The mattress was evil, and it was in a loft.}. I had \index{measles}measles\footnote{You said that the measles was illegal.}. I lost a \index{medal}medal\footnote{Our medal was shiny.}. I gave \index{medicine}medicine\footnote{A medicine cabinet was in our medicine.} to others. I saw others making a \index{memorandum}memorandum. 

 I visited a menagerie. I mended. I received a \index{message}message\footnote{This message was a mail but not a chain armour. The mail was open, and I found it in a fridge. I found a food within. It seemed cold.}. I killed \index{mouse}mice\footnote{A computer mouse was within the mouse. They were discovered in a computer. A keyboard. They appeared mechanical, and you told me they were complex.}. I saw milk in large \index{quantity}quantities\footnote{Your quantity was a number but not a routine, and we found a safety in my number. (The safety was handy but not ready to hand.)}. I saw a miller. I owned a \index{mine}mine\footnote{A dynamite was within my mine. Mineral. It was both many and few, and it was discovered in a mountain.}. I was a \index{minister}minister\footnote{You found the minister in a parliament. Someone was not in the parliament.}. I saw others in a \index{mirror}mirror\footnote{A house was within our mirror, and you said the house was not a brownstone. White. It seemed expensive, and it was in a subdivision.}. I was miserly. 

 I was enveloped in a \index{mist}mist\footnote{My mist was exclusive, and it was found in a mistake. (You said that it was not mean.) A mistake.}. I saw others in a \index{mist}mist\footnote{You saw this mist in a checkbook. It appeared exclusive. You said it was not an accident, and you said that this accident was not bad.}. I caught a \index{mole}mole\footnote{My mole was in an underground, and a molecule was in them. (An ozone.)}. I saw \index{mole}moles\footnote{Our mole was seen in an underground, and your underground was enjoyable but not gratifying. I found a root within.}. I payed out \index{money}money\footnote{A purse was within this money. Your purse was a handbag but not a purse. Our handbag was in a store, and you said that it was blue.}. I counted my \index{money}money\footnote{You said this money was a time, and you told me it was fake. (You saw it in a supermarket.) I found a bag there.} and find a \index{deficit}deficit. I stole \index{money}money\footnote{My money was in a wallet. (A home was in it.) A mansion. This mansion appeared controversial.}. I saved money. I swallowed \index{money}money\footnote{I saw our money in a safe, and my safe was an archway but not an arch. You told me it was useless. A drawstring bag was not in it.}. I found a roll of currency. I was a \index{monk}monk\footnote{You told me our monk was funny, and they were discovered in a jungle. A monkey. We found a tail there.}. I feeed a \index{monkey}monkey\footnote{My monkey was funny, and they were in a jungle. (We found a sloth within.)}. I saw the new \index{moon}moon\footnote{A footprint was in this moon. It was man-made. It was in an orbit, and you told me it was round.}. 

 I saw a blood red \index{moon}moon\footnote{Someone was not in your moon. It seemed romantic, and it was in a space. It was round and pear-shaped.}. 

 I saw many \index{corpse}corpses\footnote{Our corpse was in a graveyard.} there. I gave a \index{mortgage}mortgage\footnote{Our mortgage was found in a mortgage loan.} on my property. I lost a \index{mortgage}mortgage\footnote{You found this mortgage in a mortgage loan.}. I saw my \index{mother}mother\footnote{Your mother was hard to please but not hard-to-please. You told me they were androgynous. They were found in an apartment, and I found a stair there. Our stair was not a staircase.} as I appeared in the \index{home}home\footnote{A sofa was not in this home. You told me this sofa was uncomfortable. A couch. Your couch was uncomfortable. It was in a rest area.}. 

 I saw one's mother emaciated or dead. I ascended a \index{mountain}mountain\footnote{An alp. A climber was not in it. My climber was in a mountain.}. I saw it full of \index{mouse}mice\footnote{Your mouse was warm but not tender. You told me they were constructive. They were in a kitchen, and you found a pantry in my kitchen.}. I set a \index{trap}trap\footnote{A drum was in the trap, and I saw the drum in a symphony.}. I walked in \index{mud}mud\footnote{Our mud was in a riverbed. Opaque. You found a stick in it.}. 

 I saw \index{mud}mud\footnote{Our mud was opaque but not unintelligible, and a stream was not in it. Our stream was shallow, and it was discovered in a streamer.} on my \index{clothing}clothing. 

 I wore a \index{muff}muff\footnote{Your muff was in a cupboard. A dish was not in your cupboard.}. 

 I saw my \index{sweetheart}sweetheart wearing a muff. I saw \index{mulberry}mulberries\footnote{A weasel was within your mulberry, and it was not ugly.}. I was kicked by a \index{mule}mule\footnote{You found the mule in a farm. It did not appear hairy, and it seemed sterile.}. I heard harmonious \index{music}music\footnote{I found a bass clarinet there, and our bass clarinet was found in an orchestra.}. I saw musical instruments. I was a \index{mute}mute. I saw \index{myrtle}myrtle\footnote{The myrtle was fragile and delicate.} in \index{foliage}foliage\footnote{This foliage was in a forest, and I found a stream there. You told me my stream was shallow.} and \index{bloom}bloom\footnote{You said your bloom was not an apple tree. You found a bee within.}. I saw it withered. I saw \index{nail}nails\footnote{My nail was flammable, and it was found in a jar. A mayonnaise was not in my jar.}. I dealt in \index{nail}nails\footnote{Flammable. (I found someone within.) My someone was in a lake, and it was not a student.}. I was naked. I was nearsighted. I saw my own \index{neck}neck\footnote{A pain was not in the neck. It was in a guillotine.}. I lost a \index{necklace}necklace\footnote{This necklace was a choker but not a dog collar, and you said that this choker was not valuable. You saw them in a jewelry store.}. I was in need. I used a \index{needle}needle\footnote{The needle was found in a haystack, and you told me it was sharp.}. I found a needle. I broke one. I saw a \index{mulatto}mulatto. I saw an empty \index{nest}nest\footnote{We found a weasel there.}. I ensnared \index{anything}anything\footnote{The anything was a ladder but not a run, and it was discovered in a container. (You found a stuff there.) Infinite.} with a \index{net}net\footnote{Our net was good, and we found a bicycle within. My bicycle was found in a city.}. I walked among \index{nettle}nettles without being stung. I heard a strange \index{noise}noise\footnote{You said that your noise was not funny, and we saw it in a movie theatre. (You told me the movie theatre was light.) A ticket booth was not in it.}. I saw my own \index{nose}nose\footnote{This nose was a lip. We found a spout there, and your spout was in a garage.}. I felt a numbness creeping over me. I discarded the \index{robe}robes\footnote{I saw your robe in a suitcase. Loud.} of my \index{order}order\footnote{An order book was in this order.}. I was a \index{nurse}nurse\footnote{My nurse was in a hospital. You found a nursery there.}. 

 I saw my wife \index{nurse}nurse\footnote{We found a nursery within, and they were seen in a clinic. This clinic appeared educational.} their \index{baby}baby\footnote{My baby was creative and originative, and I found a comforter there. (Your comforter was not a duvet, and they were warm.) They were found in a bed.}. I ate them. I saw \index{nymph}nymphs \index{bathing}bathing in clear \index{water}water\footnote{You said that our water was not fleet. A steam. (You found a steam room in this steam, and it was in a university.)}. 

 I saw an \index{oak}oak\footnote{I saw the oak in an oak tree.} full of \index{acorn}acorns\footnote{The acorn was in a roof.}. I lost an oar. I took an \index{oath}oath. I prepared it for the \index{table}table\footnote{You said this table was not a desk. We found a silverware in it, and it appeared rigid and nonrigid. It was discovered in a restaurant. It was hazardous.}. I stood at the \index{base}base\footnote{You told me my base was nice, and it was in a baseball. (It was dangerous but not grievous.) We found a dry in it.} of an obelisk. I read one. I obligated myself in any \index{incident}incident. I was far out on the \index{ocean}ocean\footnote{I found a lobster in the ocean. Our lobster was in an ocean.}. I allowed \index{wading}wading. 

 I saw the \index{ocean}ocean\footnote{A ship was in your ocean, and it seemed blue. I found it in a planet, and my planet was round.} so shallow as to allow wading. I sailed on the \index{ocean}ocean\footnote{A ship was not in your ocean. This ship was not a junk, and it was in a shipwreck. It seemed safe.} when it was calm. I was offended. I gave. I was turned out of \index{office}office\footnote{Your office seemed illegal, and I found a chair there. (I found your chair in a floor.)}. I saw the offspring of domestic \index{animal}animals\footnote{We found our animal in a wild. You found a chest in it.}. I was anointed with \index{oil}oil\footnote{Your oil was not a motor oil. It was in an underground. We found a coal there, and the coal seemed black.}. I dealt in it. I took them from \index{bottle}bottles\footnote{You said that our bottle was large, and it was recyclable. I found a shampoo within, and I found this shampoo in a shower.}. I broke a \index{bottle}bottle\footnote{A pill was within my bottle, and it was large and enceinte. It was recyclable, and you said it was a carafe. We found the carafe in a restaurant.} of \index{olife}olives. I ate them. I saw \index{omelet}omelet\footnote{You found an egg in my omelet, and you said that this egg was yummy.} being served. 

 I was being drawn through the \index{street}streets\footnote{An avenue. (You said that it was not rural, and it seemed dark.) You found it in a city, and a manhole cover was within it.} in an \index{omnibus}omnibus. I ate them. I was cutting \index{onion}onions\footnote{My onion was seen in a table, and I found a food in my table. It was hazardous and wild. Small. You said it was not a desk.} and feel the escaping \index{juice}juice in my \index{eye}eyes\footnote{An eyeglass was within your eye. The eyeglass looked portable, and you saw it in a breast pocket.}. I attended an opera. 

 I slipped on an \index{orange}orange\footnote{We saw your orange in an orange juice, and this orange juice was orange. It did not seem fluid.} peel. I saw a \index{storm-swept}storm-swept \index{orchard}orchard\footnote{A fruit tree was in my orchard.}. I heard the \index{music}music\footnote{You told me your music was sound. It did not seem funny, and we found it in a movie. A projector was in your movie. It was not a thriller.} of an \index{orchestra}orchestra\footnote{You said our orchestra was an oboe, and the oboe was found in a cabinet.}. I heard the pealing forth of an \index{organ}organ\footnote{You said our organ was a lung. An air was not in the lung. Translucent. You said that it was flammable.} in grand anthems. I saw an \index{organ}organ\footnote{Your organ was a heart, and our heart was seen in a cadaver. I found an artery there. You told me it was genetic.} in a \index{church}church\footnote{This church was white but not bloodless. You told me it was quiet, and you found an aisle there. (Your aisle was not a lane, and it was in a store.)}. I heard doleful \index{singing}singing and \index{organ}organ\footnote{You said my organ was a lung. It was found in a human body, and my human body was fragile. We found an artery in it.} \index{accompaniment}accompaniment. I wore \index{ornament}ornaments\footnote{Your ornament was in a windowsill, and it was a bow but not a stem.}. 

 I worked on an ouija \index{board}board\footnote{A committee was in my board. Our committee was discovered in a meet.}. I failed to work. 

 I worked. I saw fat oxen in green \index{pasture}pastures\footnote{Our pasture was both pure and impure, and I found a mouse in it. It was in a countryside.}. I saw a dead ox. I ate \index{oyster}oysters\footnote{The oyster was discovered in an ocean, and the ocean was salty. You found a ship within.}. I saw a \index{pagoda}pagoda\footnote{My pagoda was large and big.}. I was carrying a \index{pail}pail\footnote{I found my pail in a playpen.}. I saw others in \index{pain}pain\footnote{You said our pain was not an ache. The ache was decorative but not ornamental.}. I saw newly painted houses. I saw and heard fine \index{lady}ladies\footnote{This lady looked sexy and unsexy, and they were hot but not red-hot. I found them in a city. (A jewelry was within them.)} and \index{man}men\footnote{You said your man was not a boy. They were not intelligent, and they were found in a truck. You found a menu there. It was hygienic.} \index{dancing}dancing and conversing. I was a \index{participant}participant in the entertainment. I saw a pall. I was afflicted with \index{palsy}palsy\footnote{My palsy was deadly.}. I saw my \index{friend}friend\footnote{Our friend was important, and they were in a school. I found a girl within, and you said that it was not big.} so afflicted. 

 I talked to a \index{person}person through a \index{pane}pane of glass. I saw \index{pantomime}pantomimes\footnote{The pantomime was both dark and light.}. 

 I had occasion to refer to. I referred to. I started to Paradise and find myself bewildered and lost. I received pardon. I owned a \index{parrot}parrot\footnote{Your parrot was cute but not precious, and you saw them in a zoo. We found a zebra there.}. I saw my \index{business}business \index{partner}partner\footnote{The partner was a marriage.} with a \index{basket}basket\footnote{The basket was large and big, and you told me it was nonspherical. We found a fruit within, and you found it in a home.} of \index{crockery}crockery\footnote{My crockery was discovered in a cupboard.} on my \index{back}back\footnote{You told me this back was important, and a rosebush was within them. You saw the rosebush in a flower bed.}. I ate them. I saw \index{passenger}passengers\footnote{My passenger was not stupid, and I saw them in a bus stop. (I found someone in your bus stop.)} coming in with their \index{luggage}luggage\footnote{A bag was not in this luggage, and you told me your bag was tender. They were discovered in a supermarket, and you said that they were not large.}. I ate it. I saw one. I saw or manufacture \index{patent}patent\footnote{My patent was seen in a medicine chest. I found a barbiturate in your medicine chest.} \index{medicine}medicines\footnote{We saw your medicine in a jar. (You found a peanut butter in this jar, and it did not appear large.)}. I walked through a \index{pathway}pathway\footnote{My pathway was human.} bordered with green \index{grass}grass\footnote{Our grass appeared green and ripe, and we found them in a field. They were a wheat but not a pale yellow, and my wheat was edible and eatable. (You found a wheat field in it.)} and \index{flower}flowers\footnote{Green. It was a violet, and it was found in a table. (A floor was in my table.) Level.}. I saw a large \index{paunch}paunch. I saw a shriveled \index{paunch}paunch. I saw \index{pauper}paupers\footnote{The pauper was alive but not live, and they looked rich.}. I entered a \index{pawn-shop}pawn-shop. I redeemed an \index{article}article\footnote{We saw our article in a newspaper. Skew. It did not seem lightweight.}. I saw a \index{pawn-shop}pawn-shop. I saw dried \index{peach}peaches\footnote{My peach was in a jar. You said that this jar was large. You found a food in it.}. 

 I owned \index{peacock}peacocks\footnote{My peacock was in a wale.}. I preserved them. I saw dried peas. 

 I ate dried peas. I saw them growing among \index{leaf}leaves\footnote{The leaf appeared different, and we found an insect in it. We saw the insect in an air. They did not seem strange, and they were not a ladybug.}. I caught one. I had \index{penalty}penalties\footnote{The penalty was not an execution.} imposed upon me. I payed a \index{penalty}penalty\footnote{This penalty did not appear nonsense, and I found it in a penalty box. (It was an execution.)}. I found them. I drew a \index{pension}pension\footnote{A pension fund.}. I failed in my \index{application}application\footnote{A menu was within your application. My menu was in an application.} for a \index{pension}pension\footnote{You said your pension was not a pension fund.}. 

 I saw red \index{pepper}pepper growing. I saw \index{pile}piles\footnote{A duffel bag was within your pile, and it was in a garage.} of red \index{pepper}pepper\footnote{You found this pepper in a kitchen, and a kitchen utensil. This kitchen utensil was heavy.} \index{pod}pods\footnote{You found someone in the pod, and it was both large and little. It was a podiatrist but not a foot doctor.}. I put it on my \index{food}food\footnote{A soup. You found our soup in a cupboard. It appeared edible, and you found a monkey in it.}. I saw it growing. I spilt perfume. I was distilling perfume. I perfumed my \index{bath}bath\footnote{My bath was in a house, and I found a bathroom within. You told me this bathroom was clean, and you said it was not a bidet. (It was both dark and light.)}. I saw new \index{petticoat}petticoats\footnote{A crinoline was in the petticoat.}. I saw phosphorus. I saw \index{photograph}photographs\footnote{A scenery was not in our photograph, and it was a photo but not an exposure. Two-dimensional. I saw it in a shelf. It was blurry.}. I saw a \index{piano}piano\footnote{We found someone within, and you told me it was blue. You said it was not a clavichord. You saw our clavichord in a parlor.}. I was eating them. I made a \index{picture}picture\footnote{Someone was in your picture. An image. Blurry.}. I destroyed pictures. 

 I saw my \index{likeness}likeness in a living \index{tree}tree\footnote{You found a leaf in the tree, and you told me it was unanimated. It was in a mountain. (The mountain was not an alp.)}. I made pies. I saw them being used in a \index{shooting}shooting match. I saw them flying. I was a pilgrim. I took \index{pill}pills\footnote{We saw our pill in a pharmacy. You told me this pharmacy was antonymous. It was not a drugstore, and someone was in this drugstore.}. I gave them to others. I saw a \index{pine}pine\footnote{The pine was seen in a jar. We found a fungus in it.} \index{tree}tree\footnote{A pine tree, and someone was not in it. Alive. (You found it in a forest, and you told me the forest was cool.)}. I swallowed a \index{pin}pin\footnote{You found your pin in a pizza. A pincushion was not in it.}. I lost one. I stuck one into my \index{flesh}flesh\footnote{My flesh was in an inside, and you said it was a meat. It seemed sour and sweet. It appeared green.}. I was a \index{pirate}pirate\footnote{This pirate was in a sea, and we found a batten in them. (Rich.) They appeared stupid.}. I owned one. I was attacked by some \index{person}person using a pitchfork. I crossed a \index{plain}plain\footnote{You told me your plain was dry, and a gazelle was in it. You saw our gazelle in a zoo.}. I had \index{plaster}plaster fell upon me. I saw \index{plasterer}plasterers at \index{work}work\footnote{Our work was in an office. A pen was not in the office. (My pen was not heavy.) It was fancy. You said it was not a marker.}. 

 I attended a play. 

 I saw persons plowing. I plowed myself. 

 I saw them ripe. I gathered them. I found a \index{pocketbook}pocketbook\footnote{We found a shoulder bag in my pocketbook.} filled with \index{bill}bills\footnote{You found a billfold in my bill, and I saw it in a mail. It appeared hard.} and \index{money}money\footnote{You told me this money was fake, and a billfold was not in it. My billfold was seen in a pocket.}. I threw the \index{poison}poison\footnote{Our poison was a wine but not a vino. This wine was in a bottle. You told me the bottle was recyclable.} away. I handled \index{poison}poison\footnote{Your poison was found in a chemistry lab. (It was a wine but not a wine-colored.)}. I recovered from the \index{effect}effects\footnote{This effect was difficult.} of \index{poison}poison\footnote{A wine. (It was in a chemistry lab, and this chemistry lab was dark and dour.)}. I took \index{strychnine}strychnine or other poisonous medicine under the \index{advice}advice of a physician. I killed one. 

 I took \index{interest}interest\footnote{You said that my interest was not false. (A satisfaction was not in it.)} in politics. 

 I saw the Pope. I inhaled the \index{odor}odor\footnote{This odor was seen in an air.} of one. I discharged one. I tried to use cancelled \index{stamp}stamps\footnote{My stamp appeared useful and useless. You found it in a mail.}. I used cancelled \index{stamp}stamps\footnote{The stamp was found in a desk. You told me your desk was opaque.}. I saw \index{torn}torn\footnote{I found a tornado in your torn, and we found it in a tornado. The tornado was mild but not meek. Loud. It was a waterspout but not a downpour.} \index{stamp}stamps\footnote{Our stamp looked useful and useless. It was discovered in a desk.}. I cooked them. I saw them rotting. I saw \index{powder}powder\footnote{We found a cornstarch there.}. I heard preaching. I argued with a \index{preacher}preacher\footnote{Your preacher was not weird, and we saw them in a cathedral.}. I saw one \index{walk}walk\footnote{Someone was within my walk. (It seemed healthy and unhealthy.) It appeared good for you.} away from me. I saw a long-haired \index{preacher}preacher\footnote{This preacher was discovered in a cathedral. We found a bishop in my cathedral, and it seemed educational.}. I fell over a \index{precipice}precipice\footnote{Your precipice did not appear small.}. I confessed to a \index{priest}priest. I was in a \index{printing}printing \index{office}office\footnote{We found our office in a downtown. It was ugly. A telephone was within it.}. I saw any one dismissed from \index{prison}prison\footnote{The prison was a jail, and the jail was in a county courthouse. You found a human within.}. 

 I saw others promenading. I was in the \index{company}company\footnote{You found an employee there. A startup. They were found in a build.} of a \index{prostitute}prostitute. 

 I was in a \index{pulpit}pulpit\footnote{You said that your pulpit was not deadly. It was discovered in a cathedral.}. I felt the \index{pulse}pulse of another. I saw a broken pump. 

 I was punching any person with a \index{club}club or fist. I saw a quack \index{doctor}doctor\footnote{A thermometer was not in the doctor. Your thermometer was seen in a cabinet.}. I was in a quagmire. I ate them. I saw or hear a \index{quartette}quartette. I saw \index{vessel}vessels\footnote{Your vessel was not a bottle, and it was in a port.} while standing on the \index{quay}quay\footnote{Our quay was both powerful and powerless.}. I found myself in \index{quicksand}quicksand. I was afflicted with this disease. I saw \index{rabbit}rabbits\footnote{Your rabbit was pure. (It was in a forest.) My forest appeared pretty, and I found a stick there.} frolicing about. I ate them. I was in a \index{rage}rage\footnote{The rage seemed educational.} and scolding and tearing up \index{thing}things\footnote{A fungus was not in our thing, and it was found in a place. (It was solid and strong.) You said it was not a house. You told me the house was white.} generally. I saw others in a \index{rage}rage\footnote{This rage was enjoyable but not pleasurable.}. I saw an \index{obstruction}obstruction on these \index{road}roads\footnote{We found a possum in your road, and I found my possum in a road. This road was not a street. (Rural.) It appeared dark and light.}. I walked the \index{cross}cross\footnote{Your cross was seen in a crossroad. I found someone within, and my someone was not dangerous. A slave. Bad.} \index{ty}ties\footnote{A typewriter ribbon was not in our ty, and you said it was a typeface. The typeface was weird but not eldritch.} of a \index{railroad}railroad\footnote{A railroad car. (It was discovered in a railroad track.)}. 

 I saw a \index{road}road\footnote{My road looked grey. It did not seem dangerous. (A highway.) I found your highway in a country, and someone was not in it.} inundated with clear \index{water}water\footnote{Our water was found in a toilet, and a toilet paper was not in my toilet. (It was a restroom.)}. I saw and hear \index{rain}rain\footnote{Our rain was cold. It was in a weather. A drizzle. A gazelle was in it. (It was hot.)} approaching. I found myself regretting some \index{duty}duty\footnote{My duty was both ugly and beautiful. (It was in an airport.)} unperformed while listening to the \index{rain}rain\footnote{Our rain seemed wet. (We found a lemur in it, and it was a shower.) It was in a raindrop.}. I saw it \index{rain}rain\footnote{This rain looked cold and hot. (A rain forest was in it, and our rain forest did not seem distinct.)} on others. I got my \index{clothe}clothes\footnote{A velvet was within your clothe. You said that this velvet was drunk. (You told me it was rough.) We saw it in a jewelry store.} wet and soiled while out in a \index{rain}rain\footnote{A marmoset was within your rain. You said that it was cloudy. (It was cold, and we saw it in a street.) You said this street was an avenue.}. I ate them. I killed one. I fell into a \index{rat-trap}rat-trap. I saw an empty \index{one}one\footnote{A football field, and I found it in a house. You found a wall in our house, and this wall seemed white.}. I cut myself with one. I saw idle ones. I put \index{ice}ice\footnote{The ice was solid, and it was cold and inhuman. It was discovered in a supermarket. An egg was not in your supermarket.} in one. I payed \index{rent}rent\footnote{I found my rent in a renter.}. I could n't pay my \index{rent}rent\footnote{Your rent was in a city.}. I was under \index{sentence}sentence\footnote{My sentence was not a penalty, and your penalty appeared nonsense. It was in a penalty box.} and receive a \index{reprieve}reprieve. 

 I heard of others resigning. I attended a religious \index{revival}revival. I took a \index{part}part\footnote{We found a party in my part, and it was healthy. We found it in a party.} in it. I ate it. I saw \index{rib}ribs\footnote{Your rib was in a ribbon. It was a ribbon but not a palm. You told me it was gay.}. I saw it mixed with \index{dirt}dirt\footnote{I saw our dirt in a bed, and a human was within the bed. You told me it was big. It was flammable. It was a cot but not a camp bed.} or otherwise impure. 

 I was possessed of \index{rich}riches\footnote{Your rich seemed evil, and it appeared big. We found a condominium there, and this condominium was found in a complex. A build.}. I solved \index{riddle}riddles\footnote{The riddle was discovered in a newspaper.}. I was trying to solve \index{riddle}riddles\footnote{Your riddle was discovered in a newspaper, and I found an opinion in this newspaper. Lightweight. It looked light.}. 

 I rode slowly. I received a \index{ring}ring\footnote{You found a diamond in your ring. (Our diamond was translucent.) It appeared expensive, and it was in an engagement ring.}. I had \index{ringworm}ringworms appeared on me. I saw them on others. I rose to high \index{position}positions. I found myself rising high into the \index{air}air\footnote{My air looked clear. (A pollution was not in it, and you said this pollution was an air pollution.) My air pollution was evil but not malign.}. I was water-bound by the overflowing of a river. I lost the \index{road}road\footnote{You said my road was a parkway, and our parkway was found in a city. (A movie house was in the city.)}. 

 I saw a \index{mother}mother. I saw or think myself a rogue. I was in a rogue's \index{gallery}gallery\footnote{We found a paint in your gallery, and my paint appeared empty. I found it in a wall. It appeared decorative.}. I saw Roman \index{candle}candles\footnote{An egg. You told me this egg was white. (It was in a supermarket.) You found a food in my supermarket.}. I saw a \index{roof}roof\footnote{Your roof seemed red. (You found a fiddler in it.) Mean. You saw them in a roof.} falling in. I repaired. I saw \index{rooster}roosters\footnote{My rooster was found in a farm, and we found a heifer in my farm. It looked silly.} fighting. I saw \index{root}roots\footnote{I saw our root in a root beer. A root cellar was in them.} of \index{plant}plants\footnote{Our plant was in a field, and a lizard was within them. A skink.} or \index{tree}trees\footnote{You told me your tree was green, and you found a leaf there. You said it was not an apple tree, and it was found in a garden. Organic.}. 

 I used them as \index{medicine}medicine\footnote{The medicine was seen in a refrigerator. You found a medicine cabinet within, and it was colorful.}. I climbed one. I decended a \index{rope}rope\footnote{We found a nylon in your rope. Your nylon was in a drawer. You told me it was synthetic.}. I broke them. I let a rope down from an upper \index{window}window\footnote{My window appeared transparent. I saw it in a house. You said that your house was not large. I found a wall within. A mansion.} to people below. 

 I inhaled their \index{fragrance}fragrance\footnote{The fragrance was ugly but not atrocious.}. I wore or saw \index{rosette}rosettes\footnote{Your rosette was weird but not eldritch.} on others while. I used rouge. I saw others with it on their faced. I saw it on my \index{hand}hands\footnote{A bone was within our hand. They appeared valuable and worthless, and they were in a keyboard. A keyboard instrument.}. 

 I found that my \index{limb}limbs\footnote{A leg. A statement was within your leg.} will stretch like \index{rubber}rubber\footnote{Yellow. It was a balloon, and it was seen in a wallet.}. I drank \index{rum}rum\footnote{The rum was powerful and hefty. It was not a ruminant.}. I ran in \index{company}company\footnote{You found your company in a city. (We found an employee in them.) This employee did not seem fragile.} with others. I ran from \index{danger}danger\footnote{We found your danger in a garage, and you told me it was beautiful. It was a pollution but not a contamination.}. I saw \index{stock}stock\footnote{A stockade was not in our stock. (Risky.) It was found in a newspaper.} running. I was ruptured. 

 I saw \index{stock}stock\footnote{You told me my stock was old. It was in a newspaper, and a headline was within my newspaper.} entering \index{rye}rye \index{field}fields\footnote{This field did not seem breathtaking. It was a prairie, and we found a wheat in it. Your wheat was discovered in a field.}. I passed at the \index{end}end\footnote{Your end seemed good and bad, and I found them in an endpoint. They were a stop but not a point. A hook was not in them.} of the two full \index{year}years\footnote{Your year was seen in a trunk.}. I unlocked a safe. I was trying to unlock a safe. I drank a tea made from saffron. 

 I sailed on a small \index{vessel}vessel\footnote{The vessel was a bottle but not a nursing bottle. We found it in a port.}. I made it. I wore a \index{sash}sash\footnote{You said the sash was a cummerbund.}. I lost a saw. I heard the buzz of a saw. I found a rusty saw. I saw any \index{one}one\footnote{A kitchenette was not in my one, and it was discovered in a room. You said it was not a football field.} with a scaldhead. I was scalded. I weighed on \index{scale}scales\footnote{Your scale was discovered in a bathroom. You said the bathroom was a bidet, and my bidet was both strong and impotent.}. I wielded a \index{sceptre}sceptre. I imagined that I wield a \index{sceptre}sceptre. I attended \index{school}school\footnote{The school was found in a neighborhood. A neighbor was in this neighborhood.}. I had my scissors sharpened. I broke them. 

 I scratched others. I was scratched. I heard the lonely sighing of the \index{sea}sea\footnote{You said our sea was a search engine.}. I saw \index{seal}seals\footnote{My seal was hairy. (It was in a beach.)}. I visited a \index{seaport}seaport. I saw \index{member}members\footnote{You told me our member was cheap. They appeared antibiotic. (They were seen in a cabinet.) A dish was within your cabinet.} of the \index{sect}sect\footnote{Our sect was in a section, and we found a section in it.} called Shakers. I imagined me belong to them. I shook \index{hand}hands\footnote{My hand was subjective, and we found a briefcase in them. (I found them in a pant.)} with some prominent \index{ruler}ruler\footnote{You said your ruler was not a queen. They seemed straight, and you said that they were safe. I saw them in a cabinet.}. I had my own \index{head}head\footnote{You found a mouth there, and you told me they were big. They were in a morgue.} shampooed. 

 I saw a \index{shark}shark\footnote{A tooth was in the shark, and you told me they were little. You saw them in a zoo.} pursuing and attacking me. I saw a dead one. I was being shaved. I saw \index{man}men\footnote{You told me my man was unhappy, and they were both mortal and immortal. You saw them in a build. The build was not a house. You found a stair within.} \index{shaving}shaving. I saw \index{shears}shears. I saw them broken. I saw \index{flock}flocks\footnote{A blowfish was not in our flock. (I found it in a roof, and our roof appeared red.) You said that it was not flat.} of \index{sheep}sheep\footnote{The sheep did not seem strange. A wool was within them, and they were discovered in a farm.}. I ate the flesh of sheep. 

 I saw them in \index{idleness}idleness. I was elected \index{sheriff}sheriff\footnote{The sheriff did not appear mean.} or felt interested in the \index{office}office\footnote{You told me our office was messy. (We found a telephone in it.) You saw it in a city.}. I imagined that I was elected \index{sheriff}sheriff\footnote{Our sheriff did not seem strange.} or felt interested in the \index{office}office. I lost my \index{life}life\footnote{The life was precious, and they were not a person. A bone was in this person, and it was in a hospital.} in one. I saw a \index{ship}ship\footnote{The ship was found in a port, and it appeared safe and dangerous. Someone was in it. An oil tanker.} on my \index{way}way\footnote{A human was in our way. You said that my human was hairy. It appeared selfish and unselfish. It was seen in a home. This home was a mansion.} through a tempestuous \index{storm}storm\footnote{Your storm was scary. A thunderstorm. Your thunderstorm seemed dangerous.}. I saw others shipwrecked. I putted on my \index{shirt}shirt\footnote{A button was within this shirt, and the button seemed round. It was in a jacket.}. I saw a \index{shoemaker}shoemaker. I saw my \index{shoe}shoes\footnote{We saw your shoe in a store. (A foot was not in it.) A sandal.} ragged and soiled. I found them untied. I lost them. I shot both \index{barrel}barrels\footnote{You said that our barrel was not large, and it was in a market. We found a bread in my market.} of a double-barreled \index{shotgun}shotgun\footnote{Your shotgun was in a roadblock, and a barricade was within our roadblock.}. I saw my own \index{shoulder}shoulders\footnote{You found our shoulder in a shoulder bag.} appearing thin. I saw shrouded \index{corpse}corpses\footnote{This corpse was in a funeral, and our funeral appeared sad. It was a funeral director but not a mortician.}. I saw a shrouded removed from a corpse. I was in a \index{siege}siege. I was skating on \index{ice}ice\footnote{This ice was transparent. It was seen in a hockey game, and we found an injury in my hockey game.}. I saw others skating. 

 I saw \index{skate}skates\footnote{Your skate was a hockey skate.}. I saw a \index{skeleton}skeleton\footnote{The skeleton was in a museum. An artifact was not in our museum.}. I saw a \index{friend}friend\footnote{You told me my friend was unimportant. They were seen in a school, and they did not seem mortal. I found a chair in them.}'s \index{skull}skull\footnote{You saw the skull in a skullcap. You said it was a craniotomy.}. 

 I saw my own \index{skull}skull\footnote{My skull was seen in a skullcap.}. I saw the \index{sky}sky\footnote{I found a planet in the sky. (You said that my planet was round.) Big. They were in a sky.} \index{turn}turn\footnote{Yellow. It was discovered in a turnpike, and you found a turnstile there.} red. I was slandered. I saw others sleeping. I saw a \index{sleigh}sleigh\footnote{A sleight was not in this sleigh. It was seen in a sleight.}. I slid. I slid down a \index{hillside}hillside\footnote{Your hillside seemed ugly.} covered with green \index{grass}grass\footnote{You told me your grass was ripe. (They were both organic and inorganic.) I found a front yard there. A wheat. They were found in a grind.}. I saw them wriggling and falling over others. I handled them. I saw \index{hair}hairs\footnote{Our hair looked thin and fat, and we found a hairpin within. It was an eyebrow. It was seen in a drain.} turned into snakes. 

 I saw them bite others. I saw little \index{snake}snakes\footnote{You said your snake was not a rattler, and they seemed black. They did not seem cute, and a mouse was within them. (You found them in a forest.)}. I hypnotized a \index{snake}snake\footnote{My snake was black, and a mouse was in them. (This mouse did not seem warm-blooded.) They were in a desk.}. I stepped on them. 

 I sneezed. 

 I saw or hear others sneezed. I found myself in a \index{snow}snow\footnote{Our snow looked cold, and it was mild but not soft. A snowstorm was in it, and we saw it in a countryside.} \index{storm}storm\footnote{Your storm was mild and modest. (It was a thunderstorm but not an electric storm, and it was in a sea.) Wide.}. I saw dirty \index{snow}snow\footnote{I found a track within. I saw it in a grind. (It was beautiful.) It was cloudy but not nebulose.}. I saw the \index{sun}sun\footnote{Your sun was in a universe. They were a sunset but not a sundown. Beautiful. I found a lizard in them. You told me they were large.} shining through \index{landscape}landscapes\footnote{You found a rosebush within. (This rosebush was in a landscape.)} of \index{snow}snow\footnote{We saw the snow in a mountain. (It appeared cold.) A track was not in it.}. 

 I snowballed. I was making \index{soap}soap\footnote{The soap was pale blue but not light-blue, and it was in a bathroom. You told me it was nonslippery. (We found a soap dish within.) A shampoo.}. I had sold \index{anything}anything\footnote{Infinite. A marker. (The marker was found in a school.) It was black and sinister.}. I saw \index{soldier}soldiers\footnote{Creative. You said they were a troop. A bugle was in our troop.} marching. I was a worthy \index{soldier}soldier\footnote{A mortar was within my soldier, and you said that our mortar was dangerous. We found it in an armory. Opaque.}. I dressed a sore. I imagined another's \index{soul}soul\footnote{The soul was in a human, and the human seemed alive. It was not a police officer. Evil. We found a pistol there.} was in me. I saw them distressed or wounded. I killed one. I was spinning. I saw \index{spirit}spirits\footnote{My spirit was a ghost but not a spectre. (It was not clear, and you found it in a graveyard.) You found a human within. Our human seemed intelligent.}. I heard \index{spirit}spirits\footnote{This spirit was wet and loaded, and it was a ghost but not a ghostwriter. I found the ghost in a cellar. (Our cellar looked dark and light.)} knocking on \index{door}doors\footnote{Your door did not appear underground. (Rectangular.) You said it was not an entrance, and a couch was not in it. Our couch was in an at home.} or \index{wall}walls\footnote{This wall seemed vertical and unerect. A membrane. (It was in a house.) I found a tack in it.}. I heard \index{music}music\footnote{My music was in a carnival, and I found a roller coaster within. Scary.} supposedly coming from \index{spirit}spirits\footnote{The spirit was fluid but not runny, and you said it was a doppelganger.}. I lived in splendor. I saw others thus living. I used one in erasing. 

 I saw. I stole one. I saw \index{spring}spring\footnote{The spring was seen in a classroom. An apple tree was in it.} appearing unnaturally. 

 I was looking through a \index{spy-glass}spy-glass. I saw a dog chasing one. I saw a \index{stable}stable\footnote{A leather was within the stable. Up. You told me it was dirty.} burning denoted successful changes. I saw a \index{stain}stain\footnote{We found my stain in a carpet, and a stain was within the carpet. Toxic.} on the \index{garment}garments\footnote{Your garment was not a coat. You found a button in my coat. Skinny. It was seen in a drawer. Our drawer was large and orotund.} of others. I fell down \index{stair}stairs\footnote{Your stair was seen in a garage. A staircase. (You found a stairwell there, and you told me it was dark.)}. I walked down. I sat on \index{stair}stair\footnote{Our stair was in a garage, and you found a stairwell within.} \index{step}steps\footnote{You told me your step was sexy. It was seen in a kitchen, and you found a steppe in it. It was a jug but not a jugful.}. I saw others acting as standard-bearers. I looked upon clear. I saw \index{star}stars\footnote{The star appeared small and big. A red giant. Our red giant was not beautiful.} appearing and vanishing mysteriously. I saw them rolling around on the earth. I saw others in this \index{condition}condition\footnote{Extreme. You found it in a plan.}. I saw \index{statue}statues\footnote{We found a pigeon there. Your pigeon was in a roof.}. 

 I was accused of stealing. I saw a \index{steeple}steeple\footnote{The steeple was both high and low.} rising from a church. I decended them. 

 I fell from them. I was stung. I saw stones. 

 I threw a \index{stone}stone\footnote{Our stone was heavy. An agate. I saw it in a pond, and a pebble was within my pond.}. I sold \index{good}goods\footnote{You told me my good was important. You said it was not a penguin, and you found a good health in it.} in one. I saw straw \index{pile}piles\footnote{A duffel bag was within your pile, and you saw it in a forest.} burning. I saw \index{street-poster}street-posters at \index{work}work\footnote{The work seemed dynamic and stative, and it was a meet. It was found in a school, and we found an assignment within.}. I ate \index{sugar}sugar\footnote{You saw our sugar in a sugar bowl. I found a sugar in my sugar bowl.}. I saw the \index{sun}sun\footnote{A lizard was in this sun. Big. They were in a universe. This universe was infinite.} at noontide. I saw the \index{sunset}sunset\footnote{My sunset seemed beautiful, and you told me it was beautiful. It was discovered in a university.}. I saw surgical instruments. 

 I saw a wounded or dead one. I was \index{swearing}swearing before my \index{family}family\footnote{You saw your family in a supermarket. They were evil. A love was in them. They were associative and associatory. (They were not a husband.)}. 

 I thought the \index{floor}floors\footnote{The floor appeared dirty and clean. It was a roof. Man-made. It was in a mouth, and a solar panel was in it.} needed \index{sweeping}sweeping. I was trying to get rid of a sweet \index{taste}taste\footnote{This taste appeared sweet. (You said it was a mint, and you saw my mint in a refrigerator.)}. 

 I got rid of a sweet taste. I saw myself swollen. I saw others swollen. I swam under \index{water}water\footnote{Good. An eel was in it. You told me it was unmelted, and it was found in a pool. It was a steam.}. 

 I wore a \index{sword}sword\footnote{You said our sword was not a foil. It was both harmful and harmless. You told me it was unretentive, and it was seen in a scabbard.}. I had my sword taken from me. I saw others bearing \index{sword}swords\footnote{My sword was seen in a museum. It was an epee. Your epee did not appear sharp.}. I saw empty tables. I ate from a table without a \index{cloth}cloth\footnote{This cloth was seen in a bedroom, and it was smooth and suave. It was a linen but not a linen paper. I found a sheet in your linen.}. I saw a \index{table}table\footnote{A silverware was in the table, and my silverware was found in a table.} walking or moving in some mysterious \index{way}way\footnote{You said my way was a sweat. It did not seem unpredictable, and it was discovered in a mountain. I found a climber there.}. 

 I saw a broken \index{table}table\footnote{Your table was small. It was hazardous and wild. It was in a house. It was not a desk, and I found a plate in it.}. I saw or heard \index{table-rapping}table-rapping or \index{writing}writing. I took my \index{measure}measure. I talked. 

 I was a \index{tanner}tanner. I saw a \index{tapeworm}tapeworm\footnote{The tapeworm was bad and unsound.}. 

 I saw \index{tar}tar\footnote{The tar was in a tar paper. A target. (You found a shoulder bag in our target.)}. I saw tattooes on others. 

 I was a \index{tattooist}tattooist. 

 I saw my friends drinking \index{tea}tea\footnote{You found a teardrop in this tea.}. I was in \index{tear}tears\footnote{You found your tear in a build, and I found a door in my build. Underground. It was an entrance but not an entryway, and it looked hollow and solid.}. I was having a \index{set}set\footnote{A sett was within my set, and we saw this sett in a craven.} of \index{tooth}teeth\footnote{A nerve was not in this tooth. The nerve was seen in a spinal cord.} made. I lost my \index{tooth}teeth\footnote{My tooth was discovered in a mouth. We found a bathroom there, and you told me it was oval.}. I had my \index{tooth}teeth\footnote{You saw my tooth in a city. A build was within my city.} knocked out. 

 I examined my \index{tooth}teeth\footnote{Oval. It was seen in a mouth. You found a toothbrush within.}. I spit out \index{tooth}teeth\footnote{A nerve was within your tooth, and our nerve was in an animal. (An elephant.)}. I pulled one of my \index{tooth}teeth\footnote{Your tooth seemed oval, and you saw it in a plate. My plate was a dish but not a smasher. A dishwasher was in our dish.} and lose it. 

 I sent a \index{telegram}telegram\footnote{We found a stop there, and it was readable but not decipherable.} was a \index{sign}sign\footnote{You saw my sign in a demonstration. (You found an advertisement there, and my advertisement was a plug.)} that I will be estranged from some \index{one}one\footnote{A lamp was not in the one. (It did not seem many, and it was found in an airplane.) Your airplane was noisy, and you said it was a biplane.} holding a \index{place}place\footnote{An anemone was not in the place. It was in a dark. Reflective. (You said it was a cave.)} near me. I willed be estranged from some \index{one}one\footnote{This one was found in a house, and a kitchenette was within it. You said that it was not infinite, and you said it was not a football field. (It seemed two.)} holding a \index{place}place\footnote{Our place was in a line. You told me our line was one-dimensional, and I found a washcloth within.} near me. I was the \index{operator}operator\footnote{My operator was found in a subway. Underground. You found a subway token within.} sending these \index{message}messages\footnote{I found a tack there, and our tack was in a bulletin board. You told me it was dull.}. I looked at \index{planet}planets\footnote{Your planet was seen in an orbit, and they appeared round. You told me they were large. A sea was within them.} and starred through one. I saw others engaged in this dream. I was in a tent. I felt \index{terror}terror\footnote{I saw this terror in a terrorist, and this terrorist appeared monogamous. They seemed dangerous and safe, and I found a bomb in them.} at any object or happening. I heard a \index{minister}minister\footnote{You said my minister was not a minister of religion.} reading my \index{text}text\footnote{You found a textile in this text. You said that my textile was not limp, and it was seen in a kitchen. (A kitchen utensil.)}. 

 I thatched a \index{roof}roof\footnote{A fiddler was not in your roof, and your fiddler was fragile but not slight. (They were discovered in a roof.)} with any quickly. I saw the \index{ground}ground\footnote{Someone was not in your ground. It did not seem nocturnal, and you said it was not a groundcover.} thawing after a long \index{freeze}freeze\footnote{You told me your freeze was solid, and a meat was within it. (The meat did not seem wrong.) It was a hamburger but not a burger, and our hamburger was found in a hockey game.}. I attended a \index{vaudeville}vaudeville\footnote{Our vaudeville was in a vaudeville theatre. Big.} \index{theater}theater\footnote{You said that the theater was solid, and a movie was in it. You told me it was cheap, and it was seen in a movie.}. I looked at a \index{thermometer}thermometer\footnote{My thermometer was in a drawer. I found a pencil in this drawer, and the pencil seemed cylindrical. It was a pencil eraser but not a rubber eraser.}. I saw a broken one. I pursued or capture a thief. I saw wounded \index{thigh}thighs\footnote{Our thigh appeared fragile.}. I was thirsty. I saw broken \index{thread}threads\footnote{Our thread was in a cabinet.}. I saw a well-developed and graceful \index{throat}throat. I felt that my \index{throat}throat was sore. I saw others on a \index{throne}throne. I was tickled. I saw large \index{tick}ticks\footnote{Our tick was small and small-scale, and it was seen in a ticket office. We found a ticket booth in it. It was brown, and you said it was not a ticket.} on \index{stock}stock\footnote{My stock was in a suitcase, and a tie was within the suitcase. (The tie appeared pointless.)}. I saw them in \index{cage}cages\footnote{We found your cage in a zoo, and it was fierce. You found a marmoset in it.}. I saw \index{money}money\footnote{My money was a time but not a fourth dimension, and our time was discovered in a timer.} and \index{valuable}valuables\footnote{You said my valuable was a hand. (It was in a mailbox.)} in a till. I put my \index{hand}hands\footnote{You found your hand in a house, and a cigarette was within them. (Expensive.)} on them. 

 I used it. I smoked \index{tobacco}tobacco\footnote{Your tobacco looked addictive and nonaddictive. A cigarette was within it. (It was not organic.)}. I heard a tocsin sounded. I saw \index{tomb}tombs\footnote{You found a bone there. My bone seemed stiff. You found it in an animal. A human.}. I saw my own \index{tomb}tomb\footnote{We found a bone in your tomb, and your bone appeared hard. It was in a vertebrate. You said your vertebrate was not a lizard.}. I saw my own \index{tongue}tongue\footnote{My tongue was in a tongue depressor, and you told me it was rare.}. I saw the \index{tongue}tongue\footnote{You told me my tongue was rare, and it was in a mouth.} of another. I saw others toothless. 

 I used one. I saw a \index{top}top\footnote{You saw your top in a beach, and a peak was within it.}. 

 I was in a \index{tornado}tornado\footnote{A projectile was within the tornado, and it was a twister but not a cruller. The twister seemed dangerous and safe, and it appeared destructive.}. I was looking upon a rushing \index{torrent}torrent. I saw \index{toy}toys\footnote{Your toy seemed durable. A toy box was within it. We found it in a floor. (A roof.)}. I gave away \index{toy}toys\footnote{A yo-yo. Durable. Dangerous. It was found in a drawer.}. 

 I was implicated in a \index{tragedy}tragedy\footnote{Our tragedy was in a melodrama. It was powerful and brawny.}. I saw a \index{train}train\footnote{Our train appeared noisy, and we found a bridge within. It was seen in a train station.} of \index{car}cars\footnote{I found a driveway there, and your driveway was found in a city.} moving. I saw \index{freight}freight\footnote{I saw your freight in a sea. Your sea appeared wide and narrow.} \index{train}trains\footnote{Our train was seen in a train station, and a human was within it. A woman. You told me your woman was pretty.}. 

 I saw a \index{traitor}traitor\footnote{A warlock.}. I set a \index{trap}trap\footnote{A weasel was not in this trap.}. I was caught in a \index{trap}trap\footnote{You found a mouse there.}. 

 I caught \index{game}game\footnote{My game was educational. (It was painful and awful.) It was a horseshoe but not a shoe. This horseshoe was in a beach. You found a beach towel within.} in a \index{trap}trap\footnote{A drum was in the trap.}. I saw an empty \index{trap}trap\footnote{I found a weasel in my trap.}. I traveled. 

 I saw \index{tray}trays\footnote{My tray was discovered in a hospital. The hospital seemed dirty and clean.}. I saw \index{trench}trenches\footnote{A soldier was within your trench.}. 

 I saw \index{tripe}tripe\footnote{Your tripe was cute but not precious.}. I saw \index{triplet}triplets. I heard \index{newly-born}newly-born \index{triplet}triplets crying. I had \index{triplet}triplets. I put them on wrong \index{side}side\footnote{A midget was not in your side, and it was seen in a carnival. (Square.)} out. I caught them with a \index{seine}seine\footnote{Your seine appeared shallow.}. I blew a \index{trumpet}trumpet\footnote{My trumpet was in a brass band.}. I saw the \index{content}contents\footnote{My content was in a box, and the box was opaque. It was a coffin. Opaque.} of a \index{trunk}trunk\footnote{I found my trunk in a garage. I found a spare tire in it.} thrown about in disorder. I checked my \index{trunk}trunk\footnote{Your trunk was a jeep but not a landrover, and it was seen in a bedroom. (A keepsake was in it.)}. I saw a tub full of \index{water}water\footnote{The water was a steam. (You found a coral reef in it.) You said that this coral reef was yellow.}. 

 I tumbled off of any \index{thing}thing\footnote{This thing was fuzzy, and it was seen in a backpack. It was heavy but not grueling, and you found an attribute within.}. I saw others tumbliing. 

 I saw them dressed for the \index{market}market\footnote{You found a fruit in my market. It was in a rural area.}. I ate turkey. I drank \index{turtle}turtle\footnote{Your turtle was strange but not unknown. We saw it in a zoo. (It appeared slow and fast.)} \index{soup}soup\footnote{You said our soup was not a miso.}. I was affected with this malady. I was ugly. I had ulcers. I saw others carrying them. I carried a leaky one. I saw my \index{uncle}uncle\footnote{The uncle was friendly, and they were found in a family. They appeared fertile.} dead. I had a \index{misunderstanding}misunderstanding with my \index{uncle}uncle\footnote{Our uncle was friendly. They were not fertile. We saw them in a family, and the family was not a wife.}. 

 I was in an \index{underground}underground\footnote{Dark. It was an underground press but not a samizdat.} \index{habitation}habitation\footnote{My habitation was big.}. I rode on an underground railway. I was undressing. I was unfortunate. 

 I saw a \index{uniform}uniform\footnote{You told me your uniform was undetectable. A uniformity.}. I saw \index{person}people\footnote{My person was found in a theater. You said it was not an actor, and a soul was within it.} arrayed in strange \index{uniform}uniforms\footnote{A uniformity. It seemed undetectable.}. I met unknown persons. I was urinating. I found myself a \index{usurer}usurer. I was vaccinated. I was vaccinated on my \index{leg}leg\footnote{A muscle was not in the leg, and you said that my muscle was not dead. We found them in an animal. (You said my animal was an insect.)}. I was a vagrant. I was sending \index{valentine}valentines. I rode in a \index{vehicle}vehicle\footnote{This vehicle was in a garage. We found a bicycle there.}. I bought one. 

 I wore a \index{veil}veil\footnote{Your veil was creative.}. I saw others wearing \index{veil}veils\footnote{My veil was not weird.}. I lost my veil. I wore a bridal \index{veil}veil\footnote{Your veil was weird and uncanny.}. I threw a \index{veil}veil\footnote{My veil did not appear strange.} aside. I saw them swollen. I was veneering. I thought myself one. I saw an old veranda. I thought some \index{person}person\footnote{Your person was in a conference, and we found a lecture there.} was vexed with me. I was the \index{victim}victim of any \index{scheme}scheme\footnote{You told me my scheme was good. It was in a mind, and a society was in the mind.}. I victimized others. I used vinegar on \index{vegetable}vegetables\footnote{My vegetable was in a grocery store. (It appeared edible, and you said it was not a pea.) It was good and just. A row was within it.}. I visited a \index{vineyard}vineyard\footnote{I found a lizard in my vineyard. You said that it was not sparse.} which was not well-kept and filled with bad odors. I did some other \index{person}persons\footnote{Your person was discovered in a build, and a computer was not in the build. It appeared ugly and beautiful. A library. (The library did not seem large.)} violence. 

 I gathered them. I saw. I played on one in my \index{dream}dreams\footnote{Your dream was discovered in a rainbow, and you told me it was asleep. Someone was in it, and this someone was dangerous and life-threatening. It was a criminal.}. I played was unsuccessful. 

 I was warned in a \index{vision}vision\footnote{You said our vision was not a visionary.}. I saw \index{vision}visions\footnote{You said your vision was not a visionary.} of any \index{order}order\footnote{An order book was not in this order, and we saw it in a mall.}. I threw it on \index{person}people\footnote{Weird. I found a soul within. We found our soul in a human. You said your human was not a woman.}. I vomited. I saw others vomiting. I vomited. I lost one. I won one. I put up a wager. I was not able to put up a \index{wager}wager. I payed out \index{wage}wages\footnote{Your wage was in a work. Hard.}. 

 I had my \index{wage}wages\footnote{You saw your wage in an office.} reduced. I drove one down a hill. I drove one up \index{hill}hill\footnote{We found this hill in an outside, and it seemed steep. A lizard was within it, and it was not a sand dune.}. I drove a heavily loaded \index{wagon}wagon\footnote{My wagon was seen in a garage, and it was not a coach. I found a clipboard there.}. 

 I saw a covered \index{wagon}wagon\footnote{You saw our wagon in a wagon train, and it was a coach but not a bus. A clipboard was in the coach. They did not appear wrong.}. I heard a \index{wail}wail\footnote{You found someone within, and your someone was both dangerous and safe.}. I walked in pleasant places. I walked in the \index{night}night\footnote{You said my night was an earwig. Our earwig was not small. Slim.} brought \index{misadventure}misadventure. I walked on \index{top}top\footnote{Your top was found in a build. You found someone within.} of a \index{wall}wall\footnote{Your wall appeared black and white. It was found in a house. A membrane.}. I cracked a decayed \index{walnut}walnut\footnote{You said your walnut was not a walnut tree.}. I found myself contented in a \index{state}state\footnote{Your state was discovered in a state highway. It was false, and a county was within it.} of \index{want}want\footnote{Your want was found in a newspaper. You said that this newspaper was lightweight. A comic was within it.}. I relieved wanted. I imagined me had a scant \index{wardrobe}wardrobe\footnote{This wardrobe was discovered in a home. A handbag was in it, and my handbag was both tough and tender.}. I had a scant wardrobe. I saw a warrant served on some \index{one}one\footnote{A football field, and it was in an airplane. A human was within this airplane. It appeared man-made, and it seemed heavy and light.} else. I saw them leaving my hands. 

 I saw them on others. 

 I saw a washboard. I was washing myself. I thought I was a water-carrier. 

 I was a water-carrier. I lighted wax tapers. I lost my \index{way}way\footnote{A run. It seemed unpredictable, and you found a rosebush in it. (We found it in a mountain.)}. I saw others wealthy. I saw a weasel \index{bent}bent\footnote{The bent was tall and marvellous.} on a marauding \index{expedition}expedition. 

 I destroyed them. I saw a \index{weather}weather\footnote{My weather was discovered in a roof. Our roof was dirty and dingy, and it was red. (A shingle was not in it.)} witch. I was weaving. I was wedded. I was dissatisfied with \index{wedlock}wedlock. 

 I was weeding. I was employed in a well. I saw an empty well. I saw one with a \index{pump}pump\footnote{Your pump was seen in a jar. The jar appeared large. You found a cookie within.} in it. 

 I was wet. I was soaking wet. I saw a whale approaching a \index{ship}ship\footnote{A cargo was within the ship, and it was in a shipwreck. It seemed safe, and it was not a junk. Safe.}. I saw a whale overturn a \index{ship}ship\footnote{This ship was discovered in a shipwreck.}. I saw or work with \index{whalebone}whalebone. I saw large \index{field}fields\footnote{We found an apple tree in the field. We saw our apple tree in a countryside.} of growing wheat. I saw large clear \index{grain}grains\footnote{A mouse was in our grain. It seemed edible and inedible, and it was in a beach.} of \index{wheat}wheat\footnote{I saw my wheat in a bread, and a wheat field was in it. (It was both small and big.)} running through the \index{thresher}thresher\footnote{You said that my thresher was human.}. I saw its \index{content}contents\footnote{The content was seen in a box, and you told me it was unhappy. You said that it was not white.} getting wet. I saw idle or broken wheels. 

 I was in the \index{path}path\footnote{The path was a road. You told me it was predictable, and it was both ugly and beautiful.} of a \index{whirlwind}whirlwind\footnote{You said that my whirlwind was not fragile.}. 

 I drank it alone. I destroyed \index{whisky}whisky\footnote{Your whisky was in a jar.}. I heard a whisper coming to me as \index{advice}advice or warning. I was whistling. 

 I was whitewashing. I lost a \index{wig}wig\footnote{Our wig was not a dance, and you found a dance floor in the dance. Your dance floor was seen in a city.}. I saw others doing so. I saw a wild \index{man}man\footnote{Our man was in a love. You told me they were weak. (They appeared emotional.) They were not a boy. I found a penis within.}. I thought a will was against them. I destroyed one. I walked briskly against a brisk \index{wind}wind\footnote{I found a pot plant within. My pot plant was discovered in a table.}. I saw one broken or idle. I had \index{wing}wings\footnote{You saw our wing in an aircraft, and you found a flap in them.}. I saw a \index{wire}wire\footnote{Your wire was discovered in a wall, and a telephone box was within it. It was contagious.} \index{fence}fence\footnote{My fence was both smart and stupid, and I found a garden within.}. I killed one. I argued with one. I saw a dark-haired woman with blue \index{eye}eyes\footnote{An eye doctor. It was in an eye socket. We found an eye socket in it.} and a \index{pug}pug\footnote{Stupid.} nose. 

 I saw \index{wood}woods\footnote{The wood was opaque, and it did not appear distasteful. You saw it in a boat, and a marmoset was within it. It was a door.} on fire. 

 I saw others at \index{work}work\footnote{An office was within your work. (It was found in a desk.) You told me it was dynamic. It was not a meet.}. I looked for work. 

 I was wounded. 

 I saw others wounded. I was writing. I read strange \index{writing}writing. I tried to read strange \index{writing}writing. I felt that I was \index{yearning}yearning for the \index{presence}presence\footnote{Fragile. It was a cholelithiasis.} of \index{anyone}anyone\footnote{Real.}. I was \index{yearning}yearning for the presence of \index{anyone}anyone\footnote{Your anyone seemed funny.}. I thought my \index{lover}lover\footnote{The lover was in a backyard, and this backyard was both expensive and cheap. (A vegetable garden was within it.)} was yearning for me. I received poor \index{yield}yield\footnote{This yield was discovered in a street corner. You found a lamppost in my street corner.} for my \index{labor}labors\footnote{Our labor was in a laboratory. The laboratory was hazardous. It was yellow but not chicken. An instrument was within it.}. I saw a \index{yoke}yoke\footnote{Our yoke was discovered in a plane.}. I was young again. I saw the young in \index{school}school\footnote{My school was discovered in a neighborhood. Solid. (A human was in it, and it was yellow.) A kindergarten.}. 

 I saw one wild in my native \index{country}country\footnote{The country was found in a war. My war seemed expensive and cheap. (A tank was within it.)}. I studied the \index{zodiac}zodiac. I approached it or it approached me. I drew a \index{map}map\footnote{I found a place in this map, and it was in a library. This library looked dark and light.} of it.

\chapter{}

I was abandoned. 

 I saw this pious \index{man}man\footnote{A boy. Strong. They were seen in a bed. I found a penis in them. They were lazy.} in devotional \index{exercise}exercises\footnote{Your exercise was not a bike. We found someone within, and you saw it in an exercise bike.}. I could n't find my \index{abode}abode. I grieved over the absence of any one. I was possessed with an abundance. I was playing an \index{accordion}accordion\footnote{I found your accordion in an orchestra. (This orchestra was an oboe but not a hautbois.)}. I accused any one of a mean \index{action}action\footnote{The action was a punch but not a biff. You told me it was one, and it was discovered in a theater. (You said that our theater was not big, and I found a seat within.)}. I seemed to be disputing. 

 I was disputing. I thought that I had an extensive \index{acquaintance}acquaintance. I saw an \index{adder}adder. I bid cheerful \index{adieus}adieus to \index{person}people\footnote{Our person was not distinct. (It appeared human, and a bone was in it.) It was an astronaut but not a spaceman, and it was in a conference.}. I was an \index{object}object\footnote{Solid. (It was a stapler but not a stapling machine.) An object program was not in it. Heavy. It was in a drawer.} of \index{admiration}admiration\footnote{Your admiration was a vanity.}. I saw others advancing. 

 I was victimized by an \index{adventurer}adventurer. I received \index{advice}advice. I looked at \index{photograph}photographs\footnote{You found a backdrop within. You said it was a photo, and you found it in a newspaper. It appeared blurry. It seemed two-dimensional.} in an \index{album}album\footnote{You found a photograph within.}. I saw a \index{priest}priest\footnote{A priesthood was within this priest.} at the \index{altar}altar\footnote{Our altar was sacred. It was seen in a ceremony. (My ceremony was a ritual.)}. 

 I saw an \index{amateur}amateur\footnote{A bowl.} \index{actor}actor\footnote{This actor appeared fragile, and they were in a theater.} on the \index{stage}stage\footnote{I found a backdrop there. (A platform.) Red. It was seen in a theatre.}. I lied in \index{ambush}ambush to \index{revenge}revenge\footnote{Illegal.} myself on others. I saw others amorous. I saw myself or others appareled in white. I saw yellow \index{apparel}apparel. 

 I saw an \index{archbishop}archbishop\footnote{My archbishop did not seem religious.}. I saw respectable-looking \index{stranger}strangers\footnote{I found your stranger in a subway. They did not seem strange.} arrested. I was going to be married in August. I was married in August. 

 I saw an \index{author}author\footnote{My author was fragile but not thin. They were in a bookstore. A novel was within the bookstore.} over my work. I was a \index{bachelor}bachelor\footnote{A fungus was not in the bachelor.}. I saw or carrying a basket. I habitueed's of this beverage. 

 I saw an empty \index{bird}bird\footnote{I found a string in the bird. They were a hawk but not a mortarboard, and they were both pure and unsaturated. We found them in a sky, and they looked cool and warm.}'s \index{nest}nest\footnote{A feather was within the nest, and you said it was a nestl.}. I saw a \index{blood}blood\footnote{The blood appeared fluid. (We found a blood bank in them.) Liquid. They were in a capillary.} \index{stone}stone\footnote{This stone was discovered in a stream, and a canoe was within my stream. Shallow. It was not a brook.}. I visited a \index{book}book\footnote{This book seemed expensive and cheap. It was a text. It was both solid and liquid. (A blowfish was within it.) It was in a desk.} store. 

 I ate them. 

 I was a \index{bride}bride\footnote{Beautiful. They were female. (They were in a bridesmaid.)}. I saw bridle \index{bit}bits\footnote{This bit was a life but not a liveliness, and our life seemed finite and infinite. They were in a universe, and a mean was not in them.}. I carried a heavy \index{burden}burden. I was drinking \index{buttermilk}buttermilk\footnote{My buttermilk was both bad and unregretful.} made into \index{oyster}oyster\footnote{You found a pearl in my oyster. It was in an ocean.} \index{soup}soup\footnote{You found this soup in a cupboard, and you said it was a miso. It was unhealthy but not insalubrious, and we found a fungus there.}. I heard a \index{buzzard}buzzard talking. I saw \index{buzzard}buzzards. I was in a \index{camp}camp\footnote{We found a campus in my camp.}. I saw \index{car}cars\footnote{We found a mirror there. It seemed dangerous and safe. (It was a bus but not a heap.) Your bus was useful but not utilitarian, and it was seen in a bus station.}. I saw a \index{caterpillar}caterpillar\footnote{Your caterpillar seemed useful. A cutworm.}. I ate it. 

 I was in a beautiful and well-kept \index{cemetery}cemetery\footnote{Our cemetery was quiet, and we found a graveyard in it. Our graveyard was in a church property.}. I saw the chairman of any public \index{body}body\footnote{You told me our body was beautiful, and I found a skin in it. The skin was found in a good health.}. I saw my \index{swetheart}swetheart wearing a \index{chameleon}chameleon\footnote{You said that the chameleon was not small. (They were blue.)} chained to me. I fell or saw others fell from one. I saw them looking sorrowful or reproachful. I saw \index{chimney}chimneys\footnote{You found your chimney in a roof.}. I entered one wrapt in \index{gloom}gloom\footnote{My gloom did not seem enjoyable.}. 

 I climbed a \index{ladder}ladder\footnote{I saw the ladder in a garage. (You said that it was important, and you said it was not a stepladder.)} to the last rung. I saw a new \index{coat}coat\footnote{You told me this coat was skinny. I found a flask in it, and it was found in a wardrobe.}. I drank \index{coffee}coffee\footnote{This coffee was not a latte. Bitter. It was wide and all-inclusive, and I found a coffee shop there. We saw the coffee shop in a downtown.}. I saw \index{coke}coke\footnote{You told me your coke was good. It was both wide and narrow. It was seen in a movie.} ovens burning. I completed a \index{task}task\footnote{This task was a project.} or \index{piece}piece\footnote{I found a mouse in this piece. You told me it was white, and it was discovered in a puzzle.} of \index{work}work\footnote{A public servant, and we saw our public servant in a desk. They were hard but not intemperate.}. I was in company with a \index{concubine}concubine\footnote{This concubine was human.}. I had a quiet conscience. 

 I cooked a \index{meal}meal\footnote{This meal was not a fast food, and it did not seem small. It was found in a plate, and you told me it was edible.}. I saw a cooking \index{stove}stove\footnote{We found your stove in a kitchen, and an oven was not in it.}. I counted \index{money}money\footnote{This money was in a safe, and I found a terrorist within. Dangerous. Mortal.}. I assailed me in my \index{affair}affairs\footnote{This affair was in a work.} of the \index{heart}heart\footnote{I found an artery there. We found it in a cadaver.}. I saw \index{body}bodies\footnote{A mummy. (The mummy did not seem popular.)} cremated. I heard a \index{cry}cry\footnote{I found this cry in a funeral, and you found someone within. Guilty.} of \index{surprise}surprise\footnote{My surprise seemed unpleasant and pleasant, and we found it in a box. A shoe was within your box. My shoe was a sneaker but not a fink.}. I stepped on a \index{crocodile}crocodile\footnote{You told me your crocodile was herbivorous. You said that it was slimy.}'s back. I saw a \index{crowd}crowd\footnote{You found my crowd in a fistfight. A crowd was in our fistfight, and your crowd was powerful and herculean.} in the \index{street}street\footnote{Your street was in a street corner. It was a boulevard but not an avenue. Our boulevard was both dark and light.}. I saw others crying. I stepped together on a \index{curb}curb\footnote{My curb was found in a street, and a curbside was within it.}. I was in \index{difficulty}difficulties. 

 I dug a \index{hole}hole\footnote{We saw your hole in a wall. It was a nostril but not an anterior naris. Dark.} and find any glittering \index{substance}substance\footnote{The substance was discovered in a container. A pitcher. You found a soup within, and this soup was unhealthy and insalubrious.}. I handled \index{dish}dishes\footnote{You said my dish was not a plate. They were found in a kitchen. Round. They were green and greenish. (A dishwasher was within them.)}. I was a long \index{way}way\footnote{The way was unpredictable and irregular. (We saw it in a mountain, and it was not a run.) Someone was within this run. My someone looked guilty and innocent.} from my \index{residence}residence\footnote{My residence was white but not bloodless, and it was in a home.}. I was divorced. I felt much \index{fright}fright\footnote{A tornado. (It was weird and unearthly.)} upon seeing a large \index{mastiff}mastiff. I saw dogs and cats seemingly on friendly terms. 

 I heard a \index{duet}duet played. I was in a dungeon. 

 I saw \index{earring}earrings\footnote{Our earring was in an earlobe. It was not shiny.}. I saw an \index{eel}eel\footnote{You said that our eel was not fragile.} in clear \index{water}water\footnote{You told me my water was buoyant, and you said it was not a rain. We found a rainforest there, and it was in a rainbow. Cloudy.}. I saw live electrical \index{wire}wire\footnote{We found a mouse in our wire, and this mouse was distinct. We found them in a desk, and you told me they were destructive.}. I sat at the \index{table}table\footnote{A floor was not in this table. (You told me it was stable.) Hazardous. A desk. We saw our desk in a build.} with an \index{epicure}epicure. I went on \index{errand}errands. 

 I saw the air filled with \index{smoke}smoke\footnote{Our smoke was addictive, and it was seen in an air. (Flammable.) Someone was within it.} and \index{de'bris}de'bris. I heard. I burnt me at the \index{stake}stake\footnote{Someone was not in your stake.}. I saw a \index{fan}fan\footnote{My fan was discovered in a stadium, and I found a fantasy world in them. (Strong.) They looked off and on.}. I saw \index{field}fields\footnote{This field appeared expensive and cheap, and it was not breathtaking. It was a prairie. You found a ranch there.} freshly harrowed and ready for \index{planting}planting. I heard a fife. I saw \index{file}files\footnote{This file was not a window, and it was found in a file cabinet. We found someone within.}. I saw well-kept \index{nail}nails\footnote{Someone was not in this nail. Our someone was in a desk. Our desk seemed opaque and clear.}. I was fighting \index{fire}fire\footnote{The fire was in a fireplace, and you told me it was safe. A coal was not in it.} and did not get burned. I saw a \index{fireman}fireman\footnote{Someone was within this fireman. They were stupid and stunned. (You told me they were unsexy.)}. I was flying with white wings above green \index{foliage}foliage\footnote{A perennial. It was in a forest.}. I saw a fly-trap. I crossed a clear \index{stream}stream\footnote{Shallow. I found a canoe there, and we saw it in a forest. You said it was a brook, and you said that this brook was not shallow.} of water on a \index{foot-log}foot-log. I saw \index{anything}anything\footnote{The anything was not a toy. (I found a sentence in it, and you told me it was infinite.) It was seen in a box.} \index{ill}ill\footnote{A toll road was within my ill. It looked delightful. (It was an illusion, and it was in an illness.) My illness seemed bad.} formed. I told. I accused some one of defrauding me. I saw a \index{friend}friend\footnote{The friend was in a school, and our school looked yellow. It seemed ugly. You said it was not a kindergarten, and I found a human within.} on the \index{gallows}gallows\footnote{Your gallows was blue and downhearted.} of \index{execution}execution. I extinguished \index{gas}gas\footnote{Someone was within my gas. You told me it was flammable, and it was in a gas station.}. I saw a female \index{ghost}ghost\footnote{This ghost was discovered in a cellar. Our cellar was red and cerise.} on my \index{right}right\footnote{The right was an atheist. Your atheist was seen in an office. You found a human within, and they were irreligious.} in the \index{sky}sky\footnote{A cloud was within my sky. The cloud was in a rainbow. It was fluffy.} and a male on my left. I received gifts from any one. I broke a \index{mirror}mirror\footnote{The mirror was a mirror image but not a reflection. You found a monkey in it. You told me it was nonreflective. It was in a wall.}. I pulled my glove off. I was a perfect dream. I saw grasshoppers on green \index{vegetable}vegetables\footnote{Your vegetable appeared green, and I found it in a grocery store. It seemed organic. You found a vegetable soup in it.}. I had a \index{guitar}guitar\footnote{This guitar was an acoustic guitar, and this acoustic guitar was in a rock band.}. I saw beautiful \index{hand}hands\footnote{The hand looked black and white, and a bone was in them. They were in a pocket.}. I saw my hands enlarged. I saw \index{torn}torn\footnote{A tornado was in our torn. Our tornado seemed dangerous, and it was a twister. You said that my twister was dangerous.} ones. I climbed \index{hill}hills\footnote{A sand dune. Tall. (A lizard was within it, and the lizard was discovered in a jungle.)} was good if the \index{top}top\footnote{I found someone within, and you saw it in a suitcase. This suitcase did not seem large.} was reached. I saw \index{fat}fat\footnote{Harmful. It was not a motorcycle, and it appeared male. We saw it in a fatigue.}. I was refused the \index{right}right\footnote{You said my right was not an atheist. A table was within it. It was found in a corner. My corner was quaint.} of communion and feel worthy. I saw \index{honey}honey\footnote{You told me this honey was salty. They were edible. (They were in a beehive, and you found a queen there.)}. I blew a horn. I saw brood \index{mare}mares\footnote{The mare was in a field. A wheat was in this field. Our wheat was not small.}. I saw a horse with a tender \index{foot}foot\footnote{A football stadium was in this foot. A boot. Round. They were in an office.}. I rode a \index{horse}horse\footnote{You found a barn in the horse. My barn was big and great. (We saw it in a field.) A prairie.} down \index{hill}hill\footnote{I found this hill in a countryside. It was alive, and a lizard was in it. The lizard was a skink. (They were cute but not cunning.)}. I passed in the last \index{day}days\footnote{Our day was in a daydream.}. I saw \index{image}images\footnote{Our image did not seem pretty, and you said they were a paint. They looked blurry.}. I saw \index{ink}ink\footnote{Our ink was discovered in a printer. A sheet of paper was within your printer, and a laser printer. Mechanical. They were man-made but not semisynthetic.} spilled over one's clothing. I attended a party. 

 I was invited to attend a party. I saw huge \index{piece}pieces\footnote{You found a mouse in my piece. (You told me it was black, and it was in a puzzle.)} of \index{ivory}ivory\footnote{Our ivory seemed yellow. You found a gazelle within, and my gazelle was in a herd.} being carried. I inherited \index{jewelry}jewelry\footnote{An earring was in your jewelry. It was heavy. A brooch. It was in a safe. Decorative.}. 

 I gave \index{jewelry}jewelry\footnote{Our jewelry was a necklace. Pretty. (It was in a jewelry store.)} away. I saw a broken \index{kettle}kettle\footnote{Your kettle was a teakettle, and it was in a percussion section. A xylophone was not in our percussion section.}. I handled dark \index{kettle}kettles\footnote{Your kettle was in a kitchen. (We found a sink in the kitchen.)}. I lost the key to any personal \index{ornament}ornament\footnote{My ornament was a bow but not a prow. (This bow seemed yellow, and it was in a cupboard.) We found a bowl in our cupboard.}. I was wounded with a \index{knife}knife\footnote{The knife was heavy. It looked dangerous. A straight razor, and I saw it in a restaurant. A metal was in it.}. I saw men toiling. I was in a laboratory. I was alone on a turbulent and muddy \index{lake}lake\footnote{I found someone within. It was in a mountain, and it seemed blue.}. I saw lighted lamps burning with a clear \index{flame}flame\footnote{Your flame was in a chemistry lab, and it was not a flamethrower. (It appeared hot.) I found a castanets in it, and it seemed scary.}. 

 I saw a \index{lantern}lantern\footnote{We found my lantern in a festival.} going before me in the \index{darkness}darkness\footnote{Our darkness was found in a cellar. You told me it was scary.}. I carried a lantern. I engaged in a lawsuit. I received such a letter. I heard my \index{whistle}whistle\footnote{Our whistle was a whistleblower but not a whistle-blower.}. 

 I found myself in a \index{library}library\footnote{A newspaper was within our library. It was dirty, and it was tall but not grandiloquent. You said it was a school. I saw it in a build.} for other \index{purpose}purpose than \index{study}study\footnote{You said your study was a read, and you found them in a library. My library appeared dark, and you said that it was not white. You found a magazine in it.}. I was apparelled in clean. I saw young \index{lion}lions\footnote{You said the lion was a cub. A cube was within my cub, and you told me your cube was square.}. I heard the \index{roar}roar\footnote{The roar was both peaceful and unpeaceful.} of a \index{lion}lion\footnote{Pure. They were found in a paint. An acrylic. This acrylic appeared plastic.}. 

 I saw piles of \index{lumber}lumber\footnote{A lumberyard was not in your lumber. It was in a garage.} burning. I enjoyed much \index{luxury}luxury\footnote{A carpet. We found someone in it. Guilty.}. I met \index{person}people\footnote{You told me the person was stupid, and it was not an atheist. (It appeared individualist.) We found a bone in it, and it was discovered in a bus stop.} with affable \index{manner}manners. I looked for one. 

 I saw a marriage. I was a \index{bride}bride\footnote{My bride was sensitive and raw. I found them in a bridesmaid, and they seemed perfect and imperfect.}. I struck a \index{match}match\footnote{You said that this match was wooden, and a matchbox was within them.} in the dark. I ate them. 

 I found a \index{memorandum}memorandum. I saw \index{anything}anything\footnote{You told me my anything was infinite, and you found a sentence in it. I found it in a container, and it was not a marker.} metamorphose. I drank \index{milk}milk\footnote{The milk was in a store, and the store was big and fully grown. (It was a shop but not a workshop, and a cash register was within the shop.)}. I tried unsuccessfully to drink \index{milk}milk\footnote{Our milk was white. It was in a market, and we found a cow there. My cow did not seem distinct.}. I saw the \index{morning}morning\footnote{You told me your morning was painless. It was in a front door, and you said it was not a breakfast.} dawn clear. I felt mortified over any deed committed by myself. I saw Moses. I killed \index{mosquito}mosquitoes\footnote{You said that our mosquito was not bad. It was seen in a mosquito bite.}. 

 I protected my \index{interest}interest\footnote{An art was within this interest. You said that it was not annual.}. I saw \index{bird}birds\footnote{A duck. (Your duck was dumb.) It was discovered in a wetland. A duck was within the wetland.}' \index{nest}nests\footnote{This nest was not a nestl, and you found a bee in it.}. I saw them \index{bathing}bathing. 

 I passed afterward. I anointed with oil. I saw one-eyed creatures. I lived in fairy like \index{opulence}opulence. 

 I was caught in \index{bramble}brambles\footnote{I found this bramble in a swale. You said that the swale was carcinogenic.}. I saw a \index{man}man\footnote{Your man appeared emotional. You told me they were weak, and a robot was in them. (They were discovered in a build, and this build was a house but not a household.)} wearing \index{over-all}over-alls. I was in \index{pain}pain\footnote{Our pain was found in a body part, and they were an ache but not an aching.}. I was in Paradise. I saw them while they was living. I saw my parents looking robust and contented. I parted with \index{friend}friends\footnote{You said that my friend was emotional. Important. (They were in a fraternity house, and a party was within the fraternity house.)} and companions. 

 I saw them flying. I heard a passing \index{bell}bell\footnote{A fluff was within the bell, and you saw this fluff in a bed. (It was not a kitten, and you told me my kitten was unplayful.) It was both distinct and indistinct.}. 

 I saw others wearing \index{patch}patches\footnote{You said your patch was a lawn.}. I gathered luscious \index{peach}peaches\footnote{My peach was both juicy and juiceless, and they were seen in a jar. (You found a mayonnaise there.)} from well-filled \index{tree}trees\footnote{An acorn was within this tree. The acorn was found in a grind.}. 

 I gathered them. I ground black \index{pepper}pepper\footnote{The pepper was not a chili, and you told me it was green. It was discovered in a grocery store.}. I was in a \index{perspiration}perspiration. I heard sweet and voluptuous \index{harmony}harmony from a \index{piano}piano\footnote{The piano was a clavichord. (I found our clavichord in a music hall.)}. I found my \index{piano}piano\footnote{You said this piano was a clavichord. It was blue, and it was in a music school. I found a metronome within.} broken and out of \index{tune}tune\footnote{The tune was discovered in a jukebox.}. I saw \index{pigeon}pigeons\footnote{Our pigeon was found in a roof.} and hearing them cooing above their cotes. 

 I polished any \index{article}article\footnote{You saw your article in a newspaper.}. I ate one. I saw ponies. I spoke to the Pope. 

 I built a porch. I saw a \index{porcupine}porcupine\footnote{A quill was not in our porcupine, and the quill did not seem soft. (It was found in an ink.) Red.}. I gazed upon the \index{portrait}portrait\footnote{You saw the portrait in a wall.} of some beautiful \index{person}person\footnote{This person was an actor but not a histrion. I found a heart in it. It was individualist but not individualistic. It was discovered in a hospital, and it was mean.}. I saw a \index{potter}potter\footnote{Blue. They were not blue. We found a pottery within.}'s \index{field}field. I saw dressed \index{poultry}poultry\footnote{Our poultry was in a grocery store, and it appeared chicken.}. 

 I had done. I scaled them. I held on to a \index{railing}railing. I heard the \index{patter}patter\footnote{You saw this patter in a rug.} of \index{rain}rain\footnote{My rain was in a raindrop, and it was hot and blistering. A lemur was within it, and it was a drizzle. (Cold.)} on the \index{roof}roof\footnote{You told me this roof was red. I found a tile there, and my tile was in a floor.}. I used a \index{rake}rake\footnote{The rake was seen in a garage. A bicycle was not in this garage.}. I was \index{rambling}rambling through the country. I gave a \index{reading}reading. 

 I rented a \index{house}house\footnote{You said this house was not a basement, and your basement was not big. It was in a cellar, and a mouse was within my cellar.}. 

 I handled them without \index{harm}harm\footnote{We found a human in your harm. It was strange. (It was in a cabinet.)} to myself. I was resurrected from the dead. 

 I resuscitated another. 

 I felt rheumatism attacking me. I saw a \index{person}person\footnote{You told me this person was strange. It was not individualist. An atheist. A soul was in it, and it was in an apartment.} dressed in mourning sitting on a \index{roof}roof\footnote{The roof was man-made and synthetic. I found it in an airplane. An airliner. A seat was within it, and the seat was high.} \index{corner}corner\footnote{A right angle was in your corner, and the right angle did not appear high. (We found it in a corner, and your corner seemed quaint.)}. I was clothed in \index{rubber}rubber\footnote{A balloon. It seemed malleable. It was in a pencil case.} \index{garment}garments\footnote{We found a silk within, and we found the silk in a tie. (You said that your tie was not pointless.)}. 

 I received \index{merchandise}merchandise\footnote{This merchandise was seen in a box.} \index{sample}samples. I ate sardines. I killed me. I ascended one. I fell from one. I taught a \index{school}school\footnote{You told me the school was safe. You saw it in a city. You found a museum within.}. I was robbed by one. I read Shakspeare's worked. I merelied contemplate getting a shave. I lost my \index{shawl}shawl. I saw a shovel. 

 I was in a \index{shower}shower\footnote{We found our shower in a locker room. (Dark.) A duffel bag was within it.}. I saw any of my \index{family}family\footnote{The family was enjoyable. A person was within them, and they were both associative and nonassociative. A husband. (They were found in a supermarket.)} \index{pale}pale\footnote{I found the pale in a palestra.} and sick. I was sighing over any \index{trouble}trouble\footnote{We found a government there. You told me my government was unimpressive. It was discovered in a democracy.} or sad \index{event}event\footnote{You told me our event was immanent. A miracle. (This miracle was both transient and immanent.) I found it in a universe.}. I gave \index{promise}promise of \index{happiness}happiness\footnote{The happiness was happy. Unpleasant. It was in a rainbow. I found a dream within.}. I was singing while \index{everything}everything\footnote{I found your everything in a universe, and I found a meteor in this universe.} around I gave \index{promise}promise of \index{happiness}happiness\footnote{You told me this happiness was happy, and it did not seem pleasant. It was in a celebration.}. I was \index{sowing}sowing \index{seed}seed\footnote{Your seed appeared heavy. An acorn. The acorn was discovered in a forest, and a branch was in our forest.}. 

 I found myself in a department \index{store}store. I was suffocating. I saw a black \index{swan}swan\footnote{The swan appeared alive. (Mean.)}. I saw \index{dreg}dregs in my \index{tea}tea\footnote{The tea seemed good, and a black tea.}. I was thirsty for \index{tea}tea\footnote{I found my tea in a teacher. (It was fluid and mobile, and a teahouse was within it.)}. I recalled a \index{text}text\footnote{You said that your text was limp. It was in a school. You said this school was a kindergarten. We found a student within.}. I tried to recall a \index{text}text\footnote{This text was a cipher. My cipher was creative but not originative.}. I was at a \index{theater}theater\footnote{Our theater was large and declamatory. Expensive. It was discovered in a movie. A box office was in it.}. I received or buy a new thimble. I heard the terrific \index{peal}peals\footnote{Our peal was cool and coolheaded.} of \index{thunder}thunder. I saw one running away from me. I was tipsy. I carried a \index{torch}torch\footnote{This torch was powerful but not hefty. It was in a wale.}. I found myself. I saw green tress newly felled. I took a Turkish bath. I saw \index{type}type\footnote{You told me my type was loud. They were in a keyboard. (The keyboard was a harpsichord.)}. I saw a broken \index{vase}vase\footnote{My vase did not seem large. It was in a shelf, and it was a vasectomy.}. I was preparing \index{vegetable}vegetables\footnote{You told me this vegetable was edible. Alive. I found it in a grocery store, and a toilet paper was within this grocery store.} for \index{dinner}dinner. I saw my \index{vein}veins\footnote{I found a blood there.}. I had a strange vision. I heard the \index{voice}voice\footnote{My voice was a soprano but not a treble. Loud. A velvet was within them, and you saw them in a choir.} of \index{distress}distress\footnote{I found a lemur within.}. I saw a \index{volcano}volcano\footnote{My volcano appeared hot and cold, and it appeared big. We found a hot spring in it.}. 

 I was making or listening to vowed. I vowed. I drove a wagon near a dangerous \index{embankment}embankment. I was troubled with \index{wart}warts\footnote{The wart appeared dangerous.} on my \index{person}person\footnote{This person was individualist, and it was in a hospital. I found a wind there, and it looked dirty and clean.}. I attended a wedding. I saw wedding \index{clothe}clothes\footnote{We found a silk in your clothe. (It seemed ugly and beautiful.) It was in a house. It was a shirt.}. I saw a \index{wedding}wedding\footnote{Enjoyable. Costly.} \index{ring}ring\footnote{My ring looked expensive, and it was found in a jewelry store. Fuzzy. A diamond was in it.} on the hand of a \index{friend}friend\footnote{This friend was in a fraternity house. You said that they were mortal, and you told me they were insignificant. (You found a ring there.)}. 

 I rubbed \index{wheat}wheat\footnote{My wheat was discovered in a wheat field. A wheat field was not in it.} from the \index{head}head\footnote{I saw your head in a helmet. They seemed on and off, and I found an ear within.} into my \index{hand}hand\footnote{Valuable. We found them in a glove. We found a sunglass there.} and eat it. I saw young \index{person}people\footnote{The person was a student but not a bookman, and a lead pencil was not in this student. They were in a school. Creative. They seemed tough.}.

\chapter{}

I was abroad. 

 I footed up \index{account}accounts\footnote{The account was stupid and stupefied. (A ledger was in it.) Your ledger was discovered in an office.}. 

 I drank any \index{acid}acid\footnote{You told me this acid was sweet, and you found it in a chemistry lab. You said that it was fluid.} was an adverse \index{dream}dream\footnote{Your dream appeared asleep and awake, and it was in a rainbow. Someone was within it. A criminal.}. I met an \index{acquaintance}acquaintance. I saw them in the \index{garden}garden\footnote{Your garden looked perennial and annual, and it was a lawn. I found a fungus there. We found it in a garden.}. 

 I added figures with a \index{machine}machine\footnote{Our machine was in a laboratory, and they seemed hard and voiced. (They were not a robot, and a machine shop was within them.)}. 

 I was in affluence. I was displeased with my apparel. I cured \index{bacon}bacon\footnote{The bacon was yummy but not toothsome. It appeared good, and it was in a refrigerator.} was bad. I was a barmaid. I saw them on my \index{person}person\footnote{You told me the person was mean, and it was individualist but not individualistic. (You found it in an apartment.) A condominium.}. I saw others beheaded. I committed \index{bigamy}bigamy. I saw a \index{bishop}bishop\footnote{You said our bishop was not an archbishop.} in my \index{dream}dreams\footnote{This dream was a wish but not a wishing. It was in a rainbow, and a sky was in this rainbow. Cloudy.}. I heard young animals bleating. I wore new \index{boot}boots\footnote{You said that this boot was not essential, and a kitten was within it. (It was in a house.) You said our house was a mansion.}. I saw it soiled or shrunken. 

 I saw a long bridge dilapidated. I crossed a \index{bridge}bridge\footnote{Your bridge was seen in a river, and you said that it was not addictive. It appeared expensive and cheap, and you found a homeless person within.} safely. 

 I attended the \index{burial}burial\footnote{You said that my burial was not powerful.} of a relative. I kept a calendar. I had one successfully treated. 

 I was \index{molding}molding \index{candle}candles\footnote{You found a candle holder in the candle. It was found in a table. (You said it was not an egg.) Your egg was good and ripe, and it seemed blue.}. I interpreted \index{dream}dreams\footnote{This dream was not a wish. This wish did not seem lucid, and a pail was not in it.} of this \index{character}character\footnote{This character was seen in a theater, and you found a seat in the theater. You told me the seat was adjustable.} by the \index{influence}influences surrounding me. 

 I saw a \index{captain}captain\footnote{The captain was found in a charge. A woman was not in your charge.} of any \index{company}company\footnote{A human was not in my company, and they were discovered in a build. A corporation.}. I was looking for a \index{carriage}carriage\footnote{You found someone within. The someone was discovered in a museum, and it was not a neighbor. You told me your neighbor was hostile.}. I saw young \index{calf}calves\footnote{Our calf was both black and white and color.}. I saw fresh. I saw an old bramble grown and forgotten \index{cemetery}cemetery\footnote{I found this cemetery in a field. (I found a monument within.) Quiet.}. I lost at \index{chess}chess\footnote{Someone was within our chess. Your someone was both dangerous and safe, and it was in a zoo. You told me it was innocent. It was a student but not a pupil.}. 

 I read cipher. I saw myself climbing the \index{side}side\footnote{Our side was seen in a dining-room, and a sideboard was within my dining-room.} of a \index{house}house\footnote{A wall was within the house. (It looked blue.) It was a cellar. It was both white and black. It was found in a street.} in some mysterious \index{way}way\footnote{You said that this way was unpredictable. (It was in a mountain, and a climber was within my mountain.) It looked high. You said it was an alp.}. I saw bright transparent \index{cloud}clouds with the sun shining through them. I heard a cock crowing in the \index{morning}morning\footnote{You said the morning was not a breakfast. My breakfast was discovered in a table. (Pleasant.) It seemed powerful.}. 

 I received \index{command}commands\footnote{I found someone there.}. I sought \index{refuge}refuge\footnote{You saw your refuge in a refugee. Our refugee was a refugee camp but not a camp.} in a \index{convent}convent\footnote{My convent was a convention but not a conventionalism, and you found a person within.}. I passed through a green and luxurious corn-field. 

 I saw others \index{corpulent}corpulent\footnote{Your corpulent was strange.}. I wove cotton \index{cloth}cloth\footnote{The cloth was discovered in a kitchen, and you found a fabric within. A linen. (It appeared soft, and it was smooth but not suave.)}. I was in a beautiful and fertile \index{country}country\footnote{Beautiful. It was not expressive. A human was not in it. It was discovered in a war.}. I saw them fly to the \index{ground}ground\footnote{You said my ground was not a groundcover, and someone was within it. It was not nocturnal.}. I leaved port. I saw a \index{crew}crew\footnote{This crew was found in a space shuttle.} getting ready to leave \index{port}port\footnote{My port was discovered in a campsite. (A ship was not in it.) A schooner.}. I went on \index{crutch}crutches. I was \index{decorating}decorating. I showed my \index{devotion}devotion to God. I was devout. I lost my \index{inheritance}inheritance by \index{disobedience}disobedience. I was kicked by this little animal. I entered a \index{door}door\footnote{We saw our door in a wall, and it seemed underground. It was large. It was an entrance but not an entree, and I found a lock there.}. I saw a \index{flock}flock\footnote{The flock was in a meadow, and we found a butterfly within.} of white \index{dove}doves\footnote{You said that the dove was safe, and you said they were not a dovecote.}. I saw wild \index{duck}ducks\footnote{Our duck was discovered in a pond, and you told me it was dumb.} on a clear \index{stream}stream\footnote{This stream was found in a river, and it seemed shallow. A lizard was in it, and you said it was a brook.} of \index{water}water\footnote{An eel was in our water. (It was brutal.) It was in a soup, and our soup was not a miso.}. I ate \index{egg}eggs\footnote{My egg was not yummy, and it looked white and black. (It was in a grocery store.) I found a yolk in it.}. I rode an \index{elephant}elephant\footnote{This elephant was endothermic and heat-absorbing, and you told me it was cute. It was in a zoo, and I found someone there.}. I failed in impressing others with my \index{eloquence}eloquence. 

 I saw or searching through \index{encyclopedia}encyclopedias\footnote{Your encyclopedia was useful. A mammoth was not in it. (Fragile.) You found it in an ice age.}. I broke an \index{engagement}engagement\footnote{I saw your engagement in a drain. Your drain was an otorrhea.}. I read or telling \index{fable}fables\footnote{My fable was fictional but not fictitious.}. I saw my own \index{face}face\footnote{You told me my face was impossible. You said they were not a hair, and I found a nose in them.}. I asked \index{favor}favors\footnote{This favor was seen in a center. You said it was a pizza.} of \index{anyone}anyone\footnote{My anyone seemed good and evil.}. I felt \index{fear}fear\footnote{The fear appeared understandable. (A gazelle was within it.) A phobia. Contagious.} from any \index{cause}cause\footnote{The cause appeared unknown and known. A cause of action was not in it.}. I built a \index{fence}fence\footnote{An apple tree was within your fence. Smart.}. I was stricken with this \index{malady}malady. 

 I saw newly plowed \index{field}fields\footnote{You found a bug within, and my bug was in a garden. It seemed small. (It did not seem small.) A water strider.}. I was defeated in a \index{fight}fight\footnote{Someone was not in our fight, and it seemed dangerous. It was not a row. (This row was dangerous and grievous.) We found it in a table.}. 

 I saw beautiful hands. I saw others in this \index{plight}plight. I floated. I was shot at while flying. I studied geography. I dreaamed of \index{meeting}meeting\footnote{Our meeting was discovered in a meetinghouse. (Our meetinghouse appeared white.)} my \index{grandparent}grandparents\footnote{This grandparent was hard to please and hard-to-please.} and conversing with them. I dealt in \index{grindstone}grindstones\footnote{Your grindstone seemed cold.}. I saw a \index{grotto}grotto\footnote{Our grotto was competitive but not free-enterprise.}. I found articles of \index{value}value\footnote{You said our value was a freedom. You told me your freedom was priceless.} in a \index{gutter}gutter\footnote{The gutter was discovered in a roof. I found a skylight there. (You said that it was flat, and it appeared red.)}. I saw myself covered with hair. I wore a new hat. I saw \index{field}fields\footnote{You told me my field was ugly, and it was not beautiful. I found a wild flower within, and we saw your wild flower in a field.} of newly cut \index{hay}hay\footnote{The hay was found in a loft. (It seemed organic and functional.) I found someone there. A neighbor.}. I saw \index{load}loads\footnote{This load was seen in a train station, and I found a ticket window there.} of \index{hay}hay\footnote{Your hay was a haystack but not a rick. It was organic, and a haystack was not in it. It was in a loft.} passing through the \index{street}street\footnote{Our street was not a lane. Our lane was in a highway, and our highway was grey but not hoar. A litter was within it.}. I saw a \index{person}person\footnote{Our person was an actor but not a role player. You said that our actor was not strange. You found them in a theater.}'s \index{head}head\footnote{A mouth was within your head. You told me they were safe, and we found them in a helmet.}. I ascended to \index{heaven}heaven\footnote{Blue. You found it in a sky, and a harp was in it.}. I was in \index{heaven}heaven\footnote{We found a soul there, and it appeared heavy. It was in a sky, and it was blue.} and \index{meeting}meeting\footnote{We found the meeting in a meetinghouse, and it was ugly but not slimy.} Christ and \index{friend}friends\footnote{The friend did not seem selfish. We found them in a door. You found a handle within, and you told me it was liquid. It was an entrance.}. I found hidden things. I saw \index{fine}fine\footnote{The fine was discovered in a cellar, and we found a furnace in this cellar. It seemed expensive. It seemed dark and light.} \index{stallion}stallions\footnote{You said the stallion was a male horse. (It was seen in a farm.)}. I rode a \index{horse}horse\footnote{You said my horse was not a mustang, and it was in a stall. You said that it was competitive, and it appeared fast. We found a cowboy in it.} to ford a \index{stream}stream\footnote{A lizard was in the stream. Shallow. (It was not a brook.) Your brook was both shallow and deep. You saw it in a forest.}. I forded a \index{stream}stream\footnote{The stream was discovered in a river. (A bridge was not in our river.) The bridge was addictive and habit-forming, and it was big.}. I saw \index{horse}horses\footnote{Competitive. A barn was in it. You found it in a country. You told me our country was ugly.} pulling \index{vehicle}vehicles\footnote{I found the vehicle in a freeway. You found a person in it. The person appeared endothermic. (You told me it was nonhuman.) A cousin.}. I saw dead and wounded caused by a hurricane. I was industrious. I leaved an \index{infirmary}infirmary\footnote{The infirmary was white and ashen.}. I was insolvent. I looked for a \index{janitor}janitor\footnote{A bucket was within our janitor, and you saw them in a school. They appeared weird.} and fail to find me. I found me. I defended myself with a \index{javelin}javelin\footnote{The javelin did not seem cool.}. 

 I saw a dead jay-bird. I felt jolly and was enjoying the \index{merriment}merriment of \index{companion}companions\footnote{A woman. My woman was in a kayak, and my kayak seemed cool.}. I knitted. I ate \index{lamb}lamb\footnote{You saw my lamb in a farm. A vineyard. A tractor was not in it.} \index{chop}chops\footnote{I saw my chop in a chopper.}. 

 I saw a \index{lamp-post}lamp-post\footnote{We saw my lamp-post in a street corner.} across my \index{path}path\footnote{You said your path was not a lane. The lane was in a highway. (You said that it was unpredictable.)}. I leapt over an \index{obstruction}obstruction. 

 I was associated in any \index{way}way\footnote{I saw our way in a mountain, and you found a peak in your mountain.} with learned \index{person}people\footnote{This person was in a bus stop. I found a line within, and you told me the line was one-dimensional.}. I saw shriveled \index{lemon}lemons\footnote{Your lemon was good. It seemed soft. I found it in a lemonade.}. I concealed a \index{letter}letter\footnote{Our letter appeared sharp, and you found a statement within. You found your statement in a press.} from my \index{sweetheart}sweetheart or \index{wife}wife\footnote{My wife was female. They seemed nice. We saw them in an at home.}. 

 I tried to conceal a \index{letter}letter\footnote{The letter was thin. We saw them in a mail, and you found a statement in them.} from my \index{sweetheart}sweetheart or \index{wife}wife\footnote{We saw your wife in a marriage. (Female.) You told me they were androgynous.}. I had them taken down. I carried a \index{load}load\footnote{My load was discovered in a train station, and a ticket window was in this train station.}. I saw others thus engaged. 

 I heard it whistle. I was lucky. I saw old \index{machinery}machinery\footnote{I found an industry there.}. I was in a \index{market}market\footnote{You saw my market in a city, and a coupon was in it.}. I ate \index{marmalade}marmalade\footnote{My marmalade was both transient and immanent.}. I saw a \index{mason}mason\footnote{A lizard was not in the mason.} plying my \index{trade}trade\footnote{We found a trade name in my trade.}. 

 I saw the \index{mast}masts\footnote{Someone was within this mast. It was a poet, and you saw this poet in a coffeehouse. (They were beautiful.)} of \index{ship}ships\footnote{We saw my ship in a port, and a mast was within it. A poet. Beautiful.}. I made \index{memoranda}memoranda. I mended soiled \index{garment}garments\footnote{You saw your garment in a garment bag, and a silk was in it. This silk was not a foulard.}. I went through \index{mire}mire. I found \index{money}money\footnote{This money was not a time, and it looked mutual and nonreciprocal. We found a piggy bank there. (The piggy bank was in a money.)}. 

 I was pursued by a monster. I knew my \index{fate}fate\footnote{Your fate seemed human.}. I held me in \index{conversation}conversation\footnote{You saw your conversation in a party.}. I conversed with a \index{mute}mute. 

 I saw myrrh. 

 I saw others naked. I associated with the \index{nobility}nobility. I rendered obedience to another. I listened to the \index{teaching}teachings of an \index{occultist}occultist. I brought or make an offering. I made \index{ointment}ointment\footnote{My ointment was in a medicine chest.}. I saw them growing. 

 I was in an orchard and see hogs eating the fallen fruit. I saw an \index{organist}organist. I caught one. I saw a well-fed \index{ox}ox\footnote{We found the ox in a rainbow. (Red.) I found someone in it. You said it was an oxymoron. It did not seem creative.}. I used the brush myself. I passed down an \index{avenue}avenue\footnote{The avenue was in a city, and it was grey but not gray. You said it was not a motorway.} of \index{palm}palms\footnote{You found the palm in a palm tree. I found a monkey in your palm tree.}. I saw them in \index{repose}repose. I had \index{patch}patches\footnote{A lawn. (Our lawn looked cool.) It was in a suburb.} upon my \index{clothing}clothing. I admired the golden \index{fruit}fruit\footnote{Sweet. It was discovered in an orchard, and it was a banana but not a banana tree. We found a seed in it, and this seed appeared solid.} upon graceful \index{tree}trees\footnote{An apple tree. (You saw this apple tree in a front yard.) A mailbox was within our front yard.}. I broke a \index{bottle}bottle\footnote{This bottle was a carafe. My carafe seemed recyclable. You saw it in a restaurant.} of \index{perfume}perfume\footnote{A hair gel was in my perfume. The hair gel was in a salon.}. I attended a \index{picnic}picnic\footnote{You found this picnic in a grind, and our grind was a cave. A dirt was in them.}. I smoked a \index{pipe}pipe\footnote{A system was in your pipe, and I saw it in a pipe cleaner. It seemed hollow and solid, and you said it was not a bowl.}. 

 I heard the \index{report}report\footnote{Your report was in a conference, and a table was within my conference. Your table was not a desk.} of one. 

 I saw me \index{lover}lover\footnote{Our lover was in a restaurant. A food was within our restaurant, and you told me it was round. (It was a cafe.)} plowing. I found myself gathering them up from the \index{ground}ground\footnote{We found someone in our ground, and it did not appear good. You said it was a groundcover.}. I lost my \index{pocketbook}pocketbook\footnote{I found a shoulder bag within.}. I saw a \index{prize}prize\footnote{The prize was in a fair. It was a trophy but not a prize.} \index{fighter}fighter\footnote{The fighter was in a fighter pilot.}. I saw or participate in a \index{torch-light}torch-light \index{procession}procession. I found myself stepping into \index{puddle}puddles\footnote{My puddle was found in a boat. The boat was not a tugboat.} of clear water. I saw a \index{pump}pump\footnote{A bee was within my pump. You told me it was edible. It was hard but not arduous, and it was discovered in a boat.}. I shot quail. 

 I saw others with it. I saw white rabbits. I was sitting in the house and see through the \index{window}window\footnote{We saw your window in a house, and your house was not a home. (This home was blue but not juicy.) It was noble, and I found a tabby cat there.} a \index{downpour}downpour of \index{rain}rain\footnote{You said your rain was not a shower, and you found a rain forest in it. Cold. (It was both mild and intense.) You saw it in a street.}. I set one. I saw a \index{baby}baby\footnote{You told me our baby was ignorant. (You said that they were not mean.) They were an infant but not a babe. We found a rifle there.} \index{play}play\footnote{The play was in a playroom.} with its \index{rattle}rattle. I saw reapers busy at \index{work}work\footnote{This work was dynamic. You said it was a homework. (Someone was within it.) My someone was both dangerous and safe. We found it in a lake.} at their \index{task}task\footnote{The task was a medical but not a checkup.}. I saw \index{religion}religion\footnote{We found a heresy in my religion. It was discovered in a confessional, and it appeared evil. It did not appear good.} declining in \index{power}power\footnote{Your power was in a cabinet. They were a knowledge but not a noesis, and you found a power plant in them. You told me this power plant was useless.}. I rented out \index{property}property\footnote{We found a property line within.}. I failed to rent out \index{property}property\footnote{Our property did not seem evil, and it was a ranch. A ranch house was not in this ranch, and I saw it in a prairie.}. I saw a \index{rhinoceros}rhinoceros\footnote{Your rhinoceros did not appear distinct. We found it in a zoo.}. 

 I cooked it. I found that a \index{rival}rival\footnote{Your rival was safe.} had outwitted me. I saw empty \index{river}rivers\footnote{We found a bridge there, and you told me this bridge was big. It appeared addictive, and it was discovered in a train.}. I saw a \index{rocket}rocket\footnote{This rocket was hard and surd. I found it in a launch pad, and you found a person within.} ascending. I found myself on a \index{roof}roof\footnote{This roof was not dirty, and it looked red. You found it in an airplane, and I found a wing in this airplane.}. I was tied with them. I was in a \index{rowboat}rowboat with others. 

 I shielded myself from satan. 

 I was trying to shield myself from satan. I felt that I was trying to shield myself from satan. I ate them. 

 I saw big \index{saw}saws\footnote{Our saw was found in a sawhorse. It was flexible, and it appeared useful.} in \index{machinery}machinery\footnote{An industry was not in this machinery.}. I carried a saw on my \index{back}back\footnote{Important. (I found a seatbelt in them.) I saw the seatbelt in a car. Our car was not a cabriolet, and it was hard and unvoiced.}. I weighed my lover. I scaped arrest. I saw or hear \index{shooting}shooting. I wore \index{silk}silk\footnote{This silk was flexible but not conciliatory. We saw it in a parachute, and you found a silk within. My silk was a foulard.} clothes. I floated in the sky among weird faced and \index{animal}animals\footnote{You told me the animal was cute. (A mouse.) My mouse was in a computer. A cable was within my computer.}. 

 I saw others \index{sowing}sowing. I saw broad. I rode a \index{fine}fine\footnote{My fine looked small, and I found a tablecloth in it. My tablecloth was in a table.} \index{stallion}stallion\footnote{Our stallion was in a field. It was not a male horse.}. I sold a pair of soiled. I saw only the \index{tail}tail\footnote{My tail was found in a back, and I found a fabric in them. You told me my fabric was flexible.} of a \index{beast}beast\footnote{Your beast looked illegal and legal, and they were a beast of burden. They were fragile.}. I found my \index{tea}tea\footnote{We found a teaspoon in our tea. You saw our teaspoon in a drawer. It seemed shiny.} chest empty. 

 I had them filled. 

 I was surrounded by temptations. I saw my \index{tenant}tenant\footnote{I saw our tenant in an apartment. My apartment was tall and marvellous.}. I played a successful \index{game}game\footnote{You said that my game was not painful, and you told me it was enjoyable. It was a backgammon. We found someone in my backgammon.} of tenpins. I had thatched with \index{straw}straw\footnote{Someone was not in the straw. It was found in a strawberry. It was both edible and inedible. (A besom.)} was leaking. I found that a roof which I had thatched with \index{straw}straw\footnote{You said our straw was not a besom. Sweet. You saw it in a strawberry, and I found someone there. You told me the someone was guilty.} was leaking. I saw \index{ice}ice\footnote{This ice was a water ice but not an ice.} thawing. I tickled others. I saw timber. I moved smoothly along. 

 I was on a \index{train}train\footnote{I saw my train in a train station. We found a train ticket there.} and it appeared to move smoothly along. I travelled alone in a \index{car}car\footnote{My car was a bus but not a motorcoach. Expensive. It was man-made but not synthetic. We found a radiator there, and we found the radiator in a house.}. I caught one with a \index{hook}hook\footnote{You found a chlamydia there. It was in a bedroom.}. I saw \index{turnip}turnips\footnote{Your turnip was discovered in a refrigerator, and it was green but not fleeceable.} growing. I saw \index{turtle}turtles\footnote{I saw your turtle in a zoo. Cute. Slow-moving.}. I put a \index{letter}letter\footnote{My letter was found in a mailbox. Your mailbox was open, and I found a letter in it.} in one. I was a \index{usurper}usurper. I saw poisonous \index{vine}vines\footnote{A vinery was in your vine. (It appeared sour and sweet.) It was seen in a jungle, and you said that it was not alive.}. 

 I found myself \index{walking}walking rapidly in my dreams. I saw a \index{walking}walking \index{stick}stick\footnote{This stick was in a forest. Pretty. I found a moss in it, and the moss was both green and ripe.}. I jumped over it. I wandered through \index{waste}waste\footnote{A garbage was in my waste, and the garbage was a refuse but not a garbage. The refuse was found in a dump.} \index{place}places\footnote{An anemone was not in this place. (My anemone was in an ocean, and it was both cool and warm.)}. I had it sprayed on my \index{head}head\footnote{My head was in a morgue, and a head was in the morgue.}. I was associated with wealthy \index{person}people. 

 I was reading the \index{report}reports\footnote{You found our report in a reporter, and you said that it was fictional.} of a \index{weather}weather\footnote{You told me the weather was intense, and it was not a tornado. (It was in a newspaper.) You found a cartoon within.} \index{bureau}bureau\footnote{A drawer was not in your bureau, and it was a self-justification but not an alibi. It was discovered in a city.}. I thought I was reading the reports of a \index{weather}weather\footnote{You told me the weather was intense, and it was a blizzard but not a snowstorm. (You found it in a newspaper, and I found a story in your newspaper.)} \index{bureau}bureau\footnote{My bureau was a self-justification but not an excuse. A drawer was in it, and your drawer was in a kitchen. Dark.}. I saw some \index{one}one\footnote{My one was in an office. It seemed self-employed, and it did not seem many. Someone was in it. Our someone was a neighbor but not a neighbour.} at me \index{wedding}wedding\footnote{My wedding was not free. Romantic.} dressed in mourning. I saw others weeping. 

 I weighed. I weighed with my \index{lover}lover\footnote{We found a penis within, and we saw them in a restaurant. A steakhouse. This steakhouse was rectangular but not orthogonal.}. I saw it in \index{sack}sacks\footnote{You said the sack was not a balloon, and we saw my balloon in a sky. A plane was in my sky. You told me it was down.} or \index{barrel}barrels\footnote{The barrel was large and prominent. I found an oil in it, and your oil was found in an underground. You told me the underground was dark.}. I saw or drink it. I saw \index{window}windows\footnote{Our window was clear. (It was in a library.) Your library seemed white. You found a literature there. A poetry.}. I saw the \index{wing}wings\footnote{A flap was within this wing, and they were in a mansion. Your mansion was noble.} of fowls or birds. I yielded to another's wished.

\chapter{}

I abandoned a \index{mistress}mistress. 

 I had left my abode. I had an \index{abscess}abscess\footnote{Your abscess was deadly but not venomous.} which seemed to have reached a chronic \index{stage}stage\footnote{We found a performer in your stage. This performer was in a party, and the party looked uncomfortable. Sad.}. 

 I had reached a chronic \index{stage}stage\footnote{Our stage was a platform but not a chopine. I saw it in a show, and we found a backdrop within. (Red.)}. I picked them from the ground. I threw \index{kiss}kisses\footnote{You said my kiss was a lip. You said that my lip was not free. Moist. Someone was not in it, and our someone was found in a lake.} of adieu to loved \index{one}ones\footnote{1. It was discovered in an airplane. A biplane. A wing was within it. (Expensive.)}. 

 I advocated any \index{cause}cause\footnote{A cause of action was in the cause. It was political.}. I was afraid of a dog. I saw clear \index{bottle}bottles\footnote{We found a beer in the bottle. Wide. It was bitter, and it was not an ale. I saw it in a refrigerator.} of \index{ammonia}ammonia\footnote{Our ammonia was in a cabinet.}. I ate them was not as good. I passed through green. I saw the Holy Ghost descending on Christ. I took a \index{bath}bath\footnote{A bathroom was within my bath. Your bathroom looked dirty and clean. You said it was a restroom. We found the restroom in a library, and it appeared biodegradable.}. I rode a \index{bicycle}bicycle\footnote{Red. A bike. It was in a garage, and a garden hose was not in the garage.} up \index{hill}hill\footnote{Someone was within my hill, and it was a sand dune.}. I saw others blind. I saw a \index{woman}woman\footnote{You found a period within. They were not a mother. They looked pretty. (They were mortal and deathly, and we found them in a bedroom.)} tying my \index{bonnet}bonnet\footnote{This bonnet appeared organic, and a bee was within it. This bee was in an apiary.}. I saw myself caught among \index{briar}briars\footnote{Hot.}. I saw a \index{bridge}bridge\footnote{A homeless person was within the bridge. The homeless person was discovered in a bridge. You told me this bridge was little. Addictive.} give \index{way}way\footnote{My way was a run but not a running, and I found a human in it. Unpredictable. (It was in a mountain.) You told me the mountain was ugly.} before me. I saw my \index{brother}brothers\footnote{My brother was an uncle, and the uncle was filthy. They were male, and they were found in a family.}. I rode in a cab. I owned a camel. I made a political one. I saw a candlestick bearing a whole candle. 

 I was participating in a \index{carnival}carnival\footnote{A ride was not in our carnival, and it was found in a fair.}. 

 I rode together in a \index{cart}cart\footnote{You told me my cart was animate, and it was a wheelbarrow but not a barrow. You said that it was opaque, and we found a cartoon in it. I saw this cartoon in a newspaper.}. I saw one filled. 

 I had plenty of \index{cash}cash\footnote{This cash was in a cash register, and I found a money there.}. I saw them green and shapely. I ate it with my \index{lover}lover\footnote{Attractive. (We found a penis in them.) My penis was in a vagina.}. I rode in a chariot. 

 I saw a \index{fire}fire\footnote{You found our fire in a fire extinguisher. We found a hose there, and the hose looked tubular.} \index{burning}burning\footnote{Our burning did not appear creative, and it seemed irreversible and reversible.} in a \index{chimney}chimney\footnote{Your chimney was seen in a roof. The roof appeared dirty. It appeared red. A chimney was within it.}. I saw \index{clothe}clothes\footnote{The clothe appeared dirty, and it was seen in a store. A skirt. A nylon was in it.} soiled and \index{torn}torn\footnote{You said that the torn was big, and we found a projectile there. It was in a tornado. A twister. You told me it was destructive.}. I was approached by a \index{person}person\footnote{You said our person was not an actor. Strange. (It did not seem hairy.) You found a soul in it, and you saw it in an apartment.} bearing a club. I saw bright coals of \index{fire}fire\footnote{You told me this fire was useful, and it was in a house. We found a hose there.}. I saw my \index{corpse}corpse\footnote{My corpse was seen in a grave. Grey.} in a \index{coffin}coffin\footnote{Your coffin seemed opaque. We found a velvet in it, and my velvet was discovered in a voice.}. I saw or visit a \index{coffee}coffee\footnote{Someone was not in your coffee, and it was a cappuccino. The cappuccino was both black and white.} house. 

 I heard comic \index{song}songs\footnote{You found your song in a musical. (Musical.) You found a sound there. Our sound was a noise but not an interference.}. I was copying a \index{letter}letter\footnote{A statement was not in this letter, and you saw them in an office. Ugly.}. I drew \index{champagne}champagne\footnote{Romantic. (It was in a refrigerator.)} \index{cork}corks\footnote{We found a tack within, and it was found in a corkscrew.}. I saw young \index{corn}corn\footnote{Our corn seemed green. It appeared yellow. You saw it in a can.} newly ploughed. I danced myself. I saw the dead. I was on a \index{ship}ship\footnote{The ship was a schooner. You told me it was safe. It was in a shipwreck, and you found someone within.} and that a storm was raging. I was referring to a \index{dictionary}dictionary\footnote{I found a marmoset there. We saw this marmoset in a rainforest. (It was not strange.)}. I saw shelves of polished \index{dish}dishes\footnote{The dish was a plate, and the plate was round but not pear-shaped. (A steak was within it, and the steak was seen in a grocery store.)}. I traveled alone. I entered a \index{door}door\footnote{My door was large, and it seemed underground. It was found in an apartment, and it was not an entrance. We found a lock there.} at \index{night}night\footnote{You told me your night was scary. I found a night club there.} through the rain. I saw a \index{drama}drama\footnote{A coincidence was within your drama, and a dramatic performance.}. I could n't get dressed in \index{time}time\footnote{You saw this time in a timer.} for a train. I was afflicted with the \index{dropsy}dropsy. I saw a dead \index{eel}eel\footnote{Your eel was creative but not originative.}. 

 I saw broken \index{egg}eggs\footnote{Our egg was edible and eatable, and it was in a supermarket. An embryo was in it.} and they was fresh. I saw or wearing an eyeglass. I saw a fawn. I saw my own \index{foot}feet\footnote{Round. (They were a football team.) A human was not in our football team, and you found it in a university.}. I climbed to the \index{top}top\footnote{I found someone there. (It was found in a build.)} of a fence. I threw the \index{fence}fence\footnote{You found a cow there, and they were both smart and stupid.} down and walk into the other \index{side}side\footnote{Our side was seen in a bedroom, and it was decorative. We found a sideshow in it.}. I saw my \index{home}home\footnote{This home did not appear big. A house. My house seemed expensive and cheap, and we found a room in it. My room was in a school.} \index{burning}burning\footnote{Stupid. Irreversible.}. I saw a large \index{conflagration}conflagration. I saw fireworks. I knew in the \index{firmament}firmament. I saw people me knew in the \index{firmament}firmament. I fell into a clear \index{pond}pond\footnote{You found a duck in our pond. I found it in a grind. (You told me it was infinite.)}. I saw a \index{friend}friend\footnote{We saw our friend in a fraternity house, and someone was within them. They were both selfish and unselfish. Important.} with a white cloth tied over my \index{face}face\footnote{A lip was in this face, and they were a hair. You told me they were impossible.}. I saw \index{fine}fine\footnote{A tablecloth was within my fine, and it was in a fine art. It was a fine art but not an art.} \index{fur}fur\footnote{My fur was in a basement, and you said this basement was a first floor.}. I walked with one's \index{lover}lover\footnote{My lover appeared attractive and repulsive, and you found a penis within. My penis was seen in a vagina. It was a male genitalia but not a male genital organ.} through a garden where \index{flowering}flowering \index{shrub}shrubs\footnote{I found a lizard in this shrub. This lizard seemed small and big. They were not a skink. Pure.} and plants abounded. I passed through a garlic \index{patch}patch\footnote{A lawn.}. I saw a female ghost in long. 

 I wore new \index{glove}gloves\footnote{We found a map in your glove, and you told me your map was useful. It was in a glove compartment.}. I found a \index{pair}pair\footnote{Dark. (You said it was not a forceps.)} of \index{glove}gloves\footnote{This glove appeared soft. A mitten. My mitten was both cold and hot, and I found it in a cold.}. I saw a \index{graveyard}graveyard\footnote{A casket was within our graveyard, and this casket was discovered in a funeral.} barren. I was sharpening \index{tool}tools\footnote{A toolbox was in your tool, and I saw this toolbox in a garage.}. I watched \index{hail-stone}hail-stones fell through \index{sunshine}sunshine\footnote{An apple tree was in our sunshine. (We saw this apple tree in a backyard.) This backyard seemed white.} and \index{rain}rain\footnote{You said your rain was a shower. I found a fungus in this shower. (I saw the fungus in a woodland.)}. I put a halter on a young \index{horse}horse\footnote{You said the horse was not a palomino.}. I saw pure white \index{one}ones\footnote{The one was discovered in an office, and a football field. We found a kitchenette there. 1. It was both many and few.} in large \index{lot}lots\footnote{A lotion was in my lot. This lotion was sticky. It was seen in a shelf.}. I saw others appearing handsome. I played a \index{harp}harp\footnote{Our harp was a harpsichord but not a cembalo, and I found our harpsichord in a concert.} myself. I was hated for unjust \index{cause}causes\footnote{Our cause looked political and nonpolitical, and we found a cause of action within.}. I saw a \index{helmet}helmet\footnote{I found a head within, and it appeared hard. It was not essential.}. I was reading history. I swam on a horse's back through a clear and beautiful \index{stream}stream\footnote{Shallow. It was seen in a bridge. A troll was in the bridge.} of \index{water}water\footnote{You told me this water was dangerous. You found a plankton in it. (It was not absurd.) It was in a rain. A drizzle.}. I rode \index{bareback}bareback\footnote{You said that my bareback was cute.} in \index{company}company\footnote{A human was not in the company. (You said this human was a vintner.) This vintner was found in a winery. They were both intelligent and unintelligent.} with \index{man}men\footnote{We found a human there, and they were seen in a build. A library. You told me it was dark.}. I trimmed a \index{horse}horse\footnote{You saw this horse in a cavalry, and you told me it was light. It was strange and unusual. (You found a cowboy in it, and this cowboy was not a cowboy boot.)}'s \index{mane}mane\footnote{My mane was discovered in a fenland.}. I built a \index{house}house\footnote{My house seemed good. It was in a subdivision. (A bathroom was within it.) A bidet. You told me it was clean.}. I was denouncing \index{idolatry}idolatry. I saw an \index{island}island\footnote{Small. Someone was within it. We saw it in a body of water.}. I saw \index{person}people\footnote{This person was in a hospital. You told me it was familiar. Individualist. I found a soul in it.} on an \index{island}island\footnote{Someone was within the island. I found it in an ocean. You told me it was big.}. I saw my friends started cheerfully on a \index{journey}journey\footnote{A crossroad was not in my journey. My crossroad was in a countryside, and our countryside was beautiful.}. I flew a kite. I made a \index{kite}kite\footnote{A string was in my kite, and it was not educational. It was discovered in an air, and you told me it was white.}. I worked in a \index{knitting-mill}knitting-mill. I saw \index{knot}knots\footnote{You found someone in this knot.}. I ignited my \index{apparel}apparel from a \index{lamp}lamp\footnote{I found an oil within. Our oil was found in a home. (You told me it was nonslippery.)}. I saw \index{land}land\footnote{We found a sea there. You told me it was breathtaking. It was in a country, and you said it was an island.} from the \index{ocean}ocean\footnote{A ship was not in this ocean, and the ship was in a shipwreck. You told me it was dangerous.}. I saw \index{lark}larks\footnote{Your lark was not sad.} flying. I saw a \index{leak}leak\footnote{You saw my leak in a boat, and the boat appeared expensive and cheap.} in \index{anything}anything\footnote{This anything was not a toy, and it appeared infinite and finite. It was in a box. A stuff was within it.}. I learnt. I dealt in \index{leather}leather\footnote{We found my leather in a car seat. (A leather was in your car seat.) You told me the leather was liquid.}. I got \index{letter}letters\footnote{You told me this letter was flat. A statement was within them, and we found our statement in a mail.} bearing unpleasant \index{news}news\footnote{My news was in a newspaper, and the newspaper was skew. (You said that it was lightweight.) We found an editorial there.}. I saw \index{lettuce}lettuce\footnote{The lettuce looked edible, and it was found in a grocery store. I found a toilet paper within.} growing green and thrifty. 

 I was lost in a \index{life-boat}life-boat. I saw a \index{lighthouse}lighthouse\footnote{A lantern was in our lighthouse. We found my lantern in a festival. Our festival was skew.} from a placid \index{sea}sea\footnote{A blowfish was in my sea, and my blowfish was strange and unusual. It was poisonous. It was found in an ocean.}. I admired. 

 I saw caged \index{lion}lions\footnote{A cub. The cub looked square. They were seen in a cubicle. A cubicle was within them.}. I saw a \index{man}man\footnote{A boy. You told me they were unhappy. (Selfish.) They were seen in a suit. We found a mansion in them.} controlling a \index{lion}lion\footnote{I found a zoo in this lion, and we saw your zoo in a camera. You said that this camera was not readable, and it was not a digital camera.} in its \index{cage}cage\footnote{Fierce. A kitten was in it, and it was discovered in a zoo.}. I saw Daniel in the \index{lion}lions\footnote{Alert. (You said they were not a cub.) A gazelle was within them. This gazelle was in a herd.}' \index{den}den\footnote{A black hole. It seemed dark. It looked white. (We found an animal in it.) My animal was in a wild.}. I handled. I saw good-looking women attending the \index{loom}loom. I was surrounded by \index{luxury}luxury\footnote{You found someone in the luxury. Guilty. It was dangerous but not unsafe, and you said it was not a student.}. I protected a \index{friend}friend\footnote{We found someone within, and you said that they were not selfish. You told me they were noncrucial, and they were discovered in a fraternity house.} from undeserved \index{chastisement}chastisement. 

 I played on one. 

 I saw a \index{magician}magician\footnote{My magician was in a party. Mean.}. I saw \index{manure}manure\footnote{You told me our manure was smelly. We found it in a zoo.}. I saw a marmot. 

 I was an attendant at a \index{wedding}wedding\footnote{Expensive. You told me it was cheap.}. I was a \index{master}master\footnote{I found my master in a master bedroom.}. 

 I saw them growing on green \index{vine}vines\footnote{Alive. It appeared sour. It was discovered in a forest, and you found a squirrel there.}. I drank milk. I milked. I saw clear \index{water}water\footnote{Fluid. It was seen in a waterfall. I found a photographer in our waterfall.} pouring over a mill-dam. I drank \index{mineral}mineral\footnote{The mineral appeared c. I found it in a multivitamin, and you said it was not a quartz.} \index{water}water\footnote{The water appeared transparent. I found a seaweed there. My seaweed was green. A kelp. It was in a beach.}. I danced it myself. I killed one. I saw or hear a mocking-bird. I saw morocco. I took. I found myself studying the \index{mystery}mysteries\footnote{We saw our mystery in a universe. This universe was not fuzzy, and you found a star there.} of creation. 

 I admired my \index{nudity}nudity. I was. I viewed the \index{heaven}heavens\footnote{A lemur was in our heaven, and it was blue. It was found in a sky, and you said this sky was not a river. (My river was dark and drear.)} and beautiful landscapes from an \index{observatory}observatory\footnote{Your observatory was both large and little, and we found someone in it.}. I ate it. I heard the solemn. I pacified suffering ones. I endeavorred to pacify \index{suffering}suffering \index{one}ones\footnote{Our one was a football field but not a gridiron, and it was many. You told me it was salaried. It was in an airplane. You found someone in it.}. I cooked them. I counted \index{penny}pennies\footnote{A coin was in this penny, and it was worthless. (We found it in a drawer.) The drawer was not large.}. I ate one. I made a \index{pillow}pillow\footnote{A feather was not in our pillow. Comfortable. (It was discovered in an airport.) It did not appear heavy.}. I saw planes. I saw \index{wall}walls\footnote{You told me my wall was black and white. We found a hole there. It was a membrane but not a tissue layer, and you found my membrane in an animal.} plainly plastered. I hired one. I dug them. I was in quarantine. I was rescued by me \index{lover}lover\footnote{A penis was within the lover. The penis was in a vagina, and a male genitalia.} from quicksand. I saw me \index{lover}lover\footnote{You told me your lover was repulsive. I saw them in a backyard. (A penis was not in them.) A male genitalia.} in a \index{rage}rage\footnote{Your rage was enjoyable and gratifying.}. I saw a \index{rainbow}rainbow\footnote{Our rainbow was in a water fountain. We found a spigot there.}. I saw the \index{rainbow}rainbow\footnote{You told me this rainbow was ugly, and it was in a water fountain. We found a sky in it.} hanging low over green \index{tree}trees\footnote{My tree appeared green, and you said it was an apple tree. You found someone there, and my someone was seen in a fair. It seemed guilty.}. 

 I caught \index{rat}rats\footnote{The rat was found in an alley, and a rat was in my alley. It was grey. It seemed narrow.}. I was being resuscitated. I ate it. I saw others with \index{ring}rings\footnote{My ring was not fuzzy. It looked blue. We saw it in a finger, and we found a diamond in it.}. I saw \index{rye}rye. I used a \index{hand-saw}hand-saw. I was an \index{object}object\footnote{An object program was in this object, and it was fuzzy and muzzy. (It was heavy.) A stapler. It was in a basement.} of \index{scandal}scandal\footnote{Our scandal was in a politician. I found a scandal there, and they were a mayor. (You said that they were not emotional, and they appeared insincere and sincere.)}. I discussed a \index{scandal}scandal\footnote{The scandal was seen in a newspaper. (Transient.) It was unpleasant.}. 

 I glided swiftly over the \index{sea}sea\footnote{I found a driftwood in my sea, and we saw the driftwood in a beach.} with my \index{lover}lover. I saw them looking scraggy and sick. I saw naked shoulders. I found \index{silver}silver\footnote{You said the silver was not a sterling silver. It was seen in a silver mine.} \index{money}money\footnote{Your money was mutual. (We found a purse there, and your purse was in a department store.)}. I treated others to this and other delectable iced drinks. I was discussing the immortality of my \index{soul}soul\footnote{We saw the soul in a person.}. I saw a very large \index{spider}spider\footnote{This spider was in a cellar. It looked fatal.} and a small one coming towards me. I ascended \index{step}steps\footnote{I saw our step in a hardware store, and I found a cord in this hardware store.}. 

 I made \index{deal}deals\footnote{A drug was not in your deal, and it was discovered in a casino.} in ore-bearing \index{rock}rock\footnote{Your rock did not appear beautiful. You found a cave in them. They were in a bridge. (Pretty.) They were a marble.} \index{land}lands\footnote{I found someone there. (You said the someone was not a criminal.) It seemed guilty and innocent. Dangerous. It was seen in a hospital.}. I was in a familiar \index{street}street\footnote{My street was dark. I found a bicycle there, and you said our bicycle was a bike. (This bike was discovered in a garage.)} in a distant \index{city}city\footnote{A build was within my city, and it was in a county.}. 

 I stumbled while \index{walking}walking or running. I saw the young taking suckle. I saw clear water and green \index{growth}growths\footnote{Your growth was found in a field, and it was good.}. I went through a swamp where I saw clear \index{water}water\footnote{A rain. We found a lemur there. (It was cold.) It was discovered in a forest. It looked wet and dry.} and green growths. I was repeating and pondering over one. I was suffering from a sore thumb. I saw \index{topaz}topaz. I wore a uniform. I had \index{vertigo}vertigo. I was vexed. 

 I visited. I had a jealous \index{rival}rival\footnote{You said that our rival was safe.} threw it in my \index{face}face\footnote{You said your face was not a hair. This hair was natural, and a hairpin was not in it.}. I bathed my \index{face}face\footnote{A mouth was within my face. You told me your mouth was noncrucial. A lip. (We found our lip in a can.)} and hands in a \index{bowl}bowl\footnote{The bowl seemed heavy and light, and we found it in a kitchen. (A plate was in your kitchen.)} of clear \index{water}water\footnote{Your water was in a rain, and the rain was cold. Cloudy. We found a lemur in it, and you said it was a drizzle.}. I was possessed of much wealth. I was making my will. I saw a \index{windmill}windmill\footnote{Someone was not in our windmill.} in \index{operation}operation\footnote{The operation was not a medical procedure, and it was in a computer.}. I saw workshops.

\chapter{}

I abandoned my \index{business}business\footnote{A shark was not in the business, and you said it was not a manufacturer.}. I saw my \index{abdomen}abdomen\footnote{A navel was within this abdomen.}. I saw it swollen. I found some \index{error}error\footnote{Your error seemed bad. An accident.} in \index{addition}addition\footnote{Our addition seemed commutative.}. I reached the extreme \index{point}point\footnote{A point in time was not in your point, and it appeared sharp and dull. We found it in a plane.} of \index{ascent}ascent. I found myself escaping from the \index{path}path\footnote{A lane. Our lane was outside and remote.} of one. I was in a bake \index{house}house\footnote{You found a bathroom there. A restroom. (This restroom was discovered in a library, and my library was not dark.)}. I saw \index{silver}silver\footnote{A spoon was in our silver. Your spoon was in a bowl. A curet. It was not wooden.} and \index{bank-note}bank-notes accumulated. I saw \index{beaver}beavers\footnote{A kitten was within our beaver, and it was in a river. It seemed warm-blooded.}. I saw one newly furnished. I saw a \index{bracelet}bracelet\footnote{You saw my bracelet in a jewelry store.} encircling my arm. I saw them flying about. I saw a cageful of birds. I saw a \index{camping}camping \index{settlement}settlement. I rode in one. I saw a \index{herd}herd\footnote{My herd was a cow. It was discovered in a country, and the country was beautiful. A government was not in it.} of \index{cow}cows\footnote{Your cow was found in a stable, and you told me the stable was clean. (It was ugly and frightful.) You found a leather in it.} at milking \index{time}time\footnote{A confetti was not in your time, and you told me it was theoretical. (I found it in a train station.)}. I walked in a cave with my \index{lover}lover or \index{friend}friend\footnote{The friend was emotional and excited. They were found in a door. An entrance. It looked large and little, and a neighbour was within it.}. I saw cherubs. I beheld Christ. I gathered white \index{chrysanthemum}chrysanthemums\footnote{Your chrysanthemum was green but not dark-green.}. I ate baked \index{clam}clams\footnote{You found a clam chowder in your clam. (It looked versatile.) It was in a school, and this school was an elementary school but not a grade school.} with my \index{sweetheart}sweetheart. I engaged in \index{combat}combat\footnote{The combat was in a combat mission. It was a tank but not a storage tank, and someone was in it.}. I was held in contempt by others. I ate green \index{corn}corn\footnote{I saw our corn in a field, and our field was expensive. It did not appear beautiful.}. 

 I had an \index{abundance}abundance of nice. 

 I was cunning. I curried a horse. I felt the \index{dew}dew\footnote{You said that your dew was not heavy, and it was in a library. (My library was dirty.)} falling on me. I saw others diving. I saw one dead. I saw others drowning. I saw young \index{eagle}eagles\footnote{The eagle seemed free.} in their eyrie. I was anxious to obtain an \index{education}education\footnote{You found your education in a university. Yellow.}. 

 I obtained an \index{education}education\footnote{The education was in a university, and you said that our university was yellow.}. I found a \index{nest}nest\footnote{We found a feather in the nest, and this feather was a quill.} of \index{egg}eggs\footnote{My egg was discovered in a refrigerator, and it seemed unhealthy. It seemed white, and I found an embryo there.}. I resisted \index{enchantment}enchantment. I was living on a \index{farm}farm\footnote{A tractor was not in my farm, and it was not a vineyard. You told me it was silly. It was discovered in a country. Expressive.}. I was getting fat. I saw \index{feather}feathers\footnote{Our feather was in a bird nest.} falling around me. I saw \index{fern}ferns\footnote{Our fern did not appear alive.}. I crossed a \index{ferry}ferry\footnote{You found a train in this ferry.} while the \index{water}water\footnote{The water was a steam, and it was blue. You said that it was brutal. (A dolphin was in it.) It was in a waterfall.} was calm and clear. I ate them. I saw \index{fish}fish\footnote{This fish was a catfish but not a wolf fish. Naked. It was seen in an ocean, and we found a blowfish in it. Your blowfish did not appear cool.} in clear-water \index{stream}streams\footnote{A brook. (The brook was in a bridge.) A brownstone was not in it.}. I played a \index{flute}flute\footnote{Solid. (You found it in an orchestra, and you said it was a woodwind.)}. I saw a clear fountain sparkling in the \index{sunlight}sunlight\footnote{The sunlight seemed warm and cool, and a lizard was in it.}. 

 I saw \index{vegetable}vegetables\footnote{Our vegetable was in a garden. (Nice.) We found a rosebush within.}. I saw a \index{gas}gas\footnote{You found a cigarette there, and it was an acetylene. You told me it was flammable. It was in a boat.} \index{lamp}lamp\footnote{Your lamp looked bright and dimmed, and I saw it in a house. (Your house seemed noble.) We found a window there, and you said it was an igloo.}. I was in grease. 

 I heard groaned. I compared a white \index{hair}hair\footnote{Your hair was both soft and hard, and a ribbon was in it. A bow. (You told me it was thick, and it was seen in a typewriter.)} with a black one. 

 I caressed the \index{hair}hair\footnote{You said my hair was not an eyebrow, and we found a ribbon in it. Functional. We saw it in a hair. It was red.} of a \index{woman}woman\footnote{Our woman was a girl. Someone was within the girl, and my someone was guilty. It was in a desk. The desk was sticky but not gummy.}. I saw \index{ham}hams\footnote{Our ham did not seem good. (We saw them in a hamburger.) A hamper was in them. They were a hamburger.}. I admired me own \index{hand}hands\footnote{Our hand seemed dangerous. (You found a finger there, and our finger was in a fingernail.) It was a thumb but not a quarter round, and the thumb appeared messy.}. I saw \index{silk}silk\footnote{You said my silk was a foulard.} handkerchiefs. I maintained a \index{harem}harem. I saw rich \index{headgear}headgear. I used a \index{hoe}hoe. I saw myself riding a fine bay \index{horse}horse\footnote{Our horse was both hairy and hairless, and we found someone in it. We saw my someone in a pool. It looked guilty, and it was a neighbor but not a neighbour.}. I rode a \index{horse}horse\footnote{You saw this horse in a movie. It was a pony.} in a \index{race}race\footnote{We saw my race in a racer.}. I met my \index{ideal}ideal\footnote{We saw this ideal in an idealist.}. 

 I saw a newly born \index{infant}infant\footnote{You said that our infant was happy. They seemed nostalgic, and they were a kitten. We found a grenade within.}. I saw friends in high \index{position}positions. I interceded for some \index{one}one\footnote{Your one was two. (Many.) You said it was a football field. Your football field was found in a player.}. I saw \index{ivy}ivy\footnote{My ivy did not appear green.} growing on trees or \index{house}houses\footnote{My house was big. It was in a residential area. (It was a cellar, and a bathroom was not in it.) This bathroom seemed rectangular.}. I saw jasper. I had \index{transaction}transactions with a Jew. I bought them. I danced a \index{jig}jig\footnote{My jig was intimate but not knowledgeable, and we saw it in a table. You found a piece in it. Our piece appeared black and white.}. I came before a \index{judge}judge\footnote{We found someone within. The someone was found in a pool. Educational.}. 

 I drank \index{wine}wine\footnote{My wine was discovered in a winery, and a fan was in it. You said that it was not wide. A red wine.} from a \index{jug}jug\footnote{You found a jug band within.}. I saw a \index{kangaroo}kangaroo\footnote{We found a pouch in the kangaroo, and I saw this pouch in a jacket.}. I was much affrighted. I cleaned a \index{lantern}lantern\footnote{We saw this lantern in a cave, and you found a fungus within. This fungus was a mushroom but not a mushroom-shaped cloud.}. I bought a \index{lantern}lantern\footnote{This lantern was in a cabin. (I found a dish in the cabin.)}. I sat on some \index{person}person\footnote{Individualist. (You told me it was nonhuman.) I saw it in a theater. You found an actor in the theater.}'s \index{lap}lap\footnote{My lap was in a laptop, and it was a laptop but not a laptop computer. I found a typewriter keyboard within.}. I ate them. I was carrying my own \index{luggage}luggage\footnote{This luggage was discovered in a trunk, and it seemed fuzzy. I found a bag in it. (A satchel.)}. I listened to the music of a \index{lyre}lyre\footnote{The lyre was solid and unanimous.}. I saw or \index{travel}travel\footnote{You found my travel in a bus depot, and someone was not in our bus depot. This someone appeared dangerous.} on a macadamized \index{road}road\footnote{You said that this road was not unpredictable. (We found a fork in it.) My fork seemed heavy and light. It was in a drawer.}. I saw it burnt. I saw the \index{moon}moon\footnote{I found a dust within. Yellow. You found it in a sky. It was round and pear-shaped.} with the aspect of the \index{heaven}heavens\footnote{The heaven was not heavy, and it was found in a heavenly body.} remaining normal. I committed \index{murder}murder\footnote{A meat. You told me it was dangerous, and it did not seem punishable. (You found it in a murderer.)}. I wore a sprig of \index{myrtle}myrtle\footnote{Fragile.}. I was surrounded by night. I received them. 

 I saw them. I ate parsley. 

 I ensnared them. I killed them. I saw them growing. I was executing difficult. I was descending into one. I was afflicted with the plague. 

 I used a \index{plane}plane\footnote{The plane was strong, and I found a seat belt there. Your seat belt was in a plane.}. I saw \index{carpenter}carpenters\footnote{Your carpenter was not a see, and you saw our see in a basement. A rat was not in my basement. Our rat seemed gentle.} using their \index{plane}planes\footnote{Round. It was mechanical, and you found a fork in it. It was in a taxiway, and a jet plane.}. 

 I saw a \index{porpoise}porpoise\footnote{You said that my porpoise was not cool, and it was in an ocean.}. I ate them. I received \index{present}presents. I worked a \index{pump}pump\footnote{We found a bee within. It appeared edible and inedible, and it was seen in a jar. It was hard but not laborious.}. I attended a Quaker \index{meeting}meeting\footnote{You said that this meeting was not tall, and we found it in a meetinghouse.}. I was putting a \index{quill}quill\footnote{The quill was found in a quill pen. (It was soft, and it was a quill pen but not a quill.)} on my hat. 

 I saw others raking. I saw. I wore \index{ring}rings\footnote{A diamond was within this ring. (Our diamond was seen in a jewelry store.) It was decorative and ornamental, and you told me it was clear.}. I jumped a rope. 

 I found myself defeated in a \index{rowing}rowing \index{race}race\footnote{I found someone within. I saw our someone in a desk.}. 

 I used ` ` \index{rubber}rubber\footnote{I saw my rubber in a tire. It looked elastic, and you said it was not a balloon.}'' as a \index{slang}slang\footnote{This slang was a gay. You found a fruit there, and your fruit did not seem yummy.} term. I saw \index{coffee}coffee\footnote{Your coffee was discovered in a house, and it was both illegal and legal. A coffee shop was not in it.} made of \index{rye}rye. I saw or eat \index{rye}rye \index{bread}bread\footnote{Our bread was in a toaster. A toaster oven was within our toaster, and you said that they were not hard. You told me they were good.}. I ate it. I bought one. I scratched my \index{head}head\footnote{This head was on. They were found in a helmet. (Your helmet was not brown, and a head was within it.)}. I saw a \index{seamstress}seamstress\footnote{My seamstress did not seem weird.}. I was seduced. I heard a \index{serenade}serenade. I saw \index{shepherd}shepherds\footnote{Your shepherd was not competitive.} watching their \index{flock}flocks\footnote{This flock was seen in a roof. A blowfish was in it.}. I had them blacked. I heard \index{singing}singing. I saw another young woman on the \index{stage}stage\footnote{The stage appeared red, and you said it was a platform. You saw this platform in a build.} clothed in sheer robes. I was swimming with a \index{girl}girl\footnote{You said the girl was not a niece, and the niece was seen in a reunion. Your reunion was transient and transitory.} \index{friend}friend\footnote{A flower was within our friend. Our flower was in a table. A desk. Opaque. It was sticky but not unenviable.} who was an artist in \index{swimming}swimming\footnote{A swimmer was within your swimming.}. I wore a \index{talisman}talisman\footnote{Your talisman was creative but not originative.}. I saw a \index{tarantula}tarantula\footnote{Fatal.}. 

 I was teased. I saw my thigh smooth and white. I slaked it. I saw others thirsty and drinking to slake it. I saw rugs of \index{tiger}tiger\footnote{This tiger was found in a jungle, and they did not appear alive.} \index{skin}skins\footnote{We found a bacteria within. (A mycobacteria.) You found it in a skin, and you told me it was microscopic.}. I saw it growing. I saw ripe \index{one}ones\footnote{We found someone within. You saw our someone in a hospital. It was not dangerous. Guilty. A criminal.}. I saw myself transfigured. I found \index{treasure}treasures\footnote{You saw this treasure in a box. (A treasure chest was within it.)}. I saw a bridal veil. 

 I was with my \index{lover}lover\footnote{A penis was not in this lover, and we found them in a bed. Attractive.} on a \index{veranda}veranda\footnote{You said that my veranda was not open.}. I was no longer a virgin. I heard the \index{voice}voice\footnote{You told me this voice was ugly, and we found a velvet within. They were in a choir.} of God. 

 I attended a wake. I saw \index{wallet}wallets\footnote{Your wallet was in a purse, and we found a money within.}. I found a wall obstructing my \index{progress}progress. I drank muddy \index{water}water\footnote{This water appeared blue, and I found a coral reef within. This coral reef seemed yellow.}. I saw swiftly rotating \index{wheel}wheels\footnote{Circular. Someone was in it. (It was healthy but not sound.) We found it in a garage.}. I sat in a \index{window}window\footnote{A lizard was in the window, and your lizard was in a dessert. You said they were a skink. Cute. You told me they were small.}. I saw a \index{wreath}wreath\footnote{We saw the wreath in a funeral. (A dead person was not in our funeral.)} of fresh \index{flower}flowers\footnote{I found a bee there, and it was in a flower garden.}.

\chapter{}

I heard the \index{music}music\footnote{The music was not loud, and you told me it was enjoyable. (I found it in a night club, and a classical music.) You found a harpsichord there.} of an \index{accordion}accordion\footnote{The accordion was in an orchestra.}. 

 I shook them from the \index{tree}trees\footnote{You told me the tree was tall. (It was a pine but not a pine tree.) This pine was alive and awake. We found a pine tree in it. I saw it in a pine tree.}. I saw one in distress. I bid adieu to home and country. I saw others afflicted. I saw an antelope missed its \index{footing}footing and \index{fall}fall\footnote{Our fall was discovered in a forest, and I found an apple tree in it.} from a \index{height}height\footnote{Light. (You found someone there.)}. I saw old or young in appropriate \index{apparel}apparel. I saw an \index{ass}ass\footnote{Our ass was found in a bookstore. Warm-blooded. A zit was not in them. (They looked good.)}. I saw \index{donkey}donkeys\footnote{Your donkey was competitive but not free-enterprise.} carrying \index{burden}burdens. I saw a \index{person}person\footnote{My person was an astronaut but not a cosmonaut. (I saw it in a bus stop, and it seemed human and nonhuman.) It was hairy but not hirsute. I found a liver in it.} \index{turn}turn\footnote{Someone was in our turn, and we found it in a train station.} and walk away from me. I saw \index{baseball}baseball\footnote{Stupid. (Educational.) We found a baseball game within.}. 

 I saw them growing abundantly. 

 I suffered with bronchitis. I saw a \index{fowl}fowl\footnote{You said this fowl was not a duck.} with my \index{brood}brood. I heard joyous \index{blast}blasts\footnote{You found a blast furnace there.} from a bugle. I ate fresh. I saw one sitting on a railroad. 

 I got off of one. I saw a \index{carpet}carpet\footnote{My carpet was discovered in a floor. You told me this floor was level, and you said it was not a roof. You found a tile in the roof.}. I saw a \index{cashier}cashier\footnote{This cashier was seen in a shop. Your shop was a bookstore but not a bookshop, and it was both flat and natural. (We found a cash register in it.)}. I accepted a \index{challenge}challenge\footnote{The challenge was found in a work, and a public servant.} of any \index{character}character\footnote{This character was funny, and they were in a novel.}. I saw a \index{brood}brood of \index{chicken}chickens\footnote{Our chicken appeared stupid. They seemed unhealthy. You said they were not a hen, and a chicken coop was within them. They were discovered in an oven.}. I dealt in \index{coffee}coffee\footnote{You said that our coffee was bad, and it was discovered in a cup. A latte.}. 

 I saw \index{combatant}combatants. 

 I saw a \index{comedy}comedy\footnote{You said your comedy was a slapstick. Funny.}. 

 I saw my \index{lover}lover in the \index{garb}garb\footnote{The garb looked unwanted. We found it in a garbage. (Unwanted.) It was a refuse but not a garbage. We found a refuse heap within.} of a convict. I saw shelled corn. 

 I saw \index{cotton}cotton\footnote{This cotton looked absorbent. We found a weasel within. It was flexible, and it was in a cotton ball.} in \index{bale}bales. I talked with the President of the United States. I made silken cushions. I saw \index{dahlias}dahlias. I lost my friend. I found myself alone in a desert. 

 I was one of many invited \index{guest}guests\footnote{We found a sofa bed within, and I saw them in a fraternity house.} at a \index{dinner}dinner\footnote{Our dinner seemed concave and convex, and a person was within it. Your person was warm-blooded. It was in a theater.}. I beheld a \index{dome}dome\footnote{The dome was discovered in a fairground, and you said that it was not dark. It seemed friendly and hostile, and it was a domestic animal but not a domesticated animal.} from a \index{distance}distance. 

 I was living on. I received a \index{dun}dun\footnote{We found a dungeon in my dun, and we found it in a dunce.}. 

 I saw a \index{dungeon}dungeon\footnote{Your dungeon was discovered in a basement. A first floor.} lighted up. 

 I saw my friends dwarfed. 

 I was in \index{place}places\footnote{A bed. (You told me your bed was big, and a human was within it.) It was found in a room. Empty.} of learning. I overcame my \index{enemy}enemies\footnote{Bad. You said that they were not fragile. We found them in a war, and a tank was not in the war.} in any \index{form}form\footnote{You found a rosebush within. Your rosebush was discovered in a flower garden.}. I saw others thus clothed. I saw my \index{face}face\footnote{You said your face was a hair. Your hair appeared natural and artificial, and it was both opaque and clear. It was in a mammal, and a mammoth was within it.} in a mirror. 

 I sustained a \index{fall}fall\footnote{We found a fungus there, and our fungus was found in a cave. It was a mushroom.}. I was buying a \index{farm}farm\footnote{A vineyard. A vintner was in your vineyard, and it was sparse.}. I saw \index{fig}figs\footnote{You told me this fig was safe, and you found someone there. It was nutritious and nutrient, and it was a war. The war was seen in a wart.} growing. I received a \index{bouquet}bouquet\footnote{I found a bee there, and you found the bee in an apiary.} of mixed flowers. I forsook my \index{home}home\footnote{An apartment. It was in a city, and a school was within this city.} or \index{friend}friend\footnote{I found a flower within, and my flower was found in a vase. You said that my vase was large, and it was a vasectomy.}. I saw a \index{bullfrog}bullfrog\footnote{My bullfrog was slimy but not wretched.}. I dealt in \index{fur}furs\footnote{The fur was a hair but not a whisker. Your hair was seen in a hairbrush. A hairbrush was within it. Blond.}. I saw others wearing \index{velvet}velvet\footnote{The velvet did not appear flexible, and you told me it was rough. You found it in a jewelry store.}. I saw \index{glass-blower}glass-blowers at their \index{work}work\footnote{This work was discovered in a desk, and it was not a homework. Someone was not in it. (Hard.)}. I found gold. I rode on \index{horseback}horseback\footnote{Our horseback appeared enjoyable.} and \index{passing}passing \index{musca-dine}musca-dine \index{bush}bushes\footnote{This bush was green but not gullible. (I found a paper within.) Alive. It was a coffee but not an umber, and I saw it in a rose garden.} and \index{gathering}gathering and \index{eating}eating some of its \index{fruit}fruit\footnote{My fruit did not appear unhealthy. It was a strawberry but not a strawberry mark. Someone was within this strawberry. It was discovered in a refrigerator.}. I turned a \index{grindstone}grindstone\footnote{My grindstone was both cool and warm.}. I saw a haggard face. 

 I saw other \index{thing}things\footnote{This thing appeared fuzzy. It was a universe. This universe was heavy and cloggy, and you found a planet within.} haltered. I had an injured \index{hand}hand\footnote{A finger was not in our hand. (You told me they were black.) They were found in a keyboard.}. I saw myself handsome-looking. I saw a large concourse of \index{person}people\footnote{A cousin. It appeared strange, and it was discovered in a conference. An assertiveness was within it.} gathering at a hanging. I was eating hash. I saw myself with two or more \index{head}heads\footnote{My head was in a ship. (You found a leader in them, and you told me they were dimmed.)}. 

 I was homesick. I had a \index{horse}horse\footnote{A barn was within my horse, and we found our barn in a field. Solid.} shod. I found a \index{horseshoe}horseshoe\footnote{Lucky. It was seen in a beach. A magnet. Strange.} hanging on the fence. I was trading \index{horse}horses\footnote{A palomino. It was in a movie. We found a projector in the movie, and the projector was fragile and delicate.}. 

 I worked in a \index{hotel}hotel\footnote{Your hotel did not appear educational. You said it was a motel, and I found a room in your motel. This room was in a home. Rectangular.}. I owned an elegant \index{house}house\footnote{You told me this house was little, and it was found in a subdivision. A city. We found a roadway within.}. I had a husband. I was eating \index{ice}ice\footnote{My ice was seen in a grocery store, and you said it was a flower. You found an ice age there. (It did not seem pale blue, and you told me it was slippery.)} cream. I received an \index{inheritance}inheritance. I saw \index{person}persons\footnote{This person was an atheist. Our atheist was both mortal and immortal. Irreligious. They were in a university. A human was not in them.} with the itch. I made jelly. 

 I saw a kangaroo's hide. I saw a \index{knapsack}knapsack\footnote{A notepad was in your knapsack.}. I had well-formed and smooth \index{knee}knees\footnote{Our knee was a groom.}. I made lace. I ascended to some height. I toed ascend to some height. I saw a \index{ladle}ladle\footnote{My ladle was high but not gamey, and it was discovered in a drawer.}. I saw myself reflected in a clear \index{lake}lake\footnote{A pebble was not in this lake, and our pebble was in a pond. The pond appeared finite.}. I saw foliaged trees reflected in the lake. I rode in a landau. I heard them singing as they flew. I caught them in \index{trap}traps\footnote{You found a mouse within. The mouse was cute, and they were found in a kitchen. They did not appear cute.}. I saw learned \index{man}men\footnote{You found a trouser in my man. You said my trouser was a jean, and my jean did not appear dressy. It was in a store.}. I put a \index{ledger}ledger\footnote{This ledger was in an account. (The account did not seem stupid.) It was not a general ledger.} into a safe. I had three. I saw \index{leopard}leopards in their native place trying to escape from me. 

 I scaped from me. I saw others afflicted thus. I killed a \index{lizard}lizard\footnote{A skink. This skink was in a bathroom. The bathroom was rectangular but not orthogonal, and a mouthwash was in it.}. 

 I saw others winning in a \index{lottery}lottery\footnote{You found a ticket in your lottery.}. I saw my own fair \index{loveliness}loveliness. 

 I was lying to escape punishment. I scaped \index{punishment}punishment\footnote{This punishment was seen in a jail, and you said it was not a sentence.}. I was in a mansion. I saw \index{mare}mares\footnote{This mare was seen in a field, and we found a wild flower there.} in pastures. I had a \index{master}master\footnote{A master bedroom was not in the master. You said they were a poet, and our poet was seen in a coffee shop.}. I saw myself in a \index{mirror}mirror\footnote{Your mirror was in a purse, and we found a pen there. A shoulder bag.}. I was befriended by a miser. I ate them. I was listening to the harmonious \index{note}notes\footnote{I found my note in an envelope. It was a protocol but not a communications protocol.} of the \index{nightingale}nightingale\footnote{My nightingale was alive.}. I inhaled sweet \index{odor}odors\footnote{We found the odor in a dirty laundry.}. I gave \index{offense}offense. I found myself luxuriously reposing upon an \index{ottoman}ottoman\footnote{The ottoman was discovered in a chair. It was both safe and dangerous.}. I saw \index{ox}oxen\footnote{Red. It was in an air, and someone was in it. It seemed strange, and it was not an oxymoron.} well-matched and yoked. I dealt in \index{oyster}oysters\footnote{A pearl was in this oyster. It was seen in an ocean.}. I painted a \index{picture}picture\footnote{A rosebush was within your picture. The rosebush was in a backyard.}. I raised the \index{pall}pall\footnote{You told me my pall was palliative. It seemed ugly, and it was in a palliative.} from a corpse. I saw a \index{panther}panther\footnote{Your panther appeared cool.} and \index{experience}experience\footnote{My experience appeared painful and painless.} \index{fright}fright\footnote{My fright was not a tornado, and our tornado appeared mild. A projectile was within it.}. I gathered them. 

 I enjoyed \index{drink}drinks\footnote{A liquid was within my drink, and you said it was not a cappuccino. You said that my cappuccino was not bitter.} in which there was an \index{effusion}effusion of \index{peppermint}peppermint\footnote{Your peppermint was opaque. Alive.}. I reached a pier and fail. I strove to reach a \index{pier}pier\footnote{Sexy. I saw it in a bridge, and you found a troll in my bridge.} and fail. I stood by me \index{lover}lover\footnote{A penis was in the lover. We saw the penis in a vagina.} beneath the \index{blossom}blossoms and leaved of a \index{tulip}tulip\footnote{My tulip appeared pretty. A bee was within it, and a queen bee. The queen bee seemed good.} \index{poplar}poplar. I promenaded. I cooked. 

 I was studying the \index{mystery}mystery\footnote{You said my mystery was not a time, and your time was in a kitchen. (I found a knife in your kitchen, and you told me it was big.)} of the ancient pyramids. I questioned the \index{merit}merits\footnote{My merit appeared offensive and defensive.} of a \index{thing}thing\footnote{Fuzzy. You saw it in a place. A university. A student was not in your university, and you said that it was not yellow.}. I overcame it. 

 I was unable to overcome it. I saw railings. I was out in a clear \index{shower}shower\footnote{My shower was discovered in a house, and our house seemed solid. I found a bathroom in it.} of \index{rain}rain\footnote{A shower. A shampoo was within my shower, and they appeared cold. They were in a motel room.}. I saw \index{raspberry}raspberries\footnote{Our raspberry did not seem green. It was discovered in a jar.}. I saw various \index{kind}kinds of \index{reptile}reptiles\footnote{A reptile family was within our reptile.}. I cooked it. I saw vacant \index{rocking-chair}rocking-chairs. 

 I walked a \index{rope}rope\footnote{I found a nylon in your rope, and we saw it in a boat. A tugboat.}. I saw \index{rose}roses\footnote{Green. We saw it in a rosebush, and a rosebush was within it. You told me it was romantic.} blooming and fragrant. I saw a roundabout. I saw a safe. I ate \index{salt}salt\footnote{This salt seemed hard, and we found it in a salt mine.}. 

 I was one of the \index{serenader}serenaders. I lost my \index{shirt}shirt\footnote{My shirt was an undershirt but not a singlet, and a silk was within it. This silk was in a parachute. You said that it was flexible. It was silky.}. I saw young people skating on \index{roller}roller\footnote{I found someone in my roller. The someone was dangerous but not life-threatening, and it was seen in a museum. It was a criminal but not a malefactor. You told me our criminal was smart.} \index{skate}skates\footnote{A skateboard was within our skate. Silly. It was seen in a skateboarder.}. I killed them. I was at a soda \index{fountain}fountain\footnote{Your fountain was classy, and it was in a forest. It did not seem dark, and a coin was not in it.}. I made soup. I saw \index{spider-webs}spider-webs. I saw stags. I ate them. I saw \index{sulphur}sulphur\footnote{Cute.} \index{burning}burning\footnote{The burning was powerful. You told me it was reversible.}. I walked through swampy \index{place}places\footnote{A rug was within the place. (You saw this rug in a bedroom, and this bedroom seemed dark.)}. I saw rich \index{tapestry}tapestry\footnote{The tapestry was in a museum.}. I used a \index{thimble}thimble\footnote{You found our thimble in a cabinet.}. I saw a thumb. 

 I took a \index{toddy}toddy\footnote{My toddy was stupid and dazed.}. I was trying to alleviate the \index{torture}torture\footnote{You said that our torture was not dangerous. I found a torture chamber in it. It was evil.} of others. 

 I alleviated the \index{torture}torture\footnote{This torture was both dangerous and safe, and a torture chamber was not in it. Evil.} of others. I saw \index{tourist}tourists\footnote{Your tourist was a tourist attraction.}. I saw filled \index{trench}trenches\footnote{You found a soldier within.}. I saw \index{trout}trout\footnote{Your trout was blue and gamy, and it was found in a restaurant.}. I saw a green \index{turf}turf. I was supporting an urgent \index{petition}petition. I drank from a \index{vase}vase\footnote{You said my vase was a vasectomy.}. I was in a \index{village}village\footnote{A barbershop was within our village, and you found this barbershop in a razor.}. I saw them dry. I saw \index{vitriol}vitriol. I voted fraudulently. I saw me lover at a wake. I saw the \index{waltz}waltz\footnote{The waltz was in a ballroom, and it did not seem nice.} danced. I saw \index{water-carrier}water-carriers passing. 

 I fell into a well. I climbed a steep \index{hill}hill\footnote{We found a valley there, and my valley was low. You said it was not a vale.} covered with \index{wheat}wheat\footnote{This wheat was edible and eatable. You found a wheat field in it, and you saw it in a bread.} and think me was pulling myself up by the \index{stalk}stalks of wheat. I was pulling myself up by the \index{stalk}stalks of \index{wheat}wheat\footnote{We found a wheat field there.}. I was a widow. I drank \index{wine}wine. I was hard at \index{work}work\footnote{A public servant, and a worker was within it. You told me it was undynamic, and it was seen in a desk.}. I worked with \index{yarn}yarn\footnote{This yarn was in a cabinet.}. 

 I saw \index{zinc}zinc\footnote{Your zinc did not seem opaque.}. I worked with or to see \index{zinc}zinc\footnote{You said that my zinc was malleable.}.

\chapter{}

I saw \index{acrobat}acrobats\footnote{Your acrobat was creative and originative.}. I thought she was an \index{adventuress}adventuress\footnote{Our adventuress did not seem safe.}. I saw others afraid. I related an \index{anecdote}anecdote\footnote{This anecdote was in a story.}. I made \index{broth}broth. I was in a \index{castle}castle\footnote{The castle was dark and dingy. Big. A knight was within it. (My knight was discovered in a chess set.)}. I ate them. I was attacked by it. I was a \index{concubine}concubine\footnote{Mean.}. I saw a \index{convent}convent\footnote{The convent was not dark, and it was not a convention. (You found a person in it.) My person was in a conference. It was human.}. 

 I drew \index{cork}corks\footnote{The cork was in a corkscrew. We found a tack in it.} at a \index{banquet}banquet\footnote{We found someone there. Your someone was in a desk. You told me it was guilty. It was both dangerous and safe, and you said it was a slave.}. I saw \index{cornmeal}cornmeal\footnote{Our cornmeal was in a cupboard.}. I saw cows waiting for the milking \index{hour}hour\footnote{We found an hourglass there. You told me it was late.}. I associated with a \index{person}person who had committed a \index{crime}crime\footnote{This crime was in a demonstration, and a victim was in it. Bold. Dangerous. It was not a steal.}. I possessed one. I felt delight when looking on beautiful \index{landscape}landscapes\footnote{Our landscape was found in a university, and my university did not appear yellow. Someone was not in it.}. I entertained \index{envy}envy for others. I saw \index{fish}fish\footnote{Our fish was alive but not animated. Diverse. You said it was not a crappie, and I saw it in a river. A blowfish was within it.}. I waded in \index{water}water\footnote{Our water was a steam. It was in a rain. (It was fleet and swift, and a coral reef was within it.) It was liquid.}. I dealt in \index{flour}flour\footnote{I found this flour in a cabinet, and you found a pantry in it.}. I saw a \index{garden}garden. I lost my \index{glove}gloves\footnote{Your glove was discovered in a store. (You said it was not a baseball mitt.)}. I handled \index{gold}gold\footnote{A gold mine was within my gold. Educational.}. I washed my \index{head}head\footnote{I found a mouth within. Your mouth was in a face. They were important. They were not a lip.}. I saw a \index{sow}sow\footnote{This sow was big and braggy, and you said it was not a sower.} and litter of pigs. I gained the \index{top}top\footnote{I found a peak within. This peak was found in a mountain.}. 

 I was riding up a \index{hill}hill\footnote{The hill was a sand dune but not a dune.} and the \index{horse}horse\footnote{Competitive. A palomino.} fell but I gained the \index{top}top\footnote{Someone was in our top, and you saw it in a build.}. I was overcome with \index{humidity}humidity\footnote{I saw my humidity in an air.}. I was on an island in a clear \index{stream}stream\footnote{You told me our stream was shallow, and someone was within it. I saw this someone in a lake.}. I saw Krishna. I scaped from \index{captivity}captivity\footnote{We found a lizard within.}. I saw \index{lamb}lambs\footnote{Someone was within your lamb. They were red but not ruby-red. They were in a farm. This farm was not a vineyard. You told me it was sparse.} taking \index{nourishment}nourishment\footnote{My nourishment was not a food. Your food looked edible and inedible.} from their \index{mother}mothers\footnote{This mother was not important. A kitten was in them. They were found in a house. They were a woman but not a cleaning lady. You told me this woman was hot.}. I took \index{laudanum}laudanum\footnote{Bad.}. I joined a merry \index{party}party\footnote{Our party was in a fraternity house, and we found a paddle in your fraternity house. This paddle did not appear heavy. A girl. (Red.)} upon a \index{lawn}lawn\footnote{Our lawn was a lawn chair. Our lawn chair was in a lawn.}. I bought \index{lettuce}lettuce\footnote{This lettuce was in a supermarket, and you found a bag in the supermarket. You told me it was light.}. I saw linseed \index{oil}oil\footnote{Our oil was discovered in a grind, and my grind was a cave. We found a stalagmite there.}. I saw loaves multiplied phenomenally. 

 I found myself inside a \index{mausoleum}mausoleum\footnote{Our mausoleum did not seem green.}. I gave \index{milk}milk\footnote{This milk looked white and black. (We saw it in a house.) An igloo. I found a toilet within. It did not appear noble.} away. I found myself reading or examining mortgages. I threaded a \index{needle}needle\footnote{You told me the needle was sharp, and you found it in a haystack. I found a needle there.}. I handled \index{oar}oars\footnote{You said our oar was not a paddle. You told me your paddle was red, and it was both useful and useless. (You saw it in a fraternity house.)}. I saw or eat \index{parsnip}parsnips\footnote{Your parsnip was both edible and inedible.}. I did \index{family}family\footnote{A support was in the family. My support was in a bridge, and you told me this bridge was cheap.} patching. I saw a \index{bed}bed\footnote{My bed was a cot but not a fingerstall. It looked big and little, and it was opaque and unintelligible. You found a mattress in it. (Your mattress was in a bed.)} of radishes growing. I floated on a \index{raft}raft\footnote{I found my raft in a rafter.}. I saw others reading. I saw a \index{refrigerator}refrigerator\footnote{I found a dirt within, and it seemed cold and hot. It was in a mall. It was both strong and weak. A fridge.}. I was self-reproached in the \index{midst}midst of a religious \index{excitement}excitement\footnote{Our excitement was in a library.}. I made \index{sausage}sausage\footnote{Our sausage was found in a pizza. (It was yummy but not luscious.)}. I shaved myself. I saw only the \index{side}side\footnote{You told me your side was square. (A fire hydrant was in it, and you found it in a sideboard.)} of any \index{object}object\footnote{My object was a tool. Heavy. (They were not solid.) A tool chest was within them. This tool chest was found in a garage.}. I had a fleshy. I saw others taking \index{soup}soup\footnote{Your soup did not seem yummy. You said it was not a miso.}. I saw one building its web. I saw many spiders hanging in their \index{web}webs\footnote{The web appeared impressive and unimpressive, and it was in an internet. (You said that our internet was beige, and a pornography was not in it.)} around me. I dealt in them. I cut off the \index{tail}tail\footnote{I saw this tail in an animal. (My animal seemed pure.) We found a nerve in it.} of an animal. I bought \index{leather}leather\footnote{My leather was solid. It was adaptable. It was in a car, and a woodwind was within it.} from a \index{tannery}tannery. I found myself teasing any person. 

 I was teased. 

 I scaped from one during a \index{fire}fire\footnote{The fire was in a fire hydrant. A firehouse was within it.} or other \index{excitement}excitement\footnote{We found your excitement in a hockey game.}. I tried to escape from one during a \index{fire}fire\footnote{My fire appeared dangerous and safe, and you found a fire station within. I saw it in a fireplace.} or other \index{excitement}excitement\footnote{The excitement was in a hockey game.}. I saw \index{turkey}turkeys\footnote{A heart was not in my turkey, and the heart was in an animal. You said it was a love. It was mortal.}. I sowed turnip \index{seed}seed\footnote{You found our seed in a seed catalog.}. I saw twins. I borrowed one. I saw others \index{varnishing}varnishing. I won a \index{victory}victory\footnote{Your victory was momentary.}. I was a wet \index{nurse}nurse\footnote{Your nurse was in a clinic, and a nursery was not in them.}. 

 I saw \index{barrel}barrels\footnote{The barrel appeared hollow, and it was in a market. (We found a coupon in our market.) Our coupon was not a luncheon voucher.} of \index{wine}wine\footnote{This wine was seen in a bottle. This bottle seemed recyclable. (You found a mouthwash there.)}. I was possessed of \index{wisdom}wisdom\footnote{This wisdom appeared good and bad, and it was discovered in a wisdom tooth.}. 

 I saw a \index{yacht}yacht\footnote{Expensive. (It was a yacht race but not a sailing-race.) Someone was in it, and you said that your someone was hard. It was found in a theater.}.

\chapter{}

I thought myself held in \index{abhorrence}abhorrence by others. I had been accepted by my \index{sweetheart}sweetheart. I thought myself one. I saw others in \index{adversity}adversity. I saw green \index{apparel}apparel. 

 I rode in an \index{automobile}automobile\footnote{A steel was not in our automobile, and my steel was in a build. You told me it was strong. (A stainless steel.) My stainless steel was strong and inviolable.}. I saw a beacon-light. I ate them. I saw flying \index{bird}birds\footnote{A feather was in our bird. Your feather was soft. A quill. Your quill was in a museum.}. I saw full money \index{box}boxes\footnote{You told me the box was clear, and it was discovered in a garage. It was glorious and brilliant, and you found a business card there. A cart.}. I found one. 

 I saw a \index{lot}lot\footnote{My lot seemed simple and complex, and it was a fortune but not a luck. A moistener was within it. It was in a person.} of impure \index{bread}bread\footnote{A mold was within this bread, and the mold was discovered in a cellar. You told me it was useless.}. I was eating alone. I saw a butterfly among flowers and green grasses. I rode on a \index{car}car\footnote{Our car was hard. It was seen in a road. You said it was not a bus, and this bus appeared smooth and rough. A sign was not in it.}. I bought carpets. I saw good-looking and fat \index{cattle}cattle\footnote{You saw this cattle in a fairground. A heifer was within it, and you said that it was alive.} contentedly grazing in green pastures. I milked \index{cow}cows\footnote{My cow did not seem warm-blooded. (You saw them in a barnyard.) A cow was not in this barnyard.} with \index{udder}udders well filled. I carried fresh \index{flower}flowers\footnote{My flower appeared organic. (It was in a table.) You said the table was a desk. You told me it was rigid. We found a tablecloth there.} to a \index{cemetery}cemetery\footnote{The cemetery was in a field, and we found a bug in this field. Your bug was small but not modest, and it was small.}. I saw a \index{chair}chair\footnote{This chair was not flammable. They were comfortable, and they were in a room. A chemistry lab. A computer was not in it.} \index{maker}maker\footnote{Your maker appeared late.}. I saw an empty one. 

 I was corpulent. I asked for credit. I experienced delight over any \index{event}event\footnote{You told me your event was transient, and you found someone there. It was not an election.}. I killed a \index{snake}snake\footnote{You said the snake was not a cobra. Our cobra did not seem destructive.} in my \index{presence}presence\footnote{Your presence did not seem stupid, and it was not a cholelithiasis.}. I thought I was eloquent of speech. I was eloquent of \index{speech}speech\footnote{This speech was not a talk. The talk was in a talk show.}. I was defamed by my \index{enemy}enemies\footnote{The enemy seemed bad and unregretful. They appeared mean. They were seen in a war.}. I was a \index{failure}failure\footnote{My failure was catastrophic. (We saw them in a casino.) You found a gambler within.}. I was at a fair. I was visiting a farm. I saw green \index{field}fields\footnote{You told me your field was expensive, and you said that it was breathtaking. You said it was not a prairie, and a ranch was not in my prairie.}. I saw decayed \index{fish}fish\footnote{My fish was discovered in a lake. It was not pure, and I found a blowfish within. (A shark.) Your shark was big.}. I saw \index{frog}frogs\footnote{You told me this frog was ripe. (It did not appear alive.) You saw it in a sea. A gut was within it.} in the \index{grass}grass\footnote{Our grass was in a grind, and I found a grasshopper in them. A lawn. (My lawn was healthy.)}. I was dressed in \index{gauze}gauze\footnote{Pretty. It was discovered in a hospital.}. I ran a \index{gig}gig\footnote{A planet. It was in a craven.}. I saw me husband in a mirror. I was playing golf or watching the game. I was studying \index{grammar}grammar\footnote{The grammar was straight and full-strength, and it was a grammar school. It was incorrect.}. I dug a \index{grave}grave\footnote{Grey. A casket was within it. (Your casket was in a graveyard.)}. I saw the \index{hair}hair\footnote{Your hair seemed colour. You said that it was flammable. I found a mammoth there. We saw it in a drain, and it was an eyebrow but not a supercilium.} growing out soft and luxuriant. I visited a \index{hair-dresser}hair-dresser. I dealt in \index{ham}hams\footnote{You told me our ham was hard. Yummy. (They were a hamburger but not a burger.) They were in a refrigerator, and a beer was in our refrigerator.}. I possessed bright new \index{harness}harness\footnote{My harness was human.}. 

 I fell \index{heir}heir\footnote{You said the heir was not a government.} to \index{property}property\footnote{You said my property was not a ranch. I found a property line there.} or \index{valuable}valuables\footnote{I found this valuable in a vault, and you said it was not a hand.}. 

 I visited my old \index{home}home\footnote{A condominium. You found a sofa within, and you told me it was bad. (You saw it in a city.)}. I ate \index{horseradish}horseradish\footnote{The horseradish did not seem green. You found a sofa bed in it, and we found it in a jar.}. I hunted a \index{hotel}hotel\footnote{Your hotel seemed drafty, and I found a concierge in it. It was found in a city, and it was a motel. Your motel was drafty but not draughty.}. I saw a hut in a green \index{pasture}pasture\footnote{This pasture was pure but not virtuous, and a cow was within it. You found it in a countryside, and the countryside was beautiful.}. I saw \index{ice}ice\footnote{We found an iceberg there. (You said that your iceberg was yellow.)} floating in a \index{stream}stream\footnote{Our stream was a brook but not a creek, and it was in a river. You found a pebble in our river. Painful.} of clear \index{water}water\footnote{My water was in a soup. You found a sloth in this soup. Our sloth appeared distinct, and it was slow.}. I saw others worshiping \index{idol}idols. 

 I gained an \index{independence}independence\footnote{My independence was delightful and delicious.} of \index{wealth}wealth\footnote{A diamond was within our wealth. It did not appear large. (I found it in a library.)}. I made jam. I saw them full. I was in the \index{jaw}jaws\footnote{A shark was not in this jaw.} of a wild \index{beast}beast\footnote{You said our beast was not a beast of burden.}. I was cleared from a charge by the jury. I ascended a \index{ladder}ladder\footnote{This ladder was not a stepladder. Your stepladder was in a hardware store, and we found a grill there.}. I prevented others from taking this \index{drug}drug\footnote{You said that this drug was dangerous. It appeared good and evil, and it was discovered in a concert. You found a drugstore in it. A pill.}. I saw \index{lemon}lemons\footnote{Your lemon appeared delicious, and it was seen in a mall. (Your mall seemed beautiful and ugly.) I found a movie theater there.} on their \index{native}native\footnote{You said that the native was not human, and we found them in a country.} \index{tree}trees\footnote{You said this tree was not an evergreen. (It was alive and awake, and you told me it was green.) It was in a forest, and I found a stick in your forest.} among rich \index{foliage}foliage\footnote{Our foliage was a perennial. I found it in a forest. (A stream was within this forest.)}. I wrote one. I saw a \index{lion}lion\footnote{You said that the lion was not competitive, and a gazelle was within them. We saw my gazelle in a forest.}'s \index{skin}skin\footnote{You found this skin in a person, and it looked elastic. I found a moistener within.}. I saw \index{liquor}liquor\footnote{A spirit was within our liquor, and it was a whiskey but not a whisky. (It was empty, and you found it in a fraternity house.)} in barrels. 

 I saw others suffering under this \index{malady}malady. 

 I accomplished any \index{design}design\footnote{Your design was found in a rug, and someone was within it. Guilty.} by \index{magic}magic\footnote{You found someone in the magic, and it appeared real. It was discovered in a fairy tale, and you said that it was dark. A love.}. I saw the \index{minuet}minuet danced. I looked upon a \index{quantity}quantity\footnote{You said this quantity was not a number, and we found a safety in my number. It appeared infinite. It was discovered in a mathematics, and it was both solid and liquid.} of \index{money}money\footnote{The money was mutual, and a billfold was not in it. (It was seen in a pocket, and it was not a time.)}. I slew a \index{monster}monster\footnote{Our monster was not a zombie, and I saw your zombie in a theater.}. I received a \index{necklace}necklace\footnote{The necklace was a choker but not a garrotter. Your choker appeared expensive, and they were discovered in a jewelry store.}. I saw a dead \index{nun}nun\footnote{Someone was in our nun, and you saw my someone in a museum.}. I saw a \index{nurse}nurse\footnote{You found my nurse in a hospital, and this hospital looked clean and dirty. A bed was in it.} leaving my \index{house}house\footnote{You said my house was an igloo, and someone was within this igloo. It did not appear red.}. I saw decayed \index{oat}oats\footnote{A mouse was within my oat, and you said that it was organic. It was in an oatmeal.}. I saw a \index{packet}packet\footnote{An internet.} coming in. I saw my \index{parent}parents\footnote{My parent was seen in a family, and your family was evil. They were a wife. You said that they were not loud. An uncle was within them.} looking cheerful. I dissolved an unpleasant \index{partnership}partnership\footnote{Solid.}. I attended a \index{party}party\footnote{You found my party in a home. They were invertible, and a game was within them. Educational.} of any \index{kind}kind for \index{pleasure}pleasure\footnote{You said your pleasure was a kiss. (Sharp.) I saw it in a palace, and you told me it was enjoyable.}. I saw them flying. I saw the \index{skin}skin\footnote{Your skin was discovered in a fruit. Colorful. A seed was in it.} of one. I was innocent. I arrested me for some crime of which I was innocent. I saw \index{poplar}poplars. I owned vast property. I danced a \index{quadrille}quadrille. I asked a \index{question}question\footnote{A question mark was within this question.}. I walked the \index{rail}rails\footnote{A railway was within the rail. (It was discovered in a railway station.)}. I saw the \index{rainbow}rainbow\footnote{I found a sky in this rainbow. It was discovered in a water fountain, and it appeared beautiful and ugly.}. I attended a \index{reception}reception\footnote{A lobby was within the reception, and you said our lobby was a lobbyist. I saw it in a receptionist. It appeared dark.}. I was the successful \index{rival}rival\footnote{The rival was both safe and out.}. I imagined that I was the successful \index{rival}rival\footnote{The rival appeared safe.}. I saw a clear. I thought. I saw or hear that the \index{leader}leader\footnote{Your leader appeared important. They were in a pack.} was dead. I shook hands with those beneath me. I saw \index{squirrel}squirrels\footnote{Distinct. We saw it in a countryside.}. I passed up a \index{stair}stairs\footnote{Our stair was not a stairwell, and my stairwell was in a build. We found a fire extinguisher there.}. I was a \index{standard-bearer}standard-bearer. I ate \index{sulphur}sulphur\footnote{My sulphur appeared strange.}. I saw them flying. I saw others shedding tears. 

 I admired my teeth for their \index{whiteness}whiteness and \index{beauty}beauty\footnote{We found a beauty salon in my beauty. My beauty salon was seen in a strip mall.}. I saw \index{torch}torches\footnote{Your torch was in a backpack. Powerful.}. I was a member of a \index{trust}trust\footnote{The trust looked good. You said it was not a faith.}. I imagined me was a member of a \index{trust}trust\footnote{Good. It was a faith but not an organized religion.}. I saw others took a Turkish \index{bath}bath\footnote{You found someone within, and it was in a house. (My house appeared comfy.) It was a duplex but not a semidetached house.}. I saw an \index{ulcer}ulcer\footnote{Your ulcer was not an ulcerative colitis, and this ulcerative colitis was contagious and contractable.}. I was on a \index{veranda}veranda\footnote{Our veranda was open but not unresolved.}. I revisited the \index{village}village\footnote{A barbershop was not in the village, and the barbershop was in a razor.} \index{home}home\footnote{We found your home in a field, and we found a daisy within. The daisy seemed yellow, and it was both green and ripe.} of my \index{youth}youth. I saw \index{violet}violets\footnote{You told me the violet was small. It was pretty.}. I used them as fish \index{bait}bait. I relieved or dress a \index{wound}wound\footnote{I found my wound in a war, and a bullet was within it. You told me this bullet was round. (You said it was a bulletin.)}.

\chapter{}

I served as an \index{apprentice}apprentice. 

 I saw vacant \index{teller}tellers\footnote{Your teller was discovered in a bank. Someone was within our bank. It looked competitive. It was not a credit union.}. I saw others doing so. I saw this beast of \index{burden}burden. 

 I walked on a \index{carpet}carpet\footnote{The carpet was discovered in a room. A floor was within it, and you told me it was soft.}. I saw them in full \index{bloom}bloom\footnote{An apple tree was in the bloom, and this apple tree was found in a backyard.}. I saw a damask \index{rosebush}rosebush\footnote{We saw this rosebush in a garden.} in full \index{foliage}foliage\footnote{We saw the foliage in a forest.} and \index{bloom}bloom\footnote{An orange tree was in this bloom. It was not an apple tree.}. I saw them on their \index{parent}parent\footnote{Someone was within this parent, and the someone was both dangerous and safe. You saw it in a lake, and you told me your lake was hot.} trees. I wandered through a gloomy and barren \index{desert}desert\footnote{A cave was within my desert. (Your cave appeared underground, and it was in a bat.)}. I saw a drum. I whipped my \index{assailant}assailant. I defended a \index{fort}fort\footnote{A fortune cookie was within the fort, and this fortune cookie looked sweet and sour.}. 

 I killed a \index{fox}fox\footnote{Distinct. We found them in a foxhunt.}. I ate \index{ham}ham\footnote{This ham was seen in a store. A hamper was within them. You told me they were cheap, and they appeared expensive. A hammer.}. I was hauling and putting hay into \index{barn}barns\footnote{A mouse was not in the barn. We saw it in a farm. It was ugly.}. I was a \index{hermit}hermit\footnote{Your hermit was in a fish tank.} myself. 

 I committed \index{homicide}homicide\footnote{My homicide seemed human, and you said it was a murder. We found your murder in a murderer, and it seemed wrong and right.}. I saw or gather. I saw \index{kettle}kettles\footnote{A spout was within your kettle. My spout was in a garage.}. I carried lambs in my \index{arm}arms\footnote{Our arm was in an air, and we found a pollution within. (You said this pollution was not an air pollution.) It seemed bad and good.}. I walked upon well-kept \index{lawn}lawns\footnote{You found a sprinkler in the lawn. Healthy. We saw it in a golf course.}. I saw the \index{lightning}lightning\footnote{This lightning looked loud and piano. (Powerful.) I found it in a cloud.} above my \index{head}head\footnote{Dangerous. We found them in a beer. Wide. I found a tab within.}. I saw \index{lobster}lobsters\footnote{The lobster seemed good, and it was in an ocean.}. I saw one completely demolished. I wove on an oldtime \index{loom}loom. I dealt in \index{milk}milk commercially. I received \index{gold}gold\footnote{My gold was not ductile. You found a gold mine in it.}. I saw a \index{forest}forest\footnote{You found a creature in the forest. You said that our creature was not alive. I found them in a movie. A giant.} of \index{oak}oaks\footnote{This oak was seen in an oak tree.}. I joined this order. I gathered the ripe fruit. I heard their harsh \index{voice}voices\footnote{Someone was in our voice. They appeared beautiful and ugly. A soprano. They were found in a school.} while looking upon their proudly spread \index{plumage}plumage. I inhaled \index{perfume}perfume\footnote{You found this perfume in a cabinet, and a plate was not in our cabinet. (Our plate seemed flat and contrasty.) A dish.}. I saw them soiled or torn. I stood upon a \index{pier}pier\footnote{Dangerous. It was in a bridge, and you told me it was sexy.}. I was in a \index{race}race\footnote{A car was not in the race. (It was in a race horse.)}. 

 I saw \index{radish}radishes\footnote{This radish was found in a refrigerator. It did not seem edible.}. I saw one quietly grazing denoted that I will have powerful \index{friend}friends\footnote{My friend was mortal and deadly, and someone was within them. You told me they were unimportant, and they were in a school.}. I willed have powerful \index{friend}friends\footnote{Emotional. A flower was not in them, and we found our flower in a table. You told me it was asexual.}. I saw a \index{sheriff}sheriff\footnote{My sheriff was strange and unusual.}. 

 I saw it melt. I petted one. I set a \index{table}table\footnote{My table was hazardous but not wild. A desk. It was seen in a library. It was stable. You found a silverware there.} preparatory to a \index{meal}meal\footnote{This meal was found in a plane. This plane was both hard and soft. (You told me it was little.) We found a flight attendant within.}. I cleaned or wash my \index{tooth}teeth\footnote{This tooth seemed white, and it was discovered in a mouth. A tooth was within your mouth.}. I broke down or have an accident while \index{threshing}threshing. I usurped my \index{right}rights\footnote{Someone was within this right, and it was not an atheist. The atheist was in a hospital.}. I had this \index{dream}dream\footnote{You said our dream was a freedom, and my freedom did not appear important. (It was in a university.) It appeared relative and absolute.}. I found myself walking through green and pleasant \index{valley}valleys\footnote{I found a river in my valley, and our river was both dark and light. (It was discovered in a waterfall, and you told me this waterfall was spectacular.)}. I saw them bleeding. I made a \index{voyage}voyage\footnote{This voyage was not a passage, and we found it in a voyager.}. I drank \index{wine}wine\footnote{The wine was wide. Tasty. It was in a bottle. (You said my bottle was not a carafe, and a neck was in it.)}. 

 I dealt in \index{firewood}firewood\footnote{Our firewood was found in a store, and your store was a shop but not a shop class. It was both tall and short. A bread was not in it.}. 

 I saw a bridal \index{wreath}wreath\footnote{You saw our wreath in a front door.}.

\chapter{}

I was sleeping on a bed in the open \index{air}air\footnote{Someone was within this air. It was flammable and inflammable, and it was seen in a plant. You told me it was invisible.}. I saw a clear. I saw young \index{girl}girls\footnote{Your girl was sensitive, and we saw them in a door. They were not a niece.} carrying \index{sunshade}sunshades. I saw white \index{swan}swans\footnote{Our swan appeared black. (It was not alive.)} floating upon placid \index{water}waters\footnote{A coral reef was within our water. The coral reef was dangerous and grievous.}. I carried a new \index{umbrella}umbrella\footnote{You found our umbrella in a front door. It was both sweet and sour, and I found someone there. (You told me it was blue.)} over me in a clear shower. I waded in clear \index{water}water\footnote{We found a boat in our water. (You said it was not a steam.) Transparent. You found it in a rain, and it seemed hard.}.

\backmatter
\printindex

\chapter{Attributions}

This work includes data from ConceptNet 5, which was compiled by the
Commonsense Computing Initiative. ConceptNet 5 is freely available under the
Creative Commons Attribution-ShareAlike license (CC BY SA 3.0) from
http://conceptnet5.media.mit.edu. The included data was created by contributors
to Commonsense Computing projects, contributors to Wikimedia projects, Games
with a Purpose, Princeton University's WordNet, DBPedia, OpenCyc, and Umbel.

WordNet Release 3.0 This software and database is being provided to you, the
LICENSEE, by Princeton University under the following license. By obtaining,
using and/or copying this software and database, you agree that you have read,
understood, and will comply with these terms and conditions.: Permission to
use, copy, modify and distribute this software and database and its
documentation for any purpose and without fee or royalty is hereby granted,
provided that you agree to comply with the following copyright notice and
statements, including the disclaimer, and that the same appear on ALL copies of
the software, database and documentation, including modifications that you make
for internal use or for distribution. WordNet 3.0 Copyright 2006 by Princeton
University. All rights reserved. THIS SOFTWARE AND DATABASE IS PROVIDED "AS IS"
AND PRINCETON UNIVERSITY MAKES NO REPRESENTATIONS OR WARRANTIES, EXPRESS OR
IMPLIED. BY WAY OF EXAMPLE, BUT NOT LIMITATION, PRINCETON UNIVERSITY MAKES NO
REPRESENTATIONS OR WARRANTIES OF MERCHANT- ABILITY OR FITNESS FOR ANY
PARTICULAR PURPOSE OR THAT THE USE OF THE LICENSED SOFTWARE, DATABASE OR
DOCUMENTATION WILL NOT INFRINGE ANY THIRD PARTY PATENTS, COPYRIGHTS, TRADEMARKS
OR OTHER RIGHTS. The name of Princeton University or Princeton may not be used
in advertising or publicity pertaining to distribution of the software and/or
database. Title to copyright in this software, database and any associated
documentation shall at all times remain with Princeton University and LICENSEE
agrees to preserve same.

\end{document}

